---
title: "Checking SZ Pipeline outputs"
output:
  html_document:
    keep_md: TRUE
    toc: TRUE
---

## gonna check that our subject list don't inlude any missing data


```{r}
library(tidyverse)
```

```{r}
## we created a list of files that are super short after censoring..
number_tr1 <- read_table2("../data/data/number_tr.txt", 
    col_names = c('num_TR','path')) %>%
    separate(path, into = c('project', 'hcp', 'subid','therest'), sep = .Platform$file.sep, extra = "merge") %>%
    select(num_TR, subid)
number_tr2 <- read_table2("../data/data/cobre_numtr.txt",
                      col_names = c('num_TR','path')) %>%
  separate(path, into = c('subid','therest'), sep = .Platform$file.sep, extra = "merge") %>%
  select(num_TR, subid)

num_tr = bind_rows(number_tr1, number_tr2)

subjects_not_sexmatched_20180507 <- read_csv("../phenotypic/subjects_not_sexmatched_20180507.csv")


alldata <- inner_join(num_tr, subjects_not_sexmatched_20180507, by = "subid")
alldata %>% filter(num_TR < 100) %>% select(Site, X.bad_fd, num_TR, subid)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
