---
title: "ABIDEI PINT FC mat stats"
author: "Erin W Dickie, Saba Shahab"
date: "January 15, 2018"
output:
  pdf_document: default
  html_document: default
---

This is an analysis of the FC Mats - 8mm

```{r, message = F, error=FALSE}
library(dplyr)
library(tidyr)
library(broom)
library(igraph)
library(knitr)
library(ggplot2)
library(gridExtra)
```

# Reading in the data

A couple things to note here about the how the clinical data is being parsed:

1. all catergorical variables are being set to Factors
   + Note that sex.x still needs descriptive labels
2. Education is being very basically impluted when it is not available so that we donot lose data

```{r}
## Modified by Saba Shahab on November 9, 2016 for SPINS-CMH data.

## set pint_dir to be the pint outputs
pint_dir <- "../data/PINT_outputs_s8_10-6-12/"

## reading in the qced_sublists csv to get the sublists
qced_sublists <- read.csv("../phenotypic/NEWallSubjects_completeData3_DM_not_sexmatched.csv")
pheno <- qced_sublists %>%
  mutate(Site = factor(site, levels = c(1,2,3),
                       labels = c("CMH","ZHH","COBRE")) ,
         DX = factor(DX_GROUP, level = c(1,2), labels = c('SSD', 'Ctrl')),
         Sex = factor(sex.x),
         Edu = if_else(is.na(educationCode), 
                       true = mean(educationCode, na.rm = F), 
                       false = educationCode))

##load the more descriptive list of the vertices...not we may want to change a few based on these results...
Yeo7_80verts <- read.csv("~/code/ciftify/ciftify/data/PINT/Yeo7_2011_80verts.csv")
```

## Some functions we're using

```{r}
## functions
read_subject_meants <- function(subid, pint_dir, vertex_type) {
  meants <- read.csv(file.path(pint_dir,
                               subid, 
                               paste(subid, vertex_type, "meants.csv", sep="_")),
                     header=FALSE)
  return(meants)
}


load_all_subject_matrices <- function(subids, myedgenames, pint_dir, 
                                      vertex_type) {
  ## use these parameters to set up a blank dataframe to hold all the correlations
  theZs <- as.data.frame(cbind("subid" = subids, 
                               matrix(numeric(), 
                                      nrow = length(subids),
                                      ncol = numedges,
                                      dimnames = list(1:length(subids),
                                                      myedgenames))))
  theZs[ ,2:ncol(theZs)] <- numeric(nrow(theZs)*(ncol(theZs)-1))
  
  ## now correlate everyones ts and write the correlations to a massive data frame
  for (i in 1:nrow(theZs)) {
    ## get the subid from the dataframe and read in the meants
    meants <- read_subject_meants(theZs$subid[i], pint_dir, vertex_type)
    
    ## correlate and graph
    cormat <- cor(t(meants))
    g<-graph_from_adjacency_matrix(cormat,mode="upper", 
                                   weighted=T, diag=F)
    # take the egde list as a vector
    thecorrs <- E(g)$weight
    
    # apply the Z transform (so we can do stats)
    theseZ <- atanh(thecorrs) 
    
    # save the output to the data.frame
    theZs[i,2:ncol(theZs)] <- theseZ
  }
  return(theZs)
}

make_corrplot <-function(data, attrtoplot, graph_title) {
  forplot <- as.data.frame(data) 
  forplot <- forplot %>% separate(Edge, into = c("V1", "V2"), sep = '\\.')
  g <- graph_from_data_frame(forplot, directed=F)
  g.mat <- get.adjacency(g, attr=attrtoplot)
  corrplot(as.matrix(g.mat), 
           is.corr = F, tl.cex = 0.3, tl.col = "black",
           title = graph_title)
}

#new circle graph function
radian.rescale <- function(x, start=0, direction=1) {
  c.rotate <- function(x) (x + start) %% (2 * pi) * direction
  c.rotate(scales::rescale(x, c(0, 2 * pi), range(x)))
}

draw_circle_graph <- function(data, Yeo7_80verts) {
  CircleOrder <- as.character(Yeo7_80verts$SHORTNAME)
  CircleOrder <- c(CircleOrder[75:length(CircleOrder)], CircleOrder[1:74])
  g <- graph.data.frame(data, directed = F)
  Yeo7_80verts$wnetname <- substr(Yeo7_80verts$SHORTNAME,3,6)
  Yeo7_80verts$Vhex <- NA
  Yeo7_80verts$Vhex[Yeo7_80verts$NETWORK==2] <- "#781286"
  Yeo7_80verts$Vhex[Yeo7_80verts$NETWORK==3] <- "#00760E"
  Yeo7_80verts$Vhex[Yeo7_80verts$NETWORK==4] <- "#C43AFA"
  Yeo7_80verts$Vhex[Yeo7_80verts$NETWORK==5] <- "#4682B4"
  Yeo7_80verts$Vhex[Yeo7_80verts$NETWORK==6] <- "#E69422"
  Yeo7_80verts$Vhex[Yeo7_80verts$NETWORK==7] <- "#CD3E3A"
  V(g)$color <- Yeo7_80verts$Vhex
  g$layout <- layout_in_circle(g,order = CircleOrder)
  lab.locs <- radian.rescale(x=1:80, direction=-1, start=0)
  d <-as.matrix(dist(g$layout, method = "euclidean", 
                     upper = TRUE, diag = TRUE, p = 2))
  gdist <-graph_from_adjacency_matrix(as.matrix(dist(g$layout, method = "euclidean", 
                                                     upper = TRUE, diag = TRUE, p = 2)),
                                      mode="upper", weighted=T, diag=F)
  dist.df <- cbind(data,E(gdist)$weight)
  dist.df$scaledD <- (dist.df$`E(gdist)$weight`/(-2)) + 1
  dist.df$scaleDc <- dist.df$scaledD
  dist.df$netcombo <- paste(substr(dist.df$V1,1,2), substr(dist.df$V2,1,2),sep =".")
  switchlist <- c("DA.VI", "DA.SM")
  dist.df$scaleDc[dist.df$netcombo %in% switchlist] <- dist.df$scaleD[dist.df$netcombo %in% switchlist] * (-1)
  
  plt <- plot(g, edge.width=E(g)$logp*5, 
       edge.curved=dist.df$scaleDc, 
       edge.color = E(g)$posneg,
       vertex.size = 3.5,
       vertex.label.family="sans",
       vertex.label.font=1,
       vertex.label.cex = 0.5,
       vertex.label = Yeo7_80verts$wnetname,
       vertex.label.dist=0.5,
       vertex.label.degree=lab.locs,
       vertex.label.color = V(g)$color)
  return(plt)
}

```

### Load the ivertex and tvertex Zs for all subjects

```{r}
## read in one examplar to get some parameters we want
meants1 <- read_subject_meants(qced_sublists$subid[1], pint_dir, 'ivertex')
## sort the meants into the order from the new naming scheme
names(meants1) <- paste0("TR_",1:ncol(meants1))
Yeo_meants <- cbind(Yeo7_80verts,meants1)

## correlate and graph from the first one
cormat <- cor(t(select(Yeo_meants,starts_with("TR_"))))
rownames(cormat) <- Yeo_meants$SHORTNAME
colnames(cormat) <- Yeo_meants$SHORTNAME
g<-graph_from_adjacency_matrix(cormat,mode="upper", 
                               weighted=T, diag=F, 
                               add.rownames = "code")
g.df <- as.data.frame(get.edgelist(g), names=T)

# take the egde list as a vector
thecorrs <- E(g)$weight
    
# apply the Z transform (so we can do stats)
theseZ <- atanh(thecorrs) 

## get two variables of interest.. edgenames and the number of edges
myedgenames <- paste(g.df[ ,1],g.df[ ,2],sep=".") ## the V1.V2 name
numedges <- length(myedgenames)                   ## the number of edges


## get all the Z's from ivertex
theZs_ivertex <- load_all_subject_matrices(as.character(qced_sublists$subid),
                                           myedgenames, pint_dir, 'ivertex') 
                                          

## merge all those correlations back with the demographics
alldemZs_i_m <- merge(pheno,theZs_ivertex,by="subid") %>%
    gather_("Edge", "FC", myedgenames)


## get all the Z's from tvertex
theZs_tvertex <- load_all_subject_matrices(as.character(qced_sublists$subid),
                                           myedgenames, pint_dir, 
                                           'tvertex')

## merge all those correlations back with the demographics
alldemZs_t_m <- merge(pheno,theZs_tvertex,by="subid")  %>%
  gather_("Edge", "FC", myedgenames)  


```

# Run the linear model for all Template and Personalized FC edges

Note: one trick here (but justified by Saba's thesis and Graces work, is to add a DX*Sex interation term ot all models)

```{r}
FC_lmres <- bind_rows("Template" = alldemZs_t_m, 
          "Personalized" = alldemZs_i_m, 
          .id = "vertex_type") %>%
  group_by(Edge, vertex_type) %>%
  do(tidy(lm(FC ~ DX*Sex + mean_fd + poly(age,2) + Edu + Site,.))) %>%
  ungroup() %>% group_by(term, vertex_type) %>%
  mutate(p.FDR = p.adjust(p.value, method = "fdr")) %>%
  ungroup
```

## looking at all FDR corrected results..

Most results are for the linear effect of age..but there is one significant effect of Diagnosis in the FP network (contralateral partietal areas..)

```{r}
FC_lmres %>%
  filter(term %in% c("DXCtrl","Sex2", "DXCtrl:Sex2","age")) %>%
  arrange(p.value) %>%
  select(Edge, vertex_type, term, statistic, p.value, p.FDR) %>%
  filter(p.value < 0.001) %>%
  kable()
```

```{r}
library(stringr)
FC_lmres %>%
  filter(term == "DXCtrl") %>%
  mutate(nets = str_c(str_sub(Edge, 1,2), str_sub(Edge, 6,8))) %>%
  ggplot(aes(x=statistic, fill = vertex_type)) + geom_density(alpha = 0.5) + 
  geom_vline(xintercept = 0) + facet_wrap(~nets)
```
```{r}
FC_lmres_net <- bind_rows("Template" = alldemZs_t_m, 
          "Personalized" = alldemZs_i_m, 
          .id = "vertex_type") %>%
  mutate(nets = str_c(str_sub(Edge, 1,2), str_sub(Edge, 5,8), str_sub(Edge, 11))) %>% 
  group_by(subid, vertex_type, nets) %>%
  summarise(meanZ = mean(FC)) %>%
  inner_join(pheno, by = "subid") %>%
  ungroup() %>%
  group_by(nets, vertex_type) %>%
  do(tidy(lm(meanZ ~ DX*Sex + mean_fd + poly(age,2) + Edu + Site,.))) %>%
  ungroup() %>% group_by(term, vertex_type) %>%
  mutate(p.FDR = p.adjust(p.value, method = "fdr")) %>%
  ungroup

```

```{r}
kable(FC_lmres_net %>% filter(term %in% "DXCtrl"))
```


# Looking at the significant effect in FP network

```{r}
bind_rows("Template" = alldemZs_t_m, 
          "Personalized" = alldemZs_i_m, .id = "vertex_type") %>%
    filter(Edge == "FPP1L.FPP1R") %>%
  ggplot(aes(x = DX, y = FC , by =Sex,  color = Sex)) +
    geom_boxplot() +
    facet_grid(~vertex_type) +
    labs(y = "Correlation (Z) of FPP1L.FPP1R")
```


## all the model terms within this edge

```{r}
FC_lmres %>%
filter(Edge == "FPP1L.FPP1R") %>%
  select(Edge, vertex_type, term, statistic, p.value, p.FDR) %>%
  kable()
```

## splitting the plot by Site


```{r}
bind_rows("Template" = alldemZs_t_m, 
          "Personalized" = alldemZs_i_m, .id = "vertex_type") %>%
    filter(Edge == "FPP1L.FPP1R") %>%
  ggplot(aes(x = DX, y = FC , by =Sex,  color = Sex)) +
    geom_boxplot() + 
    facet_grid(Site~vertex_type) +
    labs(y = "Correlation (Z) of FPP1L.FPP1R")
```


# building circle plots of the subthreshold effects

```{r}
#' threshold and draw circle shot
thresholded_circle_plot <- function(tidylm, p_thres, filter_term, filter_vtype) {
forgraph <- tidylm %>%
  filter(term == filter_term,
         vertex_type ==filter_vtype) %>%
  separate(Edge, into = c("V1","V2"), sep = "\\.") %>%
  select(V1, V2, statistic, p.value) %>%
  mutate(thres_statistic = if_else(p.value <= p_thres, 
                                   true = statistic, 
                                   false= 0)) %>%
  mutate(posneg = case_when(.$thres_statistic < -0.01 ~ 1,
                            .$thres_statistic > 0.01 ~ 2,
                            TRUE ~ NA_real_),
        log_p = case_when(.$p.value <= p_thres ~ log(.$p.value),
                          TRUE ~ 0)) 
  plot <- draw_circle_graph(forgraph, Yeo7_80verts)
  return(plot)
}
```

```{r}
thresholded_circle_plot(FC_lmres, p_thres = 0.001, 
                              filter_term = "DXCtrl", filter_vtype = "Template")
thresholded_circle_plot(FC_lmres, p_thres = 0.001, 
                              filter_term = "DXCtrl", filter_vtype = "Personalized")

```

```{r}
thresholded_circle_plot(FC_lmres, p_thres = 0.001, 
                              filter_term = "DXCtrl:Sex2", filter_vtype = "Template")
thresholded_circle_plot(FC_lmres, p_thres = 0.001, 
                              filter_term = "DXCtrl:Sex2", filter_vtype = "Personalized")
```
```{r}
thresholded_circle_plot(FC_lmres, p_thres = 0.001, 
                              filter_term = "Sex2", filter_vtype = "Template")
thresholded_circle_plot(FC_lmres, p_thres = 0.001, 
                              filter_term = "Sex2", filter_vtype = "Personalized")
```
```{r}
thresholded_circle_plot(FC_lmres, p_thres = 0.001, 
                              filter_term = "age", filter_vtype = "Template")
thresholded_circle_plot(FC_lmres, p_thres = 0.001, 
                              filter_term = "age", filter_vtype = "Personalized")
```


### New stuff for graph theory - 30 July 2017

```{r}

# New stuff for graph theory - 30 July 2017

## merge all those correlations back with the demographics
alldemZs_i_m <- merge(qced_sublists,theZs_ivertex,by="subid")
alldemZs_t_m <- merge(qced_sublists,theZs_tvertex,by="subid")


# Averaging z-scores for each diagnostic group for the i vertices
aggregate_all_i <- aggregate(alldemZs_i_m[, 14:3173], list(alldemZs_i_m$DX_GROUP), mean)

# Subsetting into patients and controls so I can make separate adjacency matrices
aggregate_all_i_SCZ <- aggregate_all_i[1,2:3161]
aggregate_all_i_HC <- aggregate_all_i[2,2:3161]

# Averaging z-scores for each diagnostic group for the t vertices
aggregate_all_t <- aggregate(alldemZs_t_m[, 14:3173], list(alldemZs_t_m$DX_GROUP), mean)

# Subsetting into patients and controls so I can make separate adjacency matrices
aggregate_all_t_SCZ <- aggregate_all_t[1,2:3161]
aggregate_all_t_HC <- aggregate_all_t[2,2:3161]

## Thresholding the values here
# aggregate_all_i_SCZ[aggregate_all_i_SCZ < 0.60] <- 0

# Creating an iGraph - will change weights to represent different diagnostic groups 
g<-graph_from_adjacency_matrix(cormat,mode="upper", 
                               weighted=T, diag=F, 
                               add.rownames = "code")

# Color coding the networks
V(g)$color <- ifelse(substr(V(g)$name, 0,2) == "DM", "#CD3E3A", (ifelse(substr(V(g)$name, 0,2) == "EX", "#E69422", (ifelse(substr(V(g)$name, 0,2) == "SA", "#C43AFA", (ifelse(substr(V(g)$name, 0,2) == "VI", "#781286", (ifelse(substr(V(g)$name, 0,2) == "DA", "#00760E", "#4682B4")))))))))

# Creating labels for the vertices - just the lobe and the hemisphere as the network is color-coded
V(g)$label_name <- substr(V(g)$name, 3,5)

# Creating adjacency matrices for i vertices
aggregate_all_i_SCZ_data <- as.matrix(aggregate_all_i_SCZ)
aggregate_all_i_SCZ_data <- as.vector(aggregate_all_i_SCZ_data)
E(g)$weight <- aggregate_all_i_SCZ_data
SCZ_i_vertex <- get.adjacency(g, type="both", attr="weight", sparse=FALSE)

aggregate_all_i_HC_data <- as.matrix(aggregate_all_i_HC)
aggregate_all_i_HC_data <- as.vector(aggregate_all_i_HC_data)
E(g)$weight <- aggregate_all_i_HC_data
HC_i_vertex <- get.adjacency(g, type="both", attr="weight", sparse=FALSE)

# Creating adjacency matrices for t vertices
aggregate_all_t_SCZ_data <- as.matrix(aggregate_all_t_SCZ)
aggregate_all_t_SCZ_data <- as.vector(aggregate_all_t_SCZ_data)
E(g)$weight <- aggregate_all_t_SCZ_data
SCZ_t_vertex <- get.adjacency(g, type="both", attr="weight", sparse=FALSE)

aggregate_all_t_HC_data <- as.matrix(aggregate_all_t_HC)
aggregate_all_t_HC_data <- as.vector(aggregate_all_t_HC_data)
E(g)$weight <- aggregate_all_t_HC_data
HC_t_vertex <- get.adjacency(g, type="both", attr="weight", sparse=FALSE)

# # Writing the adjacency matrices to use in MATLAB
# write.csv(SCZ_i_vertex, "..//projects/saba/HCP_fMRI_SCZ/new_analyses_20170412/FC_analyses/Graph_Theory/SCZ_i_vertex.csv")
# write.csv(HC_i_vertex, "/projects/saba/HCP_fMRI_SCZ/new_analyses_20170412/FC_analyses/Graph_Theory/HC_i_vertex.csv")
# write.csv(SCZ_t_vertex, "/projects/saba/HCP_fMRI_SCZ/new_analyses_20170412/FC_analyses/Graph_Theory/SCZ_t_vertex.csv")
# write.csv(HC_t_vertex, "/projects/saba/HCP_fMRI_SCZ/new_analyses_20170412/FC_analyses/Graph_Theory/HC_t_vertex.csv")


#plot.igraph(g,vertex.label=V(g)$name,layout=layout.fruchterman.reingold, edge.color="black",edge.width=E(g)$weight)

hist(aggregate_all_i_SCZ_data, main="SCZ: i-vertex", xlab = "z-scores", xlim=c(-0.5, 3.0))
hist(aggregate_all_i_HC_data, main="HC: i-vertex", xlab = "z-scores", xlim=c(-0.5, 3.0))
hist(aggregate_all_t_SCZ_data, main="SCZ: t-vertex", xlab = "z-scores", xlim=c(-0.5, 3.0))
hist(aggregate_all_t_HC_data, main="HC: t-vertex", xlab = "z-scores", xlim=c(-0.5, 3.0))


# Reassigning weights to the igraph
E(g)$weight <- aggregate_all_i_SCZ_data
E(g)$weight <- aggregate_all_i_HC_data
E(g)$weight <- aggregate_all_t_SCZ_data
E(g)$weight <- aggregate_all_t_HC_data

# Using 0.65 for i-vertex, and 0.35 for t-vertex
# Using 0.2 for i-vertex, and 0.19 for t-vertex

g_few=delete.edges(g, which(E(g)$weight <=0.20))
plot(g_few, vertex.label=V(g_few)$label_name)

g_few_vert=delete.vertices(g_few,which(degree(g_few)<15))
plot(g_few_vert, vertex.label=V(g_few_vert)$label_name)
sum(degree(g_few))
degree(g_few)
betweenness(g_few_vert)
degree(g_few_vert)

# Ratio of the number of edges and the number of possible edges
edge_density(g_few)

## rm the extra object in memory
#rm(cormat, meants1, theZs_tvertex, theZs_ivertex, Yeo_meants, g)
```

