---
title: "Sub-cortical Cortical Stats Split by Hemisphere"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    keep_md: yes
---

# Sub-cortical Cortical Stats Left and Right

This analysis tries to combine timeseries data from PINT outputs with subcortical timeseries to ask two questions

1. "External" validation of PINT. If PINT is indeed helping us better target meaningful resting state networks than we should see "cleaner" patterns of between the PINT output cortical ROIs and parcels of the subcortical structure that have been associated with these networks in literature.
   + i.e. connectivity of the cortical ROIS with "expected" subcortical parcel should increae and correlation with other parcels should decrease after PINT.
   
2. To interograte SSD related differences in Cortical-Subcortical connectivity - and to see if they persist after PINT.

Some work Ji (in prep) kinda suggests that there might be differences between left and right subcortical structures. AND spliting the left and right seemed to make more sense for whole brain correlations (because our cortical nodes have a hemisphere). So in this analysis have separate left and right ROIs

```{r}
library(tidyverse)
library(broom)
library(knitr)
library(tableone)
library(cowplot)
library(ggridges)
```


## The paths to data

```{r setting paths}
output_base <- '../data/ciftify_fmriprep/'

Yeo7_2011_80verts <- read_csv("../templates/Yeo7_2011_80verts.csv",
                              col_types = c(
                                hemi = col_character(),
                                tvertex = col_integer(),
                                LRpairs = col_integer(),
                                roiidx = col_integer(),
                                NETWORK = col_integer(),
                                LOBE = col_character(),
                                SHORTNAME = col_character(),
                                x = col_integer(),
                                y = col_integer(),
                                z = col_integer()
                              ))

YeoNet_colours = list("VI" = "#781286",
                      "SM" = "#4682B4",
                      "DA" = "#00760E", 
                      "VA" = "#C43AFA",
                      "DM" = "#CD3E3A", 
                      "FP" = "#E69422")

pheno <- read_csv('../phenotypic/20181118_pheno_qapass.csv') %>%
  drop_na(DX)
```




# Code for reading in all the timeseries..


A table that describes the current expected subortical files

```{r define-subcotical-files}
# a tibble table to specify the subcortical meants files that were generated
YeoNet_subcort_list <- c('VI','SM','DA','VA', 'LI','FP','DM')
```

These functions are for reading timeseries files

```{r subcortical file reading functions}

#' read a meants file generated by PINT of ciftify_meants
#'
#' @param filepath the full path to the file
#'
#' @return a dataframe where rows are rois and colums are timepoints
read_meants_csv <- function(filepath) {
   meants <-read_csv(filepath, 
                     col_names = FALSE,
                     col_types = c(.default = col_double()))
   return(meants)
}

#' Read the contents of a csv generated by PINT
#'
#' @param outputprefix The prefix to the PINT outputs
#' @param vertex_type "pvertex" or "tvertex"
#' @param projectname the outputdir
#' @param output_dir the basepath of the pint outputs
#'
#' @return a dataframe of the _meants.csv contents
read_pint_meants <- function(outputprefix, vertex_type, projectname, output_dir) {
  expected_filepath <- file.path(output_dir, projectname, "out",'ciftify_PINT', 
                           str_c(outputprefix, '_desc-clean_bold_', 
                                 vertex_type, '_meants.csv'))
  meants = read_meants_csv(expected_filepath)
  return(meants)
}

#' Read the contents of a csv generated by PINT coord volume spheres
#'
#' @param outputprefix The prefix to the PINT outputs
#' @param projectname the outputdir
#' @param output_dir the basepath of the pint outputs
#'
#' @return a dataframe of the _meants.csv contents
read_pint_volsphere_meants <- function(outputprefix, projectname, output_dir) {
  expected_filepath <- file.path(output_dir, projectname, "out",'ciftify_meants', 
                           str_c(outputprefix, '_desc-volcleansm8_atlas-6mmYeo780_timeseries.csv'))
  meants = read_meants_csv(expected_filepath) 
  return(meants)
}

#' Read the contents of a subcortical csv
#' expample file path is sub-CMHHEF011_ses-01_task-rest_acq-CMH_run-01_bold_desc-cleansm0_atlas-7RSN_roi-Lcerebellum_timeseries.csv
#'
#' @param outputprefix the prefix to the pint outputfile
#' @param hemi The hemisphere "L" or "R"
#' @param subregion region "thalamus", "stiatum", "cerebellum"
#' @param output_dir the basepath of the output data
#' @param projectname the project name inside the output dir
#'
#' @return a dataframe of the _meants.csv contents
read_subcortical_hemi_meants <- function(outputprefix, hemi, subregion, projectname, output_dir) {
  expected_filepath <- file.path(output_dir, projectname, "out",'ciftify_meants', 
                           str_c(outputprefix,
                                 '_desc-cleansm0_atlas-7RSN_roi-', 
                                 hemi, subregion, '_timeseries.csv'))
  meants = read_meants_csv(expected_filepath)
  return(meants)
}

#' Contructs the expected output prefix from subid session and func_base
#'
#' @param subid The subject identifier
#' @param sessid The session identifier (or null)
#' @param func_base The functional file prefix
#'
#' @return an output prefix string for the filenames
construct_output_prefix <- function(subid, sessid, func_base) {
  prefix <- if_else(is.na(sessid),
                    file.path(subid, str_c(subid, '_', func_base)),
                    file.path(subid, sessid, 
                      str_c(subid, '_', sessid, '_', func_base)))
  return(prefix)
}

#' get func_base from pint summary filename
#'
#' @param subid The subject identifier
#' @param sessid The session identifier (or null)
#' @param func_base The functional file prefix
#'
#' @return an output prefix string for the filenames
get_func_base_from_pint_summary_filename <- function(filename, subject, session) {
  func_base <- if_else(is.na(session), 
                       filename %>%
                         str_replace(str_c(subject, "_"), '') %>%
                         str_replace('_desc-clean_bold_summary.csv',''),
                       filename %>%
                         str_replace(subject, '') %>%
                         str_replace(session, '') %>% 
                         str_replace('__','') %>%
                         str_replace('_desc-clean_bold_summary.csv',''))
  return(func_base)
}

```


This reads all files and generate PINT to subcortical correlation values for a given subject

```{r read and correlated function}

the_subcortical_guide <- tribble(
 ~subcort_hemi, ~subcort_ROI, ~subcort_NET,
 "L", "thalamus", c('VI','SM','DA','VA', 'FP','DM'),
 "L", "striatum", c('SM','DA','VA', 'LI','FP','DM'),
 "L", "cerebellum", c('VI','SM','DA','VA', 'LI','FP','DM'),
 "R", "thalamus", c('VI','SM','DA','VA', 'LI','FP','DM'),
 "R", "striatum", c('VI','SM','DA','VA', 'LI','FP','DM'),
 "R", "cerebellum", c('VI','SM','DA','VA', 'LI','FP','DM')) %>%
  unnest()


#' read all fMRI timeseries data for one subject and correlates PINT ROIs with subcortex
#'
#' @param out_prefix the prefix to the pint outputfile
#' @param outputbase the path to the pint output directory
#' @param projectname the path to sub-study project (dataset)
#' @param Yeo7_2011_80verts as data frame describing the PINT ROIs 
#'
#' @return a dataframe (graph style) of PINT ROI to subcortical correlations
subject_subcort_corrs <- function(out_prefix, projectname, 
                                  outputbase, Yeo7_2011_80verts) {
  
  # read the pint meants files
  pvertex_meants <- read_pint_meants(out_prefix, 'pvertex', 
                                     projectname, outputbase)
  tvertex_meants <- read_pint_meants(out_prefix, 'tvertex',
                                     projectname, outputbase)
  volsphere_meants <- read_pint_volsphere_meants(out_prefix,
                                                 projectname, output_base)
  # read the subcortical meants files
  thalamus_L_meants <- read_subcortical_hemi_meants(out_prefix,
                                                    "L","thalamus", 
                                                    projectname, outputbase)
  striatum_L_meants <- read_subcortical_hemi_meants(out_prefix,
                                                    "L","striatum",
                                                    projectname, outputbase)
  cerebellum_L_meants <- read_subcortical_hemi_meants(out_prefix,
                                                      "L", "cerebellum",
                                                      projectname, outputbase)
  thalamus_R_meants <- read_subcortical_hemi_meants(out_prefix,
                                                    "R","thalamus",
                                                    projectname, outputbase)
  striatum_R_meants <- read_subcortical_hemi_meants(out_prefix,
                                                    "R","striatum", 
                                                    projectname, outputbase)
  cerebellum_R_meants <- read_subcortical_hemi_meants(out_prefix,
                                                      "R", "cerebellum", 
                                                      projectname, outputbase)
  
  # prepare to bind
  subcort_meants <- bind_rows(thalamus_L_meants, striatum_L_meants, cerebellum_L_meants,
                              thalamus_R_meants, striatum_R_meants, cerebellum_R_meants)
  
  # correlate the pvertex timeseries with the subcortical data
  pvertex_subcortcorr <- as.data.frame(cor(t(subcort_meants), t(pvertex_meants)))
  names(pvertex_subcortcorr) <- Yeo7_2011_80verts$SHORTNAME
  pvertex_result <- the_subcortical_guide %>% 
    bind_cols(pvertex_subcortcorr) %>%
    gather(PINT_ROI, pvertex_corr, -subcort_ROI, -subcort_NET, -subcort_hemi)
  
  # correlated the tvertex timeseries with the subcortical data
  tvertex_subcortcorr <- as.data.frame(cor(t(subcort_meants), t(tvertex_meants)))
  names(tvertex_subcortcorr) <- Yeo7_2011_80verts$SHORTNAME
  tvertex_result <- the_subcortical_guide %>% 
    bind_cols(tvertex_subcortcorr) %>%
    gather(PINT_ROI, tvertex_corr, -subcort_ROI, -subcort_NET, -subcort_hemi)
  
  # correlated the volume timeseries with the subcortical data
  tvolume_subcortcorr <- as.data.frame(cor(t(subcort_meants), t(volsphere_meants)))
  names(tvolume_subcortcorr) <- Yeo7_2011_80verts$SHORTNAME
  tvolume_result <- the_subcortical_guide %>% 
    bind_cols(tvolume_subcortcorr) %>%
    gather(PINT_ROI, tvolume_corr, -subcort_ROI, -subcort_NET, -subcort_hemi)
  
  # combine pvertex and tvertex and return
  subresult <- pvertex_result %>%
    inner_join(tvertex_result, by = c("PINT_ROI", "subcort_ROI", "subcort_NET", "subcort_hemi")) %>%
    inner_join(tvolume_result, by = c("PINT_ROI", "subcort_ROI", "subcort_NET", "subcort_hemi"))
  return(subresult)
}

#' reads in all the timeseries files for one participant
#' note that Yeo&_2011_80verts and output_base are pulled from the global env
run_read_subject_subcort_corrs <- function(out_prefix, projectname) {
  df <-subject_subcort_corrs(out_prefix, projectname,
                             output_base, Yeo7_2011_80verts)
  return(df)
}

# run_read_subject_subcort_corrs(subcort_outputlist$subid[1])

```


### This reads all the subcortical files it can find

Write a func_base and outputprefix cols into the pheno file for the file reading step

```{r}
pheno <- pheno %>%
  mutate(func_base = get_func_base_from_pint_summary_filename(filename,subject, session), 
         outputprefix = construct_output_prefix(subject, session, func_base)) 
```

a litle chunck I use to test if test if the reader is working...

```{r eval = FALSE}
run_read_subject_subcort_corrs(pheno$outputprefix[1], pheno$dataset[1])
```


```{r read all the data}

all_subcort_results <- pheno %>%
  select(subject, outputprefix, dataset) %>%
  mutate(subcort_corrs = map2(outputprefix, dataset,
                              ~run_read_subject_subcort_corrs(.x, .y)))
```

```{r cache-subcort-Rdata, eval = FALSE}
save(all_subcort_results, file = "03_subcort_results_cache.Rdata")
```

```{r load-cached-results, eval=FALSE}
load("03_subcort_results_cache.Rdata")
```

### merge with the phenotypic data

```{r merge with pheno and clean}
results_pheno <- all_subcort_results %>%
  inner_join(pheno, by = "subject") %>%
  unnest() %>%
  mutate(YeoNet = str_sub(PINT_ROI, 1,2),
         hemisphere = str_sub(PINT_ROI, 5,5)) %>%
  mutate(conn_type = if_else(YeoNet == subcort_NET, "same_net", "diff_net"),
         YeoNet = factor(YeoNet, levels = c("VI", "SM", "DA", "VA", "FP", "DM")),
         subcort_NET = factor(subcort_NET, levels = c("VI", "SM", "DA", "VA", "FP", "DM", "LI"))) %>%
  select(subject, PINT_ROI, subcort_ROI, subcort_NET,subcort_hemi, 
         pvertex_corr, tvertex_corr, tvolume_corr,
         DX, Sex, fd_mean, Age, Site, Scanner, Age_pt, fd_mean_pt,  
         YeoNet, hemisphere, conn_type) 

```





## make a subject table from resuts pheno


```{r report_demographics}
library(tableone)
therealtable1 <- CreateTableOne(
  strata = c("DX", "Site"),
  vars = c("Age", "Sex", "fd_mean", "fd_perc"),
  data = filter(results_pheno, PINT_ROI=="DMP1L",subcort_ROI=="thalamus", subcort_NET=="VA", subcort_hemi == "L")
)
tabMat <- print(therealtable1, quote = FALSE, noSpaces = TRUE, printToggle = FALSE)
kable(tabMat)

```

```{r report_demographics-pooled}
library(tableone)
therealtable1 <- CreateTableOne(
  vars = c("Age", "Sex", "DX", "fd_mean", "fd_perc"),
  data = filter(results_pheno, PINT_ROI=="DMP1L",subcort_ROI=="thalamus", subcort_NET=="VA", subcort_hemi == "L")
)
tabMat <- print(therealtable1, quote = FALSE, noSpaces = TRUE, printToggle = FALSE)
kable(tabMat)

```


# Is PINT "focusing" cortical subcortical connectivity

```{r plotting-PINT-change-matrix, fig.width=6, fig.height=8}
table1 <- results_pheno %>%
  mutate(corr_diff = pvertex_corr - tvertex_corr) %>%
  gather(corr_type, rval, pvertex_corr, tvertex_corr, tvolume_corr) %>%
  group_by(corr_type, YeoNet, subcort_ROI, subcort_NET) %>%
  summarise(n = n(),
            Mean = mean(rval),
            SD = sd(rval)) 
  
ggplot(table1, aes(y = YeoNet, x = subcort_NET, fill = Mean)) + 
  geom_tile() +
  scale_fill_distiller(breaks = c(-0.5,0.5), type = "div", palette = 5) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  facet_grid(subcort_ROI~corr_type) 

```
functions to help re-annotated the function axes

```{r function-to-plot-annots}
#' sets some the main variables to factors to more descriptive labels
add_corrtype_and_subcortROI_columns <- function(data) {
  result <- data %>%
    mutate(corrtype = factor(corr_type, levels = c('tvolume_corr','tvertex_corr','pvertex_corr'),
                           labels = c("Volume Template", "Surface Template", "Surface Personalized")),
         subcortROI = factor(subcort_ROI, 
                             levels = c("striatum", "thalamus", "cerebellum"),
                             labels = c("Striatum", "Thalamus", "Cerebellum"))) 
  return(result)
}

#'drop VI DA and LI network from resutls
drop_VI_DA_LI <- function(data) {
  result <- data %>%
    filter(subcort_NET != "VI",
         subcort_NET != "DA",
         subcort_NET != "LI",
         YeoNet != "VI",
         YeoNet != "DA") 
  return(result)
}
```


```{r plotting-PINT-change-matrix-reduce, fig.width=7.5, fig.height=7.5}

table1 %>%
  drop_VI_DA_LI() %>%
  add_corrtype_and_subcortROI_columns() %>%
ggplot(aes(y = YeoNet, x = subcort_NET, fill = Mean)) + 
  geom_tile() +
  geom_text(aes(label = sprintf('%3.2f',Mean))) +
  scale_fill_distiller(breaks = c(-0.5,0.5), type = "div", palette = 5) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  facet_grid(corrtype~subcortROI) +
  labs(y = "Cortical RSN Network", x = "Subcortical Subregion")

```


```{r plotting-PINT-change-matrix-hemi, fig.width=12, fig.height=12}
table1 <- results_pheno %>%
  mutate(corr_diff = pvertex_corr - tvertex_corr) %>%
  gather(corr_type, rval, pvertex_corr, tvertex_corr, tvolume_corr) %>%
  group_by(corr_type, YeoNet, hemisphere, subcort_ROI, subcort_NET, subcort_hemi) %>%
  summarise(n = n(),
            Mean = mean(rval),
            SD = sd(rval)) 

table1 %>%
  drop_VI_DA_LI() %>%
  add_corrtype_and_subcortROI_columns() %>%
ggplot(aes(y = YeoNet, x = subcort_NET, fill = Mean)) + 
  geom_tile() +
  geom_text(aes(label = sprintf('%3.2f',Mean))) +
  scale_fill_distiller(breaks = c(-0.5,0.5), type = "div", palette = 5) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  facet_grid(subcortROI*subcort_hemi~corrtype*hemisphere) +
  labs(y = "Cortical RSN Network", x = "Subcortical Subregion")  
```

We see in the above figure that the Yeo 7 Network connectivity strongly shows the expected pattern in the cerebeullum. 

Lower evidence is seen in the striatum and thalamus, although there is a faint increase across the diagonal for the SM, VA and DM especially

```{r paired-ttests-of-PINT-effect, fig.heigth = 2, fig.width=8}
net_means <- results_pheno %>%
  mutate(corr_diff = pvertex_corr - tvertex_corr) %>%
  group_by(YeoNet, subcort_ROI, subcort_NET, conn_type, subject) %>%
  summarise(netmean_pvertex = mean(pvertex_corr),
            netmean_tvertex = mean(tvertex_corr),
            netmean_tvolume = mean(tvolume_corr)) %>%
  ungroup()

net_means_pint_t <- net_means %>%
  group_by(YeoNet, subcort_ROI, subcort_NET) %>%
  do(tidy(t.test(.$netmean_pvertex, .$netmean_tvertex, paired = TRUE))) %>%
  ungroup() %>% mutate(p_FDR = p.adjust(p.value, method = "fdr"))

net_means_pint_t %>%
  ungroup() %>%
  mutate(sig = if_else(p_FDR < 0.05, '*', NA_character_) ) %>%
  drop_VI_DA_LI() %>%
  mutate(subcortROI = factor(subcort_ROI, 
                           levels = c("striatum", "thalamus", "cerebellum"),
                           labels = c("Striatum", "Thalamus", "Cerebellum"))) %>%
ggplot(aes(x = YeoNet, y = subcort_NET, fill = statistic)) + 
  geom_tile(color = "black", na.rm = TRUE) +
  geom_point(aes(shape = sig), na.rm = TRUE) +
  scale_fill_distiller(breaks = c(-10,10), type = "div", palette = 5) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  facet_wrap(~subcortROI)
```
Here we plot the paired t-stat camparing personalized to template, we see a very strong increase in correlation along the diagonal (i.e. with the hypothesized regions) and decreases on the off-dignonal (i.e. decreased connectivity with the other network's parcels)

```{r}
net_means_vpint_t <- net_means %>%
  group_by(YeoNet, subcort_ROI, subcort_NET) %>%
  do(tidy(t.test(.$netmean_pvertex, .$netmean_tvolume, paired = TRUE))) %>%
  ungroup() %>% mutate(p_FDR = p.adjust(p.value, method = "fdr"))

net_means_vpint_t %>%
  ungroup() %>%
  mutate(sig = if_else(p_FDR < 0.05, '*', NA_character_) ) %>%
  drop_VI_DA_LI() %>%
  mutate(subcortROI = factor(subcort_ROI, 
                           levels = c("striatum", "thalamus", "cerebellum"),
                           labels = c("Striatum", "Thalamus", "Cerebellum"))) %>%
ggplot(aes(x = YeoNet, y = subcort_NET, fill = statistic)) + 
  geom_tile(color = "black", na.rm = TRUE) +
  geom_point(aes(shape = sig), na.rm = TRUE) +
  scale_fill_distiller(breaks = c(-10,10), type = "div", palette = 5) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  facet_wrap(~subcortROI)
```

# trying to calculate an vs off diagonal term

In the above table to calcuculated the "focussing" effect as the change (in on person) between in connectivity with the expected parcel subtracted by the change in connectivity from other regions.

Below we plot these values against zero

```{r net-focus-tstats}
net_focus <- net_means %>%
  ungroup() %>%
  mutate(pint_diff = netmean_pvertex - netmean_tvertex,
         vpint_diff = netmean_pvertex - netmean_tvolume,
         surf_diff = netmean_tvertex - netmean_tvolume) %>%
  group_by(subject, subcort_ROI, YeoNet, conn_type) %>%
  summarise(nets_avg_pint_diff = mean(pint_diff),
            nets_avg_vpint_diff = mean(vpint_diff),
            nets_avg_surf_diff = mean(surf_diff)
            ) %>%
  ungroup() %>%
  gather(comparison, nets_avg, nets_avg_pint_diff, nets_avg_vpint_diff, nets_avg_surf_diff) %>%
  spread(conn_type, nets_avg) %>%
  mutate(focus_effect = same_net - diff_net)

net_focus %>%
  ungroup() %>%
  group_by(subcort_ROI, YeoNet, comparison) %>%
  do(tidy(t.test(.$focus_effect))) %>%
  kable()
```

Another (maybe better) way to test this is to show calculate the "focusing" value in individual subjects THAN compute how this number changes with PINT. Let try that..

```{r sub-focus-tstats}
subject_focus <- net_means %>%
  drop_VI_DA_LI() %>%
  gather(vertex_type, nets_avg, netmean_pvertex, netmean_tvertex, netmean_tvolume) %>%
  ungroup(subcort_NET) %>%
  group_by(subject, subcort_ROI, YeoNet, vertex_type, conn_type) %>%
  summarise(nets_type_avg = mean(nets_avg)) %>%
  spread(conn_type, nets_type_avg) # %>%
  # ungroup() %>%
  # mutate(focus_effect = same_net - diff_net)

subject_focus %>%
  ungroup() %>%
  group_by(subcort_ROI, YeoNet, vertex_type) %>%
  do(tidy(t.test(.$same_net, .$diff_net, paired = TRUE))) %>%
  mutate(cohenD = statistic/sqrt(parameter + 1)) %>%
  kable()
```
```{r eval = FALSE}
source('../R/R_rainclouds.R')
```
```{r eval = FALSE}
subject_focus %>%
  gather(nettype, corZ, diff_net, same_net) %>%
  filter(subcort_ROI == "cerebellum", YeoNet == "VA") %>%
  ggplot(aes(x = vertex_type, y = corZ, fill = nettype)) +
  geom_flat_violin(aes(fill = nettype), position = position_nudge(x = .1, y = 0),
                   adjust = 1.5, trim = FALSE, alpha = .5, colour = NA) +
  geom_point(aes(x = as.numeric(vertex_type)-.15, y = corZ, colour = nettype),
             position = position_jitter(width = .05), size = 1, shape = 20) +
  geom_boxplot(aes(x = vertex_type, y = corZ, fill = nettype), outlier.shape = NA, alpha = .5, width = .1, colour = "black")+
  geom_hline(yintercept = 0) +
  scale_colour_brewer(palette = "Dark2")+
  scale_fill_brewer(palette = "Dark2")+
  coord_flip() +
  ggtitle(str_c("cerebellum to cortical VA"))
```
```{r}
# library(ggridges)
samediff_subcort_raincloud <- function(data, this_subcort_ROI, this_YeoNet, no_ticks = TRUE) {
plt <- data %>%
  mutate(corrtype = factor(vertex_type, levels = c('netmean_pvertex', 'netmean_tvertex', 'netmean_tvolume'),
                           labels = c("Surface Personalized", "Surface Template", "Volume Template"))) %>%
  gather(nettype, gvalue, diff_net, same_net) %>%
  filter(subcort_ROI == this_subcort_ROI, YeoNet == this_YeoNet) %>% 
  ungroup() %>%
  ggplot(aes(y = corrtype, x = gvalue, fill = nettype, colour = nettype)) +
  geom_density_ridges(
    #jittered_points = TRUE, position = "raincloud",
    alpha = 0.5, scale = 2,
    quantile_lines = TRUE, quantiles = 2
  ) +
  geom_vline(xintercept = 0) +
  scale_colour_manual(values = c("#808080", YeoNet_colours[[this_YeoNet]])) +
  scale_fill_manual(values = c("#808080", YeoNet_colours[[this_YeoNet]])) +
  scale_x_continuous(limits = c(-0.5, 0.6)) +
  labs(y = NULL,
       x = NULL) +
  theme(legend.position='none')
if (no_ticks==TRUE) {
  plt <- plt + theme(axis.title.x=element_blank(),
        axis.text.x=element_blank())
} else {
  plt <- plt + labs(x = "Subcortical-Cortical Correlation (Z)")
}
return(plt)
  
}

focus_subcort_raincloud <- function(data, this_subcort_ROI, this_YeoNet, no_ticks = TRUE) {
plt <- data %>%
  mutate(corrtype = factor(vertex_type, levels = c('netmean_pvertex', 'netmean_tvertex', 'netmean_tvolume'),
                           labels = c("Surface Personalized", "Surface Template", "Volume Template"))) %>%
  mutate(focus = same_net - diff_net) %>%
  filter(subcort_ROI == this_subcort_ROI, YeoNet == this_YeoNet) %>% 
  ungroup() %>%
  ggplot(aes(y = corrtype, x = focus)) +
  geom_density_ridges(
    # jittered_points = TRUE, position = "raincloud",
    alpha = 0.5, scale = 2,
    quantile_lines = TRUE, quantiles = 2,
    fill = YeoNet_colours[[this_YeoNet]],
    colour = YeoNet_colours[[this_YeoNet]]
  ) +
  geom_vline(xintercept = 0) +
  scale_x_continuous(limits = c(-0.3, 0.6)) +
  labs(y = NULL,
       x = NULL) +
  theme(legend.position='none', 
        axis.title.y=element_blank(),
        axis.text.y=element_blank()) 
if (no_ticks==TRUE) {
  plt <- plt + theme(axis.title.x=element_blank(),
        axis.text.x=element_blank())
} else {
  plt <- plt + labs(x = "Same - Diff.")
}
return(plt)
  
}

samediff_plus_focus_rainclouds <- function(subject_focus, this_subcort, this_YeoNet, no_ticks = TRUE) {
plt <- plot_grid(samediff_subcort_raincloud(subject_focus, this_subcort, this_YeoNet, no_ticks), 
                         focus_subcort_raincloud(subject_focus, this_subcort, this_YeoNet, no_ticks), 
                         rel_widths = c(2,1))
return(plt)
}

subcortical_raincloud <- function(subject_focus, this_subcort) {
DM <- samediff_plus_focus_rainclouds(subject_focus, this_subcort, "DM")
FP <- samediff_plus_focus_rainclouds(subject_focus,this_subcort, "FP")
VA <- samediff_plus_focus_rainclouds(subject_focus,this_subcort, "VA")
SM <- samediff_plus_focus_rainclouds(subject_focus,this_subcort, "SM", no_ticks = FALSE)
title <- ggdraw() + draw_label(this_subcort, fontface='bold')
plt <- plot_grid(title, DM, FP, VA, SM, ncol = 1, rel_heights = c(0.5, 1, 1, 1, 1.5))
return(plt)
}
```

```{r stiatum-rainclouds}
subcortical_raincloud(subject_focus, "striatum")
```

```{r thalamus-rainclouds}
subcortical_raincloud(subject_focus, "thalamus")
```
```{r cerebellum-raincloud}
subcortical_raincloud(subject_focus, "cerebellum")
```








```{r}

subject_focus %>%
  ungroup() %>% 
  mutate(focus_effect = same_net - diff_net) %>%
  select(subject, YeoNet, vertex_type, subcort_ROI, focus_effect) %>%
  spread(vertex_type, focus_effect) %>%
  group_by(subcort_ROI, YeoNet) %>%
  do(tidy(t.test(.$netmean_pvertex, .$netmean_tvertex, paired = TRUE))) %>%
  mutate(cohenD = statistic/sqrt(parameter + 1)) %>%
  kable()
```
```{r}
subject_focus %>%
  ungroup() %>% 
  mutate(focus_effect = same_net - diff_net) %>%
  select(subject, YeoNet, vertex_type, subcort_ROI, focus_effect) %>%
  spread(vertex_type, focus_effect) %>%
  group_by(subcort_ROI, YeoNet) %>%
  do(tidy(t.test(.$netmean_tvertex, .$netmean_tvolume, paired = TRUE))) %>%
  mutate(cohenD = statistic/sqrt(parameter + 1)) %>%
  kable()
```





Recreating the DM plot from the poster to double check

```{r DM-cerebellum-plot-part1}

net_means <- results_pheno %>%
  ungroup() %>%
  group_by(YeoNet, subcort_ROI, subcort_NET, subject) %>%
  summarise(netmean_pvertex = mean(pvertex_corr),
            netmean_tvertex = mean(tvertex_corr),
            pint_diff = netmean_pvertex - netmean_tvertex) 

pint_diff_sub_DM <- net_means %>%
  ungroup() %>% 
  filter(YeoNet == "DM", subcort_ROI == "cerebellum") %>%
  select(subject, subcort_NET, pint_diff) %>%
  spread(subcort_NET, pint_diff) %>%
  mutate(overall_pint_diff = DM - (SM + VA + FP + DA)/4,
         x_val = '') %>%
  select(subject, overall_pint_diff, x_val) %>%
  ggplot(aes(y = overall_pint_diff, x = x_val)) +
    geom_boxplot(outlier.shape = NA) +
    geom_jitter(alpha = 0.3, color = YeoNet_colours$DM, fill = "grey") +
    geom_hline(yintercept = 0) + 
    labs(y = "Change in correlation after PINT", x = "Cerebellum DM - Others") +
  scale_y_continuous(limits = c(-0.3, 0.3))

DM_submeans_plot <- net_means %>%
  mutate(is_DM = if_else(subcort_NET == 'DM', TRUE, FALSE),
         SubCortNET = factor(subcort_NET, levels = c("DM", "SM", "DA", "VA", "FP"))) %>%
  filter(subcort_ROI == "cerebellum", !is.na(SubCortNET), YeoNet == "DM") %>%
  ggplot(aes(y = pint_diff, x = SubCortNET, color = is_DM)) +
  geom_boxplot(color = "black", outlier.shape = NA) + 
  geom_jitter(alpha = 0.3) +
  geom_hline(yintercept = 0) +
  scale_color_manual(values = c('black',YeoNet_colours$DM)) +
  labs(y = "Change in correlation after PINT", color = NULL, x = "Subregion of Cerebellum") +
  theme(legend.position = "none") +
  scale_y_continuous(limits = c(-0.3, 0.3))

# DM_brain_pic <- ggdraw + draw_image('DM_striatum_pic.png')

plot_grid(pint_diff_sub_DM, DM_submeans_plot, rel_widths = c(1,2.5))
```

Also the VA Striatum one

```{r VA-cerebellum-plot}

pint_diff_sub_VA <- net_means %>%
  ungroup %>% 
  filter(YeoNet == "VA", subcort_ROI == "cerebellum") %>%
  select(subject, subcort_NET, pint_diff) %>%
  spread(subcort_NET, pint_diff) %>%
  mutate(overall_pint_diff = VA - (SM + DM + FP + DA)/4,
         x_val = '') %>%
  select(subject, overall_pint_diff, x_val) %>%
  ggplot(aes(y = overall_pint_diff, x = x_val)) +
    geom_boxplot(outlier.shape = NA) +
    geom_jitter(alpha = 0.3, color = YeoNet_colours$VA, fill = "grey") +
    geom_hline(yintercept = 0) + 
    labs(y = "Change in correlation after PINT", x = "Cerebellum VA - Others") +
  scale_y_continuous(limits = c(-0.3, 0.3))

VA_submeans_plot <- net_means %>%
  mutate(is_VA = if_else(subcort_NET == 'VA', TRUE, FALSE),
          SubCort_ROI = factor(subcort_NET, 
                               levels = c("VA", "DA", 'SM', 'FP', "DM"))) %>%
  filter(YeoNet == "VA", 
         subcort_ROI == "cerebellum",
         subcort_NET %in% c('SM', "VA", "DM", 'FP', "DA")) %>%
  ggplot(aes(y = pint_diff, x = SubCort_ROI, color = is_VA)) +
  geom_boxplot(color = "black", outlier.shape = NA) + 
  geom_jitter(alpha = 0.3) +
  geom_hline(yintercept = 0) +
  scale_color_manual(values = c('black', YeoNet_colours$VA)) +
  labs(y = "Change in correlation after PINT", color = NULL, x = "Subregion of Cerebellum") +
  theme(legend.position = "none") +
  scale_y_continuous(limits = c(-0.3, 0.3))

# DM_brain_pic <- ggdraw + draw_image('DM_striatum_pic.png')

plot_grid(pint_diff_sub_VA, VA_submeans_plot, rel_widths = c(1,2.5))
```

```{r FP-straitum-plot}

pint_diff_sub_FP <- net_means %>%
  ungroup %>% 
  filter(YeoNet == "FP", subcort_ROI == "striatum") %>%
  select(subject, subcort_NET, pint_diff) %>%
  spread(subcort_NET, pint_diff) %>%
  mutate(overall_pint_diff = FP - (SM + DM + VA)/3,
         x_val = '') %>%
  select(subject, overall_pint_diff, x_val) %>%
  ggplot(aes(y = overall_pint_diff, x = x_val)) +
    geom_boxplot(outlier.shape = NA) +
    geom_jitter(alpha = 0.3, color = YeoNet_colours$FP, fill = "grey") +
    geom_hline(yintercept = 0) + 
    labs(y = "Change in correlation after PINT", x = "Striatum VA - Others") +
  scale_y_continuous(limits = c(-0.3, 0.3))

FP_submeans_plot <- net_means %>%
  mutate(is_FP = if_else(subcort_NET == 'FP', TRUE, FALSE),
          SubCort_ROI = factor(subcort_NET, 
                               levels = c('FP', "DM", 'SM', "VA"))) %>%
  filter(YeoNet == "FP", 
         subcort_ROI == "striatum",
         subcort_NET %in% c('SM', "VA", "DM", 'FP')) %>%
  ggplot(aes(y = pint_diff, x = SubCort_ROI, color = is_FP)) +
  geom_boxplot(color = "black", outlier.shape = NA) + 
  geom_jitter(alpha = 0.3) +
  geom_hline(yintercept = 0) +
  scale_color_manual(values = c('black', YeoNet_colours$FP)) +
  labs(y = "Change in correlation after PINT", color = NULL, x = "Subregion of Striatum") +
  theme(legend.position = "none") +
  scale_y_continuous(limits = c(-0.3, 0.3))

# DM_brain_pic <- ggdraw + draw_image('DM_striatum_pic.png')

plot_grid(pint_diff_sub_FP, FP_submeans_plot, rel_widths = c(1,2.5))
```

```{r VA-straitum-plot}

pint_diff_sub_VA <- net_means %>%
  ungroup %>% 
  filter(YeoNet == "VA", subcort_ROI == "striatum") %>%
  select(subject, subcort_NET, pint_diff) %>%
  spread(subcort_NET, pint_diff) %>%
  mutate(overall_pint_diff = VA - (SM + DM + FP)/3,
         x_val = '') %>%
  select(subject, overall_pint_diff, x_val) %>%
  ggplot(aes(y = overall_pint_diff, x = x_val)) +
    geom_boxplot(outlier.shape = NA) +
    geom_jitter(alpha = 0.3, color = YeoNet_colours$VA, fill = "grey") +
    geom_hline(yintercept = 0) + 
    labs(y = "Change in correlation after PINT", x = "Striatum VA - Others") +
  scale_y_continuous(limits = c(-0.3, 0.3))

VA_submeans_plot <- net_means %>%
  mutate(is_VA = if_else(subcort_NET == 'VA', TRUE, FALSE),
          SubCort_ROI = factor(subcort_NET, 
                               levels = c("VA", 'SM', 'FP', "DM"))) %>%
  filter(YeoNet == "VA", 
         subcort_ROI == "striatum",
         subcort_NET %in% c('SM', "VA", "DM", 'FP')) %>%
  ggplot(aes(y = pint_diff, x = SubCort_ROI, color = is_VA)) +
  geom_boxplot(color = "black", outlier.shape = NA) + 
  geom_jitter(alpha = 0.3) +
  geom_hline(yintercept = 0) +
  scale_color_manual(values = c('black', YeoNet_colours$VA)) +
  labs(y = "Change in correlation after PINT", color = NULL, x = "Subregion of Striatum") +
  theme(legend.position = "none") +
  scale_y_continuous(limits = c(-0.3, 0.3))

# DM_brain_pic <- ggdraw + draw_image('DM_striatum_pic.png')

plot_grid(pint_diff_sub_VA, VA_submeans_plot, rel_widths = c(1,2.5))
```
```{r SM-thalamus-plot}

pint_diff_sub_SM <- net_means %>%
  ungroup %>% 
  filter(YeoNet == "SM", subcort_ROI == "thalamus") %>%
  select(subject, subcort_NET, pint_diff) %>%
  spread(subcort_NET, pint_diff) %>%
  mutate(overall_pint_diff = SM - (VA + DM + FP + DA)/4,
         x_val = '') %>%
  select(subject, overall_pint_diff, x_val) %>%
  ggplot(aes(y = overall_pint_diff, x = x_val)) +
    geom_boxplot(outlier.shape = NA) +
    geom_jitter(alpha = 0.3, color = YeoNet_colours$SM, fill = "grey") +
    geom_hline(yintercept = 0) + 
    labs(y = "Change in correlation after PINT", x = "Striatum VA - Others") +
  scale_y_continuous(limits = c(-0.3, 0.3))

SM_submeans_plot <- net_means %>%
  mutate(is_SM = if_else(subcort_NET == 'SM', TRUE, FALSE),
          SubCort_ROI = factor(subcort_NET, 
                               levels = c("SM", "VA", "DA",'FP', "DM"))) %>%
  filter(YeoNet == "SM", 
         subcort_ROI == "thalamus",
         subcort_NET %in% c('SM', "VA", "DA","DM", 'FP')) %>%
  ggplot(aes(y = pint_diff, x = SubCort_ROI, color = is_SM)) +
  geom_boxplot(color = "black", outlier.shape = NA) + 
  geom_jitter(alpha = 0.3) +
  geom_hline(yintercept = 0) +
  scale_color_manual(values = c('black', YeoNet_colours$SM)) +
  labs(y = "Change in correlation after PINT", color = NULL, x = "Subregion of Thalamus") +
  theme(legend.position = "none") +
  scale_y_continuous(limits = c(-0.3, 0.3))

# DM_brain_pic <- ggdraw + draw_image('DM_striatum_pic.png')

plot_grid(pint_diff_sub_SM, SM_submeans_plot, rel_widths = c(1,2.5))
```


## Plotting the PINT effect separately in SSD and controls

Note that the circle denotes an uncorrected p<0.05

```{r plotting-PINT-effect-separately-by-DX-all}
net_means_byDX <- results_pheno %>%
  mutate(corr_diff = pvertex_corr - tvolume_corr) %>%
  group_by(YeoNet, subcort_ROI, subcort_NET, subject, DX) %>%
  summarise(netmean_pvertex = mean(pvertex_corr),
            netmean_tvertex = mean(tvertex_corr)) %>%
  ungroup() %>%
  group_by(YeoNet, subcort_ROI, subcort_NET, DX) %>%
  do(tidy(t.test(.$netmean_pvertex, .$netmean_tvertex, paired = TRUE)))

net_means_byDX %>%
  ungroup() %>%
  mutate(sig = if_else(p.value < 0.005, '*', NA_character_) ) %>%
ggplot(aes(x = YeoNet, y = subcort_NET, fill = statistic)) + 
  geom_tile(color = "black", na.rm = TRUE) +
  geom_point(aes(shape = sig), na.rm = TRUE) +
  scale_fill_gradient2() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  facet_grid(subcort_ROI ~ DX)
```
```{r plotting-PINT-effect-separately-by-DX}
net_means_byDX <- results_pheno %>%
  mutate(corr_diff = pvertex_corr - tvolume_corr) %>%
  group_by(YeoNet, subcort_ROI, subcort_NET, subject, DX) %>%
  summarise(netmean_pvertex = mean(pvertex_corr),
            netmean_tvertex = mean(tvertex_corr)) %>%
  ungroup() %>%
  group_by(YeoNet, subcort_ROI, subcort_NET, DX) %>%
  do(tidy(t.test(.$netmean_pvertex, .$netmean_tvertex, paired = TRUE)))

net_means_byDX %>%
  ungroup() %>%
  mutate(sig = if_else(p.value < 0.005, '*', NA_character_) ) %>%
  filter(subcort_NET != "VI",
       subcort_NET != "DA",
       subcort_NET != "LI",
       YeoNet != "VI",
       YeoNet != "DA") %>%
  mutate(subcortROI = factor(subcort_ROI, 
                           levels = c("striatum", "thalamus", "cerebellum"),
                           labels = c("Striatum", "Thalamus", "Cerebellum"))) %>%
ggplot(aes(x = YeoNet, y = subcort_NET, fill = statistic)) + 
  geom_tile(color = "black", na.rm = TRUE) +
  geom_point(aes(shape = sig), na.rm = TRUE) +
  scale_fill_gradient2() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  facet_grid(DX ~ subcortROI)
```


## running model again with sex interaction

```{r running-subcortical-model-with-sex-interaction}
library(knitr)

DX_lm_model <- results_pheno %>%
  gather(vertex_type, corZ, pvertex_corr, tvertex_corr, tvolume_corr) %>%
  filter(Age > 17, Age < 51) %>%
  filter(subcort_ROI %in% c("cerebellum", "striatum")) %>%
  group_by(vertex_type, subcort_ROI, subcort_NET, PINT_ROI) %>%
  do(tidy(lm(corZ ~ DX + Sex + fd_mean_pt + Age_pt + Scanner,.))) %>%
  select(vertex_type, subcort_ROI, subcort_NET, PINT_ROI, term, statistic, p.value) %>%
  ungroup() %>%
  group_by(term) %>%
  mutate(p_FDR = p.adjust(p.value, method = "fdr")) %>%
  arrange(p.value)

DX_lm_model %>% 
  filter(term %in% c("DXSSD")) %>%
  filter(p_FDR < 0.05) %>%
  filter(vertex_type == "pvertex_corr") %>%
  arrange(subcort_NET) %>%
  kable()
```



```{r}
ggplot(pheno, aes(x = Age, fill = Scanner)) + geom_density(alpha = 0.2)
```
```{r}
ggplot(pheno, aes(x = Age_pt, fill = Scanner)) + geom_density(alpha = 0.2)
```

```{r}
ggplot(pheno, aes(x = fd_mean, fill = Site)) + geom_density(alpha = 0.2) + facet_wrap(~ DX, ncol = 1)
```

```{r}
DX_lm_model %>% 
  mutate(pos_neg = if_else(statistic > 0, "pos", "neg")) %>%
  filter(subcort_NET != "VI",
       subcort_NET != "DA",
       subcort_NET != "LI") %>%
  group_by(vertex_type, pos_neg) %>%
  filter(term %in% c("DXSSD")) %>%
  filter(p_FDR < 0.05) %>%
  count()
```
```{r}
DX_lm_model %>% 
  group_by(vertex_type) %>%
  filter(term %in% c("DXSSD")) %>%
  count()
```


```{r DX-effect-of-PINT-scatter, fig.height=4, fig.width=4}
DX_lm_model %>%
  ungroup() %>%
  filter(term %in% c("DXSSD")) %>%  
  filter(subcort_NET != "VI",
       subcort_NET != "DA",
       subcort_NET != "LI") %>%
  select(vertex_type, subcort_ROI, subcort_NET, PINT_ROI, statistic) %>%
  spread(vertex_type, statistic) %>%
  ggplot(aes(x = pvertex_corr, y = tvolume_corr)) +
  geom_point() +
  geom_smooth(method = "lm", color = "blue") +
  geom_abline(slope = 1, intercept = 0) +
  labs(x = "Personalized (after)", y = "Volume Template",
       title = "Effect of SSD Diagnosis (t-tstat)")
```

```{r DX-effect-of-PINT-density, fig.height=4, fig.width=4}
DX_lm_model %>%
  filter(term %in% c("DXSSD")) %>%
  filter(subcort_NET != "VI",
       subcort_NET != "DA",
       subcort_NET != "LI") %>%
  select(vertex_type, subcort_ROI, subcort_NET, PINT_ROI, statistic) %>%
  spread(vertex_type, statistic) %>%
  filter(abs(pvertex_corr) > 3.0) %>%
  mutate(abs_tstat_change = abs(pvertex_corr) - abs(tvolume_corr)) %>%
  ggplot(aes(x = abs_tstat_change)) + geom_histogram() + geom_vline(xintercept = 0)
```
```{r DX-effect-of-PINT-density-fill, fig.height=4, fig.width=6}
DX_lm_model %>%
  filter(term %in% c("DXSSD")) %>%
  filter(subcort_NET != "VI",
       subcort_NET != "DA",
       subcort_NET != "LI") %>%
  select(vertex_type, subcort_ROI, subcort_NET, PINT_ROI, statistic) %>%
  ggplot(aes(x = statistic, fill = vertex_type)) + geom_density(alpha = 0.2) + geom_vline(xintercept = 0)
```
```{r DX-effect-of-PINT-scatter-net, fig.height=4, fig.width=6}
DX_lm_model %>%
  filter(term %in% c("DXSSD")) %>%
  filter(subcort_NET != "VI",
       subcort_NET != "DA",
       subcort_NET != "LI") %>%
  select(vertex_type, subcort_ROI, subcort_NET, PINT_ROI, statistic) %>%
  mutate(YeoNet = substr(PINT_ROI, 1,2)) %>%
  ggplot(aes(x = statistic, fill = vertex_type)) + geom_density(alpha = 0.2) + geom_vline(xintercept = 0) +
  facet_wrap(~ YeoNet)
```
```{r DX-effect-of-PINT-scatter-motion, fig.height=4, fig.width=6}
DX_lm_model %>%
  filter(term %in% c("fd_mean_pt")) %>%
  filter(subcort_NET != "VI",
       subcort_NET != "DA",
       subcort_NET != "LI") %>%
  select(vertex_type, subcort_ROI, subcort_NET, PINT_ROI, statistic) %>%
  mutate(YeoNet = substr(PINT_ROI, 1,2)) %>%
  ggplot(aes(x = statistic, fill = vertex_type)) + geom_density(alpha = 0.2) + geom_vline(xintercept = 0) +
  facet_wrap(~ YeoNet)
```

```{r}
DX_lm_model %>%
  filter(term %in% c("DXSSD")) %>%
  filter(subcort_NET != "VI",
       subcort_NET != "DA",
       subcort_NET != "LI") %>%
  select(vertex_type, subcort_ROI, subcort_NET, PINT_ROI, statistic) %>%
  spread(vertex_type, statistic) %>%
  mutate(YeoNet = substr(PINT_ROI, 1,2)) %>%
  ggplot(aes(x = pvertex_corr, y = tvolume_corr)) +
  geom_point(aes(color=subcort_NET)) +
  geom_smooth(method = "lm", color = "blue") +
  geom_abline(slope = 1, intercept = 0) +
#  scale_color_manual(values = YeoNet_colours) +
  facet_grid(subcort_NET~YeoNet)
```


```{r}
DX_lm_model %>%
  filter(term %in% c("DXSSD")) %>%
  filter(subcort_NET != "VI",
       subcort_NET != "DA",
       subcort_NET != "LI") %>%
  select(vertex_type, subcort_ROI, subcort_NET, PINT_ROI, statistic) %>%
  spread(vertex_type, statistic) %>%
  mutate(YeoNet = substr(PINT_ROI, 1,2)) %>%
  ggplot(aes(x = pvertex_corr, y = tvolume_corr)) +
  geom_point(aes(color=subcort_NET)) +
  geom_smooth(method = "lm", color = "blue") +
  geom_abline(slope = 1, intercept = 0) +
#  scale_color_manual(values = YeoNet_colours) +
  facet_wrap(~YeoNet)
```

```{r}
DX_lm_net_model <- results_pheno %>%
  filter(subcort_NET != "VI",
       subcort_NET != "DA",
       subcort_NET != "LI") %>%
  group_by(YeoNet, subcort_ROI, subcort_NET, hemisphere, subcort_hemi, 
           subject, DX, Age_pt, Sex, Scanner, fd_mean_pt, Age) %>%
  summarise(netmean_pvertex = mean(pvertex_corr),
            netmean_tvertex = mean(tvertex_corr),
            netmean_tvolume = mean(tvolume_corr)) %>%
  gather(vertex_type, netmean_corZ, netmean_pvertex, netmean_tvertex, netmean_tvolume) %>%
  filter(Age > 17, Age < 51) %>%
  
  group_by(vertex_type, subcort_ROI, subcort_NET, YeoNet) %>%
  do(tidy(lm(netmean_corZ ~ DX + Sex + fd_mean_pt + Age_pt + Scanner,.))) %>%
  select(vertex_type, subcort_ROI, YeoNet, term, statistic, p.value) %>%
  ungroup() %>%
  group_by(term) %>%
  mutate(p_FDR = p.adjust(p.value, method = "fdr")) %>%
  arrange(p.value)

DX_lm_net_model %>%
  filter(term %in% c("DXSSD"), 
  p_FDR < 0.06,
  vertex_type == "netmean_pvertex") %>%
  arrange(subcort_NET, subcort_ROI) %>%
  kable()
```
```{r, fig.width = 12, fig.height = 3}
DX_lm_net_model %>%
  ungroup() %>%
  filter(term %in% c("DXSSD"),
         vertex_type == "netmean_pvertex") %>%
  select(YeoNet, subcort_NET, subcort_ROI, statistic) %>%
  ggplot(aes(x = subcort_ROI, y = subcort_NET, fill = statistic)) +
  geom_tile() +
  geom_text(aes(label = sprintf('%3.2f',statistic))) +
  scale_fill_distiller(breaks = c(-10,10), type = "div", palette = 5) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  facet_wrap(~ YeoNet, nrow = 1) 
```

```{r}
DX_lm_net_model %>%
  ungroup() %>%
  filter(term %in% c("DXSSD")) %>%
  select(vertex_type, subcort_ROI, subcort_NET, YeoNet, statistic) %>%
  spread(vertex_type, statistic) %>%
  ggplot(aes(x = netmean_pvertex, y = netmean_tvolume)) +
  geom_point(aes(color=YeoNet)) +
  geom_abline(slope = 1, intercept = 0) 
```

```{r, fig.height=12}
sig_edges <- DX_lm_net_model %>%
  ungroup() %>%
  filter(term %in% c("DXSSD"), p_FDR < 0.1, vertex_type == "netmean_pvertex") %>%
  select(subcort_ROI, subcort_NET, YeoNet) %>% 
  unite(edgename, YeoNet, subcort_ROI, subcort_NET)

thing_cluster <- results_pheno %>%
  filter(DX == "SSD") %>%
  select(subject, YeoNet, subcort_ROI, subcort_NET, pvertex_corr) %>%
  group_by(subject, YeoNet, subcort_ROI, subcort_NET) %>%
  summarise(netmean_pvertex = mean(pvertex_corr)) %>%
  ungroup() %>%
  unite(edgename, YeoNet, subcort_ROI, subcort_NET) %>%
  filter(edgename %in% sig_edges$edgename) %>%
  spread(edgename, netmean_pvertex) %>%
  select(-subject) %>%
  cor(.)

library(corrplot)

corrplot(thing_cluster, order = "hclust")
```
## build super cools scatter elipse plots

```{r}
edgewise_cors_wide <- results_pheno %>%
  select(subject, DX, Site, YeoNet, subcort_ROI, subcort_NET, pvertex_corr) %>%
  group_by(subject, DX, Site, YeoNet, subcort_ROI, subcort_NET) %>%
  summarise(netmean_pvertex = mean(pvertex_corr)) %>%
  ungroup() %>%
  unite(edgename, YeoNet, subcort_ROI, subcort_NET) %>%
  spread(edgename, netmean_pvertex) 

plot_DX_scatter_elipse <- function(df, x, y, facet_by_site = FALSE) {
  xvar <- enquo(x)
  yvar <- enquo(y)
 plt <- ggplot(data = df, 
               aes(x = !!xvar, y = !!yvar, color = DX)) +
  geom_point() +
  stat_ellipse() +
  scale_color_manual(values = c("grey20","red"))
 if ( facet_by_site == TRUE ) {
   plt <- plt + facet_wrap(~Site, ncol = 4)
 }
 return(plt)
}

# Marginal densities along x axis
plot_DX_scatter_elipsed <- function(df, x, y) {
  #the tidy eval ness
  xvar <- enquo(x)
  yvar <- enquo(y)
  # make the main scatte bit using above
  main_scatter <-  ggplot(data = df, 
               aes(x = !!xvar, y = !!yvar, color = DX)) +
  geom_point(alpha = 0.7, size = 0.7) +
  stat_ellipse() +
  scale_color_manual(values = c("grey20","red"))

  xdens <- axis_canvas(main_scatter, axis = "x")+
    geom_density(data = df, aes(x = !!xvar, fill = DX),
              alpha = 0.5, size = 0.2) +
    scale_fill_manual(values = c("grey20","red"))

  ydens <- axis_canvas(main_scatter, axis = "y", coord_flip = TRUE)+
    geom_density(data = df, aes(x = !!yvar, fill = DX),
                alpha = 0.5, size = 0.2) +
  scale_fill_manual(values = c("grey20","red")) +
  coord_flip()
  
  #putting the peices together
  p1 <- insert_xaxis_grob(main_scatter, xdens, grid::unit(.2, "null"), position = "top")
  p2<- insert_yaxis_grob(p1, ydens, grid::unit(.2, "null"), position = "right")
  return(p2)
}
```

```{r , fig.height=3, fig.width = 8}
plot_DX_scatter_elipse(edgewise_cors_wide, x = FP_cerebellum_DM, y = FP_thalamus_DM, facet_by_site = TRUE)
```

```{r , fig.height=3, fig.width = 4}
ggdraw(plot_DX_scatter_elipsed(edgewise_cors_wide, x = FP_cerebellum_DM, y = FP_thalamus_DM))
```


```{r fig.height = 3, fig.width = 4}
ggdraw(plot_DX_scatter_elipsed(edgewise_cors_wide, x = VI_thalamus_DM, y = FP_thalamus_DM))
```
```{r fig.height = 3, fig.width = 4}
ggdraw(plot_DX_scatter_elipsed(edgewise_cors_wide, x = VI_striatum_FP, y = FP_striatum_FP))

```

```{r fig.height = 3, fig.width = 4}

ggdraw(plot_DX_scatter_elipsed(edgewise_cors_wide, x = DM_striatum_FP, y = FP_striatum_FP))

 
```
```{r fig.height = 3, fig.width = 10}


plot_DX_scatter_elipse(edgewise_cors_wide, x = DM_striatum_FP, y = FP_striatum_FP, facet_by_site = TRUE)
 
```
```{r fig.height = 3, fig.width = 4}
ggdraw(plot_DX_scatter_elipsed(edgewise_cors_wide, x = DM_striatum_FP, y = VA_striatum_SM))

```










```{r, fig.height=12}
thing_cluster2 <- results_pheno %>%
  filter(Site == "CMH", DX == "SSD") %>%
  select(subject, YeoNet, subcort_ROI, subcort_NET, pvertex_corr) %>%
  group_by(subject, YeoNet, subcort_ROI, subcort_NET) %>%
  summarise(netmean_pvertex = mean(pvertex_corr)) %>%
  ungroup() %>%
  unite(edgename, YeoNet, subcort_ROI, subcort_NET) %>%
  filter(edgename %in% sig_edges$edgename) %>%
  spread(edgename, netmean_pvertex) %>%
  select(-subject) %>%
  t(.) %>%
  cor(.)

library(corrplot)

corrplot(thing_cluster2, order = "hclust")
```

```{r}
DX_lm_model_bySite <- results_pheno %>%
  group_by(YeoNet, subcort_ROI, subcort_NET,  
           subject, DX, Age_pt, Scanner, Sex, Site, fd_mean_pt, Age) %>%
  summarise(netmean_pvertex = mean(pvertex_corr),
            netmean_tvertex = mean(tvertex_corr)) %>%
  gather(vertex_type, netmean_corZ, netmean_pvertex, netmean_tvertex) %>%
  filter(Age > 17, Age < 51) %>%
  group_by(vertex_type, subcort_ROI, subcort_NET, YeoNet, Site) %>%
  do(tidy(lm(netmean_corZ ~ DX + Sex + fd_mean_pt + poly(Age_pt,2),.))) %>%
  select(vertex_type, subcort_ROI, Site, YeoNet, term, statistic, p.value) %>%
  ungroup() %>%
  group_by(term) %>%
  mutate(p_FDR = p.adjust(p.value, method = "fdr")) %>%
  arrange(p.value)
```
```{r}
kable(DX_lm_model_bySite %>% filter(term %in% c("DXSSD"), 
                                    subcort_NET == "SM", YeoNet == "SM",
                                    vertex_type == "netmean_pvertex") %>%
        arrange(subcort_ROI))
```
```{r}
kable(DX_lm_model_bySite %>% 
        filter(term %in% c("DXSSD"), 
                                    subcort_NET == "VA", YeoNet == "VA",
                                    vertex_type == "netmean_pvertex") %>%
        arrange(subcort_ROI))
```
```{r}
kable(DX_lm_model_bySite %>% filter(term %in% c("DXSSD"), 
                                    subcort_NET == "DM", YeoNet == "DM",
                                    vertex_type == "netmean_pvertex")%>%
        arrange(subcort_ROI))
```


##################################### Edit from Here! ################################################################



```{r VA-DX-effect-striatum-figure, fig.height=5, fig.width = 6}
fig1 <- results_pheno %>%
  group_by(YeoNet, subcort_ROI, subcort_NET, 
           subject, DX, Age, Sex, Site, fd_mean) %>%
  filter(Age < 45, Age > 17) %>%
  summarise(Personalized = mean(pvertex_corr),
            Template = mean(tvertex_corr)) %>%
  filter(YeoNet == "VA", subcort_NET == "VA", subcort_ROI == "striatum") %>%
  ggplot(aes(y = Personalized, x = DX, color = DX)) + 
  geom_boxplot(outlier.shape = NA) + 
  geom_dotplot(binaxis = 'y', stackdir = 'center', binwidth = 0.01, alpha = 0.5) +
  scale_color_brewer(palette = "Dark2") +
  facet_wrap( ~ Site, ncol = 4) +
  labs(y = "Striatum- Cortex Resting State Correlation (Z)",
       title="Striatum-Cortical VA Network")

#ggsave(fig1, filename = 'VA_results.png',height = 8, width = 5)

fig1
```
```{r SM-DX-effect-thalamus-figure, fig.height=5, fig.width = 6}
fig1 <- results_pheno %>%
  group_by(YeoNet, subcort_ROI, subcort_NET, 
           subject, DX, Sex, Site, fd_mean) %>%
  summarise(Personalized = mean(pvertex_corr),
            Template = mean(tvertex_corr)) %>%
  filter(YeoNet == "SM", subcort_NET == "SM", subcort_ROI == "thalamus") %>%
  ggplot(aes(y = Personalized, x = DX, color = DX)) + 
  geom_boxplot(outlier.shape = NA) + 
  geom_dotplot(binaxis = 'y', stackdir = 'center', binwidth = 0.01, alpha = 0.5) +
  scale_color_brewer(palette = "Dark2") +
  facet_wrap( ~ Site, ncol = 4) +
  labs(y = "Thalamus- Cortex Resting State Correlation (Z)",
       title="Thalamus-Cortical SM Network")

#ggsave(fig1, filename = 'VA_results.png',height = 8, width = 5)

fig1
```
```{r DM-DX-effect-cerebellum-figure, fig.height=5, fig.width = 6}
fig1 <- results_pheno %>%
  group_by(YeoNet, subcort_ROI, subcort_NET, 
           subject, DX, Site, fd_mean) %>%
  summarise(Personalized = mean(pvertex_corr),
            Template = mean(tvertex_corr)) %>%
  filter(YeoNet == "DM", subcort_NET == "DM", subcort_ROI == "cerebellum") %>%
  ggplot(aes(y = Personalized, x = DX, color = DX)) + 
  geom_boxplot(outlier.shape = NA) + 
  geom_dotplot(binaxis = 'y', stackdir = 'center', binwidth = 0.01, alpha = 0.5) +
  scale_color_brewer(palette = "Dark2") +
  facet_wrap( ~ Site, ncol = 4) +
  labs(y = "Cerebellum - Cortex Resting State Correlation (Z)",
       title="Cerebellum - Cortical DM Network")

#ggsave(fig1, filename = 'VA_results.png',height = 8, width = 5)

fig1
```
```{r VI-DX-effect-thalamus-figure, fig.height=5, fig.width = 6}
fig1 <- results_pheno %>%
  group_by(YeoNet, subcort_ROI, subcort_NET, 
           subject, DX, Age, Sex, Site, fd_mean) %>%
  summarise(Personalized = mean(pvertex_corr),
            Template = mean(tvertex_corr)) %>%
  filter(YeoNet == "VI", subcort_NET == "VI", subcort_ROI == "thalamus") %>%
  ggplot(aes(y = Personalized, x = DX, color = DX)) + 
  geom_boxplot(outlier.shape = NA) + 
  geom_dotplot(binaxis = 'y', stackdir = 'center', binwidth = 0.01, alpha = 0.5) +
  scale_color_brewer(palette = "Dark2") +
  facet_wrap( ~ Site, ncol = 4) +
  labs(y = "Thalamus - Cortex Resting State Correlation (Z)",
       title="Thalamus - Cortical VI Network")

#ggsave(fig1, filename = 'VA_results.png',height = 8, width = 5)

fig1
```

```{r FP-to-DMcerebellum-DX-effect-figure, fig.height=5, fig.width = 6}
fig1 <- results_pheno %>%
  group_by(YeoNet, subcort_ROI, subcort_NET, 
           subject, DX, Age, Sex, Site, fd_mean) %>%
  summarise(Personalized = mean(pvertex_corr),
            Template = mean(tvertex_corr)) %>%
  filter(YeoNet == "FP", subcort_NET == "DM", subcort_ROI == "cerebellum") %>%
  ggplot(aes(y = Personalized, x = DX, color = DX)) + 
  geom_boxplot(outlier.shape = NA) + 
  geom_dotplot(binaxis = 'y', stackdir = 'center', binwidth = 0.01, alpha = 0.5) +
  scale_color_brewer(palette = "Dark2") +
  facet_wrap( ~ Site, ncol = 4) +
  labs(y = "DM Cerebellum - FP Cortex Resting State Correlation (Z)",
       title="DM Cerebellum - Cortical FP Network")

#ggsave(fig1, filename = 'VA_results.png',height = 8, width = 5)

fig1
```
```{r FP-to-DMstriatum-DX-effect-figure, fig.height=5, fig.width = 6}
fig1 <- results_pheno %>%
  group_by(YeoNet, subcort_ROI, subcort_NET, 
           subject, DX, Age, Sex, Site, fd_mean) %>%
  summarise(Personalized = mean(pvertex_corr),
            Template = mean(tvertex_corr)) %>%
  filter(YeoNet == "FP", subcort_NET == "DM", subcort_ROI == "striatum") %>%
  ggplot(aes(y = Personalized, x = DX, color = DX)) + 
  geom_boxplot(outlier.shape = NA) + 
  geom_dotplot(binaxis = 'y', stackdir = 'center', binwidth = 0.01, alpha = 0.5) +
  scale_color_brewer(palette = "Dark2") +
  facet_wrap( ~ Site, ncol = 4) +
  labs(y = "DM Striatum - FP Cortex Resting State Correlation (Z)",
       title="DM Striatum - Cortical FP Network")

#ggsave(fig1, filename = 'VA_results.png',height = 8, width = 5)

fig1
```

```{r}
kable(DX_lm_model_bySite %>% filter(term %in% c("DXSSD"), 
                                    subcort_NET == "DM", YeoNet == "FP",
                                    vertex_type == "netmean_pvertex") %>%
        arrange(subcort_ROI))
```
```{r}
kable(DX_lm_model_bySite %>% filter(term %in% c("DXSSD"), 
                                    subcort_NET == "DM", YeoNet == "VI",
                                    vertex_type == "netmean_pvertex") %>%
        arrange(subcort_ROI))
```

```{r VI-to-DMcerebellum-DX-effect-figure, fig.height=5, fig.width = 6}
fig1 <- results_pheno %>%
  group_by(YeoNet, subcort_ROI, subcort_NET, 
           subject, DX, Age, Sex, Site, fd_mean) %>%
  summarise(Personalized = mean(pvertex_corr),
            Template = mean(tvertex_corr)) %>%
  filter(YeoNet == "VI", subcort_NET == "DM", subcort_ROI == "cerebellum") %>%
  ggplot(aes(y = Personalized, x = DX, color = DX)) + 
  geom_boxplot(outlier.shape = NA) + 
  geom_dotplot(binaxis = 'y', stackdir = 'center', binwidth = 0.01, alpha = 0.5) +
  scale_color_brewer(palette = "Dark2") +
  facet_wrap( ~ Site, ncol = 4) +
  labs(y = "DM Cerebellum - VI Cortex Resting State Correlation (Z)",
       title="DM Cerebellum - Cortical VI Network")

#ggsave(fig1, filename = 'VA_results.png',height = 8, width = 5)

fig1
```

```{r VI-to-DMstriatum-DX-effect-figure, fig.height=5, fig.width = 6}
fig1 <- results_pheno %>%
  group_by(YeoNet, subcort_ROI, subcort_NET, 
           subject, DX, Age, Sex, Site, fd_mean) %>%
  summarise(Personalized = mean(pvertex_corr),
            Template = mean(tvertex_corr)) %>%
  filter(YeoNet == "VI", subcort_NET == "DM", subcort_ROI == "striatum") %>%
  ggplot(aes(y = Personalized, x = DX, color = DX)) + 
  geom_boxplot(outlier.shape = NA) + 
  geom_dotplot(binaxis = 'y', stackdir = 'center', binwidth = 0.01, alpha = 0.5) +
  scale_color_brewer(palette = "Dark2") +
  facet_wrap( ~ Site, ncol = 4) +
  labs(y = "DM Striatum - VI Cortex Resting State Correlation (Z)",
       title="DM Striatum - Cortical VI Network")

#ggsave(fig1, filename = 'VA_results.png',height = 8, width = 5)

fig1
```

```{r}
pheno %>%
  mutate(summary_path  = file.path(dataset, 'out', 'ciftify_PINT', str_c(outputprefix, '_desc-clean_bold_summary.csv'))) %>%
  select(summary_path) %>%
  write_csv('../data/ciftify_fmriprep/qa_passes_summary_filelist.csv')
```

```{r}
save(file = '../intermediate/03_intermediate_data.RData')
```

