---
title: "Whole Connectome Stats"
output: html_notebook
---

We are now going to see if there is anything in cortical-cortical connectivity by running the matrix of all possible connections instead of just subcortical-cortical stats. 

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(broom)
library(knitr)
library(tableone)
library(cowplot)
library(igraph)
```

## The paths to data

```{r setting paths}
output_base <- '../data/ciftify_fmriprep/'

Yeo7_2011_80verts <- read_csv("../templates/Yeo7_2011_80verts.csv",
                              col_types = c(
                                hemi = col_character(),
                                tvertex = col_integer(),
                                LRpairs = col_integer(),
                                roiidx = col_integer(),
                                NETWORK = col_integer(),
                                LOBE = col_character(),
                                SHORTNAME = col_character(),
                                x = col_integer(),
                                y = col_integer(),
                                z = col_integer()
                              ))

YeoNet_colours = list("VI" = "#781286",
                      "SM" = "#4682B4",
                      "DA" = "#00760E", 
                      "VA" = "#C43AFA",
                      "DM" = "#CD3E3A", 
                      "FP" = "#E69422")

pheno <- read_csv('../phenotypic/20181118_pheno_qapass.csv') %>%
  drop_na(DX)
```

# Code for reading in all the timeseries..


A table that describes the current expected subortical files

```{r define-subcotical-files}
# a tibble table to specify the subcortical meants files that were generated
YeoNet_subcort_list <- c('VI','SM','DA','VA', 'LI','FP','DM')
```

These functions are for reading timeseries files

```{r subcortical file reading functions}

#' read a meants file generated by PINT of ciftify_meants
#'
#' @param filepath the full path to the file
#'
#' @return a dataframe where rows are rois and colums are timepoints
read_meants_csv <- function(filepath) {
   meants <-read_csv(filepath, 
                     col_names = FALSE,
                     col_types = c(.default = col_double()))
   return(meants)
}

#' Read the contents of a csv generated by PINT
#'
#' @param outputprefix The prefix to the PINT outputs
#' @param vertex_type "pvertex" or "tvertex"
#' @param projectname the outputdir
#' @param output_dir the basepath of the pint outputs
#'
#' @return a dataframe of the _meants.csv contents
read_pint_meants <- function(outputprefix, vertex_type, projectname, output_dir) {
  expected_filepath <- file.path(output_dir, projectname, "out",'ciftify_PINT', 
                           str_c(outputprefix, '_desc-clean_bold_', 
                                 vertex_type, '_meants.csv'))
  meants = read_meants_csv(expected_filepath) %>% t() %>% as.data.frame()
  names(meants) = Yeo7_2011_80verts$SHORTNAME
  return(meants)
}
#' Read the contents of a subcortical csv
#' expample file path is sub-CMHHEF011_ses-01_task-rest_acq-CMH_run-01_bold_desc-cleansm0_atlas-7RSN_roi-Lcerebellum_timeseries.csv
#'
#' @param outputprefix the prefix to the pint outputfile
#' @param hemi The hemisphere "L" or "R"
#' @param subregion region "thalamus", "stiatum", "cerebellum"
#' @param output_dir the basepath of the output data
#' @param projectname the project name inside the output dir
#'
#' @return a dataframe of the _meants.csv contents
read_subcortical_hemi_meants <- function(outputprefix, hemi, subregion, projectname, output_dir) {
  expected_filepath <- file.path(output_dir, projectname, "out",'ciftify_meants', 
                           str_c(outputprefix,
                                 '_desc-cleansm0_atlas-7RSN_roi-', 
                                 hemi, subregion, '_timeseries.csv'))
  meants = read_meants_csv(expected_filepath)
  return(meants)
}

#' Contructs the expected output prefix from subid session and func_base
#'
#' @param subid The subject identifier
#' @param sessid The session identifier (or null)
#' @param func_base The functional file prefix
#'
#' @return an output prefix string for the filenames
construct_output_prefix <- function(subid, sessid, func_base) {
  prefix <- if_else(is.na(sessid),
                    file.path(subid, str_c(subid, '_', func_base)),
                    file.path(subid, sessid, 
                      str_c(subid, '_', sessid, '_', func_base)))
  return(prefix)
}

#' get func_base from pint summary filename
#'
#' @param subid The subject identifier
#' @param sessid The session identifier (or null)
#' @param func_base The functional file prefix
#'
#' @return an output prefix string for the filenames
get_func_base_from_pint_summary_filename <- function(filename, subject, session) {
  func_base <- if_else(is.na(session), 
                       filename %>%
                         str_replace(str_c(subject, "_"), '') %>%
                         str_replace('_desc-clean_bold_summary.csv',''),
                       filename %>%
                         str_replace(subject, '') %>%
                         str_replace(session, '') %>% 
                         str_replace('__','') %>%
                         str_replace('_desc-clean_bold_summary.csv',''))
  return(func_base)
}

```


This reads all files and generate PINT to subcortical correlation values for a given subject

```{r read and correlated function}

the_subcortical_guide <- tribble(
 ~subcort_hemi, ~subcort_ROI, ~subcort_NET,
 "L", "thalamus", c('VI','SM','DA','VA', 'FP','DM'),
 "L", "striatum", c('SM','DA','VA', 'LI','FP','DM'),
 "L", "cerebellum", c('VI','SM','DA','VA', 'LI','FP','DM'),
 "R", "thalamus", c('VI','SM','DA','VA', 'LI','FP','DM'),
 "R", "striatum", c('VI','SM','DA','VA', 'LI','FP','DM'),
 "R", "cerebellum", c('VI','SM','DA','VA', 'LI','FP','DM')) %>%
  unnest() %>%
  unite(combined_name, subcort_hemi:subcort_NET, remove = FALSE)



#' read all fMRI timeseries data for one subject and correlates PINT ROIs with subcortex
#'
#' @param out_prefix the prefix to the pint outputfile
#' @param outputbase the path to the pint output directory
#' @param projectname the path to sub-study project (dataset)
#' @param Yeo7_2011_80verts as data frame describing the PINT ROIs 
#'
#' @return a dataframe (graph style) of PINT ROI to subcortical correlations
read_concat_subject_subcort <- function(out_prefix, projectname) {
  
  # read the subcortical meants files
  thalamus_L_meants <- read_subcortical_hemi_meants(out_prefix,
                                                    "L","thalamus", 
                                                    projectname, output_base)
  striatum_L_meants <- read_subcortical_hemi_meants(out_prefix,
                                                    "L","striatum",
                                                    projectname, output_base)
  cerebellum_L_meants <- read_subcortical_hemi_meants(out_prefix,
                                                      "L", "cerebellum",
                                                      projectname, output_base)
  thalamus_R_meants <- read_subcortical_hemi_meants(out_prefix,
                                                    "R","thalamus",
                                                    projectname, output_base)
  striatum_R_meants <- read_subcortical_hemi_meants(out_prefix,
                                                    "R","striatum", 
                                                    projectname, output_base)
  cerebellum_R_meants <- read_subcortical_hemi_meants(out_prefix,
                                                      "R", "cerebellum", 
                                                      projectname, output_base)
  
  # prepare to bind
  subcort_meants <- bind_rows(thalamus_L_meants, striatum_L_meants, cerebellum_L_meants,
                              thalamus_R_meants, striatum_R_meants, cerebellum_R_meants)
  
  # create file names
  subcort_meants_t <- t(subcort_meants) %>% as.data.frame()
  # note that the_subcortical_guide is in the global env
  names(subcort_meants_t) <- the_subcortical_guide$combined_name
  
  return(subcort_meants_t)
}  

#' binds subcortical to cortical timeseries and calculates graph
#'
#' @param subcort_meants 
#' @param pint_meants 
#'
#' @return a dataframe with to and from edgenames as well as Z transformed correlation
calc_PINT_plus_subcort_cor_df <- function(subcort_meants, pint_meants) {
  result <- bind_cols(pint_meants, subcort_meants) %>%
    cor() %>%
    atanh() %>%
    graph_from_adjacency_matrix(mode="upper", 
                                   weighted=T, diag=F) %>%
    as_data_frame()
  return(result)
}


#' reads in all the timeseries files for one participant
#' note that Yeo&_2011_80verts and output_base are pulled from the global env
run_read_all_subject_timeseries_and_corZ <- function(out_prefix, projectname) {
  # read the pint meants files
  pvertex_meants <- read_pint_meants(out_prefix, 'pvertex', 
                                     projectname, output_base)
  tvertex_meants <- read_pint_meants(out_prefix, 'tvertex',
                                     projectname, output_base)
  # read the subcortical ROIs
  subcort_meants <-read_concat_subject_subcort(out_prefix, projectname)
  
  # calc edgewise correlations
  result <- bind_rows("pvertex" = calc_PINT_plus_subcort_cor_df(subcort_meants, pvertex_meants),
                      "tvertex" = calc_PINT_plus_subcort_cor_df(subcort_meants, tvertex_meants),
                      .id = "vertex_type") %>%
    rename(corZ = weight)
  return(result)
}

# run_read_subject_subcort_corrs(subcort_outputlist$subid[1])

```


### This reads all the subcortical files it can find

Write a func_base and outputprefix cols into the pheno file for the file reading step

```{r}
pheno <- pheno %>%
  mutate(func_base = get_func_base_from_pint_summary_filename(filename,subject, session), 
         outputprefix = construct_output_prefix(subject, session, func_base)) 
```

```{r}
safely(map2(pheno$outputprefix, pheno$dataset,
                              ~run_read_all_subject_timeseries_and_corZ(.x, .y)))
```


```{r read all the data}

all_corZ_results <- pheno %>%
  select(subject, outputprefix, dataset) %>%
  mutate(the_corrs = map2(.$outputprefix, .$dataset,
                              ~run_read_all_subject_timeseries_and_corZ(.x, .y)))
```

### merge with the phenotypic data

```{r merge with pheno and clean}
results_pheno <- all_corZ_results %>%
  inner_join(pheno, by = "subject") %>%
  unnest() # %>%
  # mutate(YeoNet = str_sub(PINT_ROI, 1,2),
  #        hemisphere = str_sub(PINT_ROI, 5,5)) %>%
  # mutate(conn_type = if_else(YeoNet == subcort_NET, "same_net", "diff_net"),
  #        YeoNet = factor(YeoNet, levels = c("VI", "SM", "DA", "VA", "FP", "DM")),
  #        subcort_NET = factor(subcort_NET, levels = c("VI", "SM", "DA", "VA", "FP", "DM", "LI"))) %>%
  # select(subject, PINT_ROI, subcort_ROI, subcort_NET,subcort_hemi, 
  #        pvertex_corr, tvertex_corr, 
  #        DX, Sex, fd_mean, Age, Site, Scanner, Age_pt, fd_mean_pt,  
  #        YeoNet, hemisphere, conn_type) 

```


```{r}
results_pheno
```

```{r}
DX_lm_model <- results_pheno %>%
  group_by(vertex_type, to, from) %>%
  do(tidy(lm(corZ ~ DX + Sex + fd_mean_pt + poly(Age_pt,2) + Scanner,.))) %>%
  select(vertex_type, to, from, term, statistic, p.value) %>%
  ungroup() %>%
  group_by(term) %>%
  mutate(p_FDR = p.adjust(p.value, method = "fdr")) %>%
  arrange(p.value)
```

```{r}
DX_lm_model %>% filter(term == "DXSSD", p_FDR < 0.05, vertex_type == "pvertex")
```

```{r}
DX_lm_model %>% filter(term == "DXSSD", p_FDR < 0.05, vertex_type == "tvertex")
```

```{r}
annotated_graph_edges <- DX_lm_model %>%
  ungroup() %>%
  select(to, from) %>%
  distinct() %>%
  mutate(row_number = row_number()) %>%
  gather(edge_type, edgename, to, from) %>%
  left_join(the_subcortical_guide, by = c("edgename" = "combined_name")) %>%
  mutate_if(is.character, funs(replace(., is.na(.), ''))) %>%
  mutate(etype = if_else(str_sub(edgename,2,2)=="_","SubCort", "Cort")) %>%
  mutate(cort_NET = if_else(etype == "Cort", str_sub(.$edgename, 1,2), ""),
         cort_hemi = if_else(etype == "Cort", str_sub(.$edgename, 5,5), ""),
         cort_lobe = if_else(etype == "Cort", str_sub(.$edgename, 3,3), "")) %>%
  gather(e_col, e_val, edgename, subcort_hemi:cort_lobe) %>%
  unite(e_tcol, edge_type, e_col) %>%
  spread(e_tcol, e_val) %>%
  unite(from_to_type, from_etype, to_etype) %>%
  unite(hemis, from_subcort_hemi, from_cort_hemi, to_subcort_hemi, to_cort_hemi, sep = "") %>%
  unite(networks, from_subcort_NET, from_cort_NET, to_subcort_NET, to_cort_NET, sep = "", remove = FALSE) %>%
  mutate(from_to_type = recode(from_to_type, "Cort_SubCort" = "SubCort_Cort")) %>%
  mutate(hemis = recode(hemis, "RL" = "LR")) %>%
  rename(to = to_edgename, from = from_edgename)
  
annotated_graph_edges %>% count(networks)
```


```{r}
DX_lm_model %>%
  inner_join(annotated_graph_edges, by = c("to", "from")) %>%
  filter(term == "DXSSD", p_FDR < 0.05) %>% count(vertex_type, from_to_type)

```
```{r}
DX_lm_model %>%
  inner_join(annotated_graph_edges, by = c("to", "from")) %>%
  filter(term == "DXSSD", p_FDR < 0.05) %>% count(vertex_type, from_to_type, networks) %>%
  spread(vertex_type, n, fill = 0) %>%
  mutate(vert_diff = pvertex - tvertex) %>%
  arrange(-abs(vert_diff))
```
```{r}
DX_lm_model %>% count(term)
```


```{r fig.width=20, fig.height=36}
DX_lm_model %>%
  filter(term == "DXSSD") %>%
  ungroup() %>%
  mutate(sig = if_else(p_FDR < 0.05, '*', NA_character_),
         to_names = factor(to, levels = c(Yeo7_2011_80verts$SHORTNAME, 
                                          the_subcortical_guide$combined_name)),
         from_names = factor(from, levels = c(Yeo7_2011_80verts$SHORTNAME, 
                                              the_subcortical_guide$combined_name))) %>%
ggplot(aes(x = from_names, y = to_names, fill = statistic)) + 
  geom_tile(na.rm = TRUE) +
  geom_point(aes(shape = sig), na.rm = TRUE) +
  scale_fill_gradient2(midpoint = 0) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  facet_wrap(~vertex_type, ncol = 1)
```

```{r fig.width=20, fig.height=36}
DX_lm_model %>%
  filter(term == "") %>%
  ungroup() %>%
  mutate(sig = if_else(p_FDR < 0.05, '*', NA_character_),
         to_names = factor(to, levels = c(Yeo7_2011_80verts$SHORTNAME, 
                                          the_subcortical_guide$combined_name)),
         from_names = factor(from, levels = c(Yeo7_2011_80verts$SHORTNAME, 
                                              the_subcortical_guide$combined_name))) %>%
ggplot(aes(x = from_names, y = to_names, fill = statistic)) + 
  geom_tile(na.rm = TRUE) +
  geom_point(aes(shape = sig), na.rm = TRUE) +
  scale_fill_gradient2(midpoint = 0) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  facet_wrap(~vertex_type, ncol = 1)
```

