---
title: "MDS stats"
output: html_notebook
---

# MDS statistics

```{r}
library(tidyverse)
library(broom)
library(igraph)
```

```{r setting paths}
output_base <- '../data/ciftify_fmriprep/'

Yeo7_2011_80verts <- read_csv("../templates/Yeo7_2011_80verts.csv",
                              col_types = c(
                                hemi = col_character(),
                                tvertex = col_integer(),
                                LRpairs = col_integer(),
                                roiidx = col_integer(),
                                NETWORK = col_integer(),
                                LOBE = col_character(),
                                SHORTNAME = col_character(),
                                x = col_integer(),
                                y = col_integer(),
                                z = col_integer()
                              ))

YeoNet_colours = list("VI" = "#781286",
                      "SM" = "#4682B4",
                      "DA" = "#00760E", 
                      "VA" = "#C43AFA",
                      "DM" = "#CD3E3A", 
                      "FP" = "#E69422")

pheno <- read_csv('../phenotypic/20190301_pheno_qapass.csv') %>% drop_na(DX) 

subsub <- read_csv('../data/ciftify_fmriprep/postPINT2_sub2sub_all_qa_passes.csv')
```

```{r}
mds_sub2sub <- function(data) {
  ## filter allsub2sub distances to only include the qced subids
  ## then run multidimensional scaling to resolve the sub2sub distances to a 2D plane
  distout <- data %>%
  graph_from_data_frame() %>%
  get.adjacency(attr = "distance") %>%
  as.matrix() %>%
  cmdscale(k=2) %>%
  as.data.frame()
  
  
  names(distout) <- c('mds1','mds2')
  distout$src_file <- row.names(distout)
  
  distout <- as.tibble(distout) %>%
    select(src_file, mds1, mds2)
  
  return(as.tibble(distout))
}
```

```{r}
subsub %>%
  filter(roiidx == 1) %>%
  select(subid1, subid2, distance) %>%
  mds_sub2sub()
```

```{r}
mds_results <- subsub %>%
  group_by(roiidx) %>%
  nest() %>%
  mutate(sdist = map(data, ~mds_sub2sub(.x))) %>%
  select(roiidx, sdist) %>%
  unnest()
```

```{r}
mds_pheno <- pheno %>%
  mutate(src_file = str_replace(filename, '_summary.csv','')) %>%
  inner_join(mds_results, by = "src_file") %>%
  inner_join(Yeo7_2011_80verts, by = "roiidx") 
```

```{r}
sdist_manova <- mds_pheno %>%
  group_by(SHORTNAME) %>%
  do(tidy(manova(cbind(mds1, mds2) ~ DX*Age_pt + Sex + fd_mean_pt + Scanner + SurfArea_pt,.))) %>%
  ungroup() %>%
  group_by(term) %>%
  mutate(p_FDR  = p.adjust(p.value, method = "fdr"))
```

```{r}
sdist_manova %>% filter(p_FDR < 0.1) %>% knitr::kable()
```


```{r fig.height=3, fig.width=8}
mds_pheno %>%
  filter(SHORTNAME %in% c("DAF1R", "FPF5R", "VAF4R")) %>%
  ggplot(aes(x = mds1, y = mds2, color = DX)) +
  geom_point(alpha = 0.1) +
  scale_color_manual(values = c("grey20","red")) +
  facet_wrap(~SHORTNAME, ncol = 5)
```
```{r fig.height=3, fig.width=8}
mds_pheno %>%
  filter(SHORTNAME %in% c("DAF1R", "FPF5R", "VAF4R")) %>%
  ggplot(aes(x = mds1, y = mds2, color = Age)) +
  geom_point(alpha = 0.2) +
  scale_color_viridis_c() +
  facet_wrap(~SHORTNAME, ncol = 5)
```
```{r fig.height=6, fig.width=8}
mds_pheno %>%  
  mutate(Age_coarse = case_when(Age < 25 ~ "young adult",
                                Age > 35 ~ "middle age")) %>%
  drop_na(Age_coarse) %>%
  filter(SHORTNAME %in% c("DAF1R")) %>%
  ggplot(aes(x = mds1, y = mds2)) +
  stat_density_2d(aes(fill = stat(level)), bins = 8, geom = "polygon") +
  geom_point(alpha = 0.5, size = 0.5) +
  scale_fill_viridis_c() +
  geom_hline(yintercept = 0) + geom_vline(xintercept = 0) +
  facet_grid(Age_coarse ~ Site)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
