---
title: "Double Check Clinical vars"
output:
  html_document:
    keep_md: TRUE
---

This calculations were run (on a kimel lab machine) to double check the coding of cases and controls and Sex in our phenotypic file.

While most things are fine. Two issues were identified:

1. Two participants in COBRE are coded as Controls, but appear to be cases
2. 30 (SSD) participants from ZHH look like they might be repeated. 

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(knitr)
```

## Reading Saba's clinical data page

```{r}
## reading in the qced_sublists csv to get the sublists
qced_sublists <- read_csv("../phenotypic/NEWallSubjects_completeData3_DM_not_sexmatched.csv",
                          col_types = c(
                            X1 = col_integer(),
                            name = col_character(),
                            subid = col_character(),
                            DX_GROUP = col_integer(),
                            mean_fd = col_double(),
                            age = col_integer(),
                            sex.x = col_integer(),
                            educationCode = col_double(),
                            site = col_integer(),
                            sex.y = col_integer(),
                            X.bad_fd = col_double(),
                            global_corr = col_double(),
                            mean_snfr = col_double()
                          )) 
  
pheno_pre <- qced_sublists %>%
  mutate(Site = factor(site, levels = c(1,2,3),
                       labels = c("CMH","ZHH","COBRE")) ,
         DX = factor(DX_GROUP, level = c(1,2), labels = c('SSD', 'Ctrl')),
         Sex = factor(sex.x, levels = c(1,2), labels = c('M','F')),
         Edu = if_else(is.na(educationCode), 
                       true = mean(educationCode, na.rm = T), 
                       false = educationCode))
```

## Reading some extra info about scan quality

We noticed that our algoritms seemed to be censoring in a weird way (leaving short scans)
So we have going to add stronger censoring criteria before subsampling ZHH (at the end).

```{r}
## we created a list of files that are super short after censoring..
number_tr1 <- read_table2("../data/data/number_tr.txt", 
    col_names = c('num_TR','path')) %>%
    separate(path, into = c('project', 'hcp', 'subid','therest'), sep = .Platform$file.sep, extra = "merge") %>%
    select(num_TR, subid)
number_tr2 <- read_table2("../data/data/cobre_numtr.txt",
                      col_names = c('num_TR','path')) %>%
  separate(path, into = c('subid','therest'), sep = .Platform$file.sep, extra = "merge") %>%
  select(num_TR, subid)

num_tr = bind_rows(number_tr1, number_tr2)


pheno <- inner_join(num_tr, pheno_pre, by = "subid") %>%
  filter(num_TR > 100, X.bad_fd < 0.5) 

```

## reading the COBRE demographics page

```{r}
schizconnect_COBRE_assessmentData_3125 <- read_csv("/KIMEL/tigrlab/external/SchizConnect/COBRE/schizconnect_COBRE_assessmentData_3125.csv",
                                                   col_types = c(
  source = col_character(),
  study = col_character(),
  site = col_character(),
  subjectid = col_character(),
  visit = col_character(),
  assessment = col_character(),
  assessment_description = col_character(),
  question_id = col_character(),
  question_value = col_character()
)) %>%
  mutate(subid = str_c('COBRE_', subjectid, '_SESS01'))
```

```{r}
cobre_check <- inner_join(schizconnect_COBRE_assessmentData_3125, pheno, by = "subid")
```

```{r}
cobre_check %>%
  filter(question_id == "CODEM_2") %>%
  select(sex.x, question_value) %>%
  ftable()
```

```{r}
cobre_check %>%
  filter(question_id == "CODEM_17") %>%
  select(DX_GROUP, question_value) %>%
  ftable()

```


```{r}
cobre_weird <- cobre_check %>%
  filter(question_id == "CODEM_17",
         question_value %in% c("13", "20")) %>%
  select(subid)

inner_join(cobre_weird, cobre_check, by = "subid") %>%
  select(question_id, question_value, age, Sex, Edu, DX)
```
Conclusion: These two participants are NOT Controls...(they also got excluded for motion..so oh well)

COBRE_A00028189_SESS01				
COBRE_A00035836_SESS01

```{r}
pheno_corrected <- pheno
for (badsub in cobre_weird$subid) {
  pheno_corrected$DX[pheno_corrected$subid == badsub] <- 'SSD'
  pheno_corrected$DX_GROUP[pheno_corrected$subid == badsub] <- 1
}

cobre_recheck <- inner_join(schizconnect_COBRE_assessmentData_3125, pheno_corrected, by = "subid")

cobre_recheck %>%
  filter(question_id == "CODEM_17") %>%
  select(DX_GROUP, question_value) %>%
  ftable()
```






## Now looking at ZHH data

```{r warning=FALSE, message=FALSE}
library(readxl)
qrySZ_Sess_Miklos <- read_excel("/KIMEL/tigrlab/external/miklos/demographics/qrySZ_Sess_Miklos.xlsx")
qryHC_Sess_Miklos <- read_excel("/KIMEL/tigrlab/external/miklos/demographics/qryHC_NewResting_15-40.xlsx")
```

```{r}
pheno %>% filter(Site == "ZHH") %>% select(subid) %>% slice(1:5)
```

```{r}
ZHH_HC <- qryHC_Sess_Miklos %>%
  mutate(subid = str_c('EXP_',SessNo, '_SESS01')) %>%
  inner_join(qced_sublists, by = "subid")
```

```{r}
ZHH_HC %>%
  select(sex, sex.x) %>%
  ftable
```
```{r}
ZHH_HC %>%
  select(sex, DX_GROUP) %>%
  ftable
```

```{r}
ZHH_SZ <- qrySZ_Sess_Miklos %>%
  mutate(subid = str_c('EXP_',SessNo, '_SESS01')) %>%
  inner_join(qced_sublists, by = "subid")
```


```{r}
ZHH_SZ %>%
  select(sex, DX_GROUP) %>%
  ftable
```

```{r}
ZHH_SZ %>%
  select(sex, sex.x) %>%
  ftable
```

```{r}
ZHH_SZ %>%
  select(sex, DX_GROUP) %>%
  ftable
```

```{r}
repeated_SZ_subjects <- ZHH_SZ %>%
 count(grid) %>%
 filter(n > 1)

repeated_SZ_subjects
```

```{r}
repeated_HC_subjects <- ZHH_HC %>%
 count(GRID) %>%
 filter(n > 1)
```

```{r}
ggplot(ZHH_SZ, aes(x = age, y = Age)) + geom_point()
```

```{r}
ggplot(ZHH_HC, aes(x = age, y = Age)) + geom_point()
```



```{r}
ggplot(ZHH_HC, aes(x = PtEdYears, y = educationCode)) + geom_point()
```

```{r}
ggplot(ZHH_HC, aes(x = PtEdHighestHol_Demo, y = educationCode)) + geom_point()
```


```{r}
ggplot(ZHH_SZ, aes(x = PtEdYears_NI, y = educationCode)) + geom_point()
```

```{r}
ggplot(ZHH_SZ, aes(x = PtEdHighestHol_Demo, y = educationCode)) + geom_point()
```

```{r}
set.seed(14)
ZHH_SZ_subsampled <- qrySZ_Sess_Miklos %>%
  mutate(subid = str_c('EXP_',SessNo, '_SESS01')) %>%
  ungroup() %>% 
  group_by(grid) %>%
  sample_n(1) %>%
  select(subid) %>%
  ungroup()

to_drop <- ZHH_SZ %>%
  anti_join(ZHH_SZ_subsampled, by = "subid")

pheno_corrected1 <- pheno_corrected %>%
  anti_join(to_drop, by = "subid")
```
## Now for SPINS

```{r}
spins_demographics <- read_csv("/KIMEL/tigrlab/archive/data-2.0/SPINS/data/clinical/demographics.csv") %>%
  mutate(subid  = str_c(record_id, '_01'))
```
```{r}
spins_check <- inner_join(spins_demographics, qced_sublists, by = "subid")

spins_demographics$subid[1:5]
```

```{r}
spins_check %>%
  select(group, DX_GROUP) %>%
  ftable()
```

```{r}
spins_check %>%
  select(sex, sex.x, group) %>%
  ftable()
```

# Finally writting results from corrected version back to csv

```{r}
names(pheno_corrected1)
```

```{r}
pheno_corrected1 %>%
  select(subid, name, Site, DX, age, Sex, Edu, mean_fd, X.bad_fd, global_corr, mean_snfr) %>%
  write_csv('../phenotypic/subjects_not_sexmatched_20180620.csv')
```


