---
title: "Prelim PINT stats"
output: html_notebook
---

Going to Start Loading saba's PINT data


```{r}
library(dplyr)
library(tidyr)
library(readr)
library(broom)
library(igraph)
library(stringr)
library(tibble)
library(purrr)
```


The phenotypic file is copied from saba's folder

```{r}
pint_outputs <- '../data/PINT_pcorr6-6-12_CMH_20171116/'
subcortical_outputs_dir <- '../data/subcortical_ts/'
pheno <- read_csv("../phenotypic/NEWallSubjects_completeData3_DM_not_sexmatched.csv",
                  col_types = c(
                    X1 = col_integer(),
                    name = col_character(),
                    subid = col_character(),
                    DX_GROUP = col_integer(),
                    mean_fd = col_double(),
                    age = col_integer(),
                    sex.x = col_integer(),
                    educationCode = col_double(),
                    site = col_integer(),
                    sex.y = col_integer(),
                    X.bad_fd = col_double(),
                    global_corr = col_double(),
                    mean_snfr = col_double()
                  ))


Yeo7_2011_80verts <- read_csv("~/code/ciftify/ciftify/data/PINT/Yeo7_2011_80verts.csv")
```
Reading in all the timeseries..

```{r}
pint_outputlist <- data.frame("filepath" = list.files(pint_outputs, 
                                                      recursive = T,
                                                      pattern = "_summary.csv")) %>%
  separate(filepath, into = c("subid", "summary_file"), sep = '/')
```

```{r}
subcort_outputlist <- data.frame("subid" = list.files(subcortical_outputs_dir, 
                                                      recursive = F))

pint_outputlist <- inner_join(pint_outputlist, subcort_outputlist, by = "subid")
```

```{r}
#' reads and the mean time series file
#'
#' @param meants_filepath the full path to the mean timeseries file
#' @return the meants data as data.frame
read_meants_csv <- function(meants_filepath) {
meants <- read_csv(meants_filepath, 
                   col_names = FALSE,
                   col_types = cols(.default = col_double()))
return(meants)
}

#' determines the filepath for a pint generated meants output and loads the data
#'
#' @param subid the subject id prefix for the pint output
#' @param vertex_type ivertex or tvertex
#' @param pint_outputs_dir the path to the pint outputs
#' 
#' @return a data.frame of the meants outputs
read_pint_meants <- function(subid, vertex_type, pint_outputs_dir) {
  pint_meants <- read_meants_csv(file.path(pint_outputs_dir,
                                           subid, 
                                           str_c(subid, '_', vertex_type, '_meants.csv')))
  return(pint_meants)
}

# a tibble table to specify the subcortical meants files that were generated
subcortical_files <- tribble(
  ~file_prefix, ~name,
  "Thalamus_corrected", "Thalamus", 
  "Striatum_network_1", "Striatum_VI",
"Striatum_network_2", "Striatum_SM",
"Striatum_network_3", "Striatum_DA",
"Striatum_network_4", "Striatum_VA",
"Striatum_network_5", "Striatum_Limbic",
"Striatum_network_6", "Striatum_FP",
"Striatum_network_7", "Striatum_DM")

#' reads in the subcortical data for one subject specified in the subcortical template
#'
#' @param subid the subject id prefix for the output
#' @param subcortical_outputs_dir the base output directory for the subcortical ts data
#' @param subcortical_template a dataframe with a 'file_prefix' column decscribing the subcortical regions
#' @param smoothing the amount of smoothing on the origianl dtseries (defaults to 0)
#'
#' @return the cpmcatenated mean timeseries data as a dataframe
read_subcortical_meants <- function(subid, subcortical_outputs_dir, 
                                    subcortical_template = subcortical_files,
                                    smoothing = 's0') {
  subcort_meants <- subcortical_template %>%
    mutate(filepath = str_c(subcortical_outputs_dir,subid, '/', 
                            subid, '_', smoothing, '_', file_prefix, '.nii_meants.csv'),
           thedata = map(filepath, ~read_meants_csv(.x))) %>%
    select(thedata) %>%
    unnest() 
  return(subcort_meants)
}
```

```{r}
subid <- pint_outputlist$subid[1]

# read in data for one subject
subject_subcort_corrs <- function(subid, pint_outputs, subcortical_outputs_dir,
                                  Yeo7_2011_80verts, subcortical_files) {
  
ivertex_meants <- read_pint_meants(subid, 'ivertex', pint_outputs)
tvertex_meants <- read_pint_meants(subid, 'tvertex', pint_outputs)
subcort_meants <- read_subcortical_meants(subid, subcortical_outputs_dir, subcortical_template = subcortical_files) 

ivertex_subcortcorr <- as.data.frame(cor(t(subcort_meants), t(ivertex_meants)))
names(ivertex_subcortcorr) <- Yeo7_2011_80verts$SHORTNAME
ivertex_result <- ivertex_subcortcorr %>%
  mutate(subcort_ROI = subcortical_files$name) %>%
  gather(PINT_ROI, ivertex_corr, -subcort_ROI)

tvertex_subcortcorr <- as.data.frame(cor(t(subcort_meants), t(tvertex_meants)))
names(tvertex_subcortcorr) <- Yeo7_2011_80verts$SHORTNAME
tvertex_result <- tvertex_subcortcorr %>%
  mutate(subcort_ROI = subcortical_files$name) %>%
  gather(PINT_ROI, tvertex_corr, -subcort_ROI)

subresult <- ivertex_result %>%
  inner_join(tvertex_result, by = c("PINT_ROI", "subcort_ROI"))
return(subresult)
}

```

```{r}

run_read_subject_subcort_corrs <- function(subid) {
  df <-subject_subcort_corrs(subid, pint_outputs, subcortical_outputs_dir,
                                  Yeo7_2011_80verts, subcortical_files)
  return(df)
}

all_subcort_results <- pint_outputlist %>%
  mutate(subcort_corrs = map(subid, ~run_read_subject_subcort_corrs(.x)))
```

```{r}
results_pheno <- all_subcort_results %>%
  inner_join(pheno, by = c("subid" = "name")) %>%
  unnest()
```

```{r}
table1 <- results_pheno %>%
  mutate(corr_diff = ivertex_corr - tvertex_corr) %>%
  gather(corr_type, rval, ivertex_corr, tvertex_corr, corr_diff) %>%
  group_by(corr_type, PINT_ROI, subcort_ROI) %>%
  summarise(n = n(),
            mean = mean(rval),
            sd = sd(rval)) %>%
  

library(knitr)
kable(table1 %>% arrange(mean))
```
```{r}
library(stringr)
table2 <- results_pheno %>%
  mutate(corr_diff = ivertex_corr - tvertex_corr,
         YeoNet = str_sub(PINT_ROI, 1,2)) %>%
  gather(corr_type, rval, ivertex_corr, tvertex_corr, corr_diff) %>%
  group_by(corr_type, YeoNet, subcort_ROI) %>%
  summarise(n = n(),
            Mean = mean(rval),
            SD = sd(rval)) 
  


kable(table2)
```

```{r}
library(stringr)
net_means <- results_pheno %>%
  mutate(corr_diff = ivertex_corr - tvertex_corr,
         YeoNet = str_sub(PINT_ROI, 1,2)) %>%
  group_by(YeoNet, subcort_ROI, subid) %>%
  summarise(netmean_ivertex = mean(ivertex_corr),
            netmean_tvertex = mean(tvertex_corr)) %>%
  ungroup() %>%
  group_by(YeoNet, subcort_ROI) %>%
  do(tidy(t.test(.$netmean_ivertex, .$netmean_tvertex, paired = TRUE)))
  


kable(net_means %>% arrange(p.value))
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).
