---
title: "checking completion"
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

# Check completion and add MR QA

This section of the code checks to make sure that we have preprocessed data available for all expected partcipants.

Then, for participants with more than one run/session of bold data it picks the best run per participant for the next analysis

The final output is the QAed phenotypic file is `data/processed/pheno/simple_pheno_20200214.csv` which is the input for all of the rest of the analyses.

```{r}
library(tidyverse)
library(here)
```

```{r}
processed_mri_dir <- here("data/processed/mri/")
```

## Get a list of available bold and T1w files (from the mriqc outputs)

```{r reading_mriqc_bolds, message=FALSE, warning=FALSE}
sub_projects = c("ZHH", "COBRE", "ASDD", "ASDD", "DTI3T" , "RTMSWM", "PNSC", "SPINS", "ds000030_R1.0.5")

read_mriqc_bold <- function(studyname) {
  bold <- read_csv(str_c(processed_mri_dir, studyname, "/out/mriqc/bold.csv")) %>%
    mutate(subject_id = as.character(subject_id))
  if ("session_id" %in% names(bold)) {
    bold <- bold %>% mutate(session_id = as.character(session_id))
  }
  return(bold)
}

all_the_bolds <- tibble(dataset = sub_projects) %>% 
    mutate(boldqc = map(dataset, function(x) {
        read_mriqc_bold(x)
    })) %>%
    unnest() %>%
  filter(task_id == "rest") 

```

```{r}
bolds_condensed <- all_the_bolds %>%
  select(dataset, ends_with('_id'), starts_with('fd_'), starts_with('size'), starts_with('spacing')) %>%
  mutate(subject = str_c("sub-", subject_id),
         session = str_c("ses-",session_id)) 
```


```{r message=FALSE, warning=FALSE}
read_mriqc_t1w <- function(studyname) {
  bold <- read_csv(str_c(processed_mri_dir, studyname, "/out/mriqc/T1w.csv")) %>%
    mutate(subject_id = as.character(subject_id))
  if ("session_id" %in% names(bold)) {
    bold <- bold %>% mutate(session_id = as.character(session_id))
  }
  return(bold)
}

all_the_T1w <- tibble(dataset = sub_projects) %>% 
    mutate(t1wqc = map(dataset, function(x) {
        read_mriqc_t1w(x)
    })) %>%
    unnest() %>%
  group_by(dataset, subject_id) %>%
  summarise(num_t1w = n())
```

### the list of usable scans is all participants with both T1w and bold data

```{r}
usable_scans <- all_the_bolds %>%
  group_by(dataset, subject_id, task_id) %>%
  summarise(num_rest = n()) %>%
  full_join(all_the_T1w, by = c("subject_id", "dataset")) %>%
  mutate(num_scans = num_rest + num_t1w,
         subject = str_c("sub-", subject_id)) %>%
  ungroup()
```


```{r}
usable_scans %>%
  ungroup() %>%
  select(subject_id, dataset, num_scans) %>%
  drop_na(num_scans) %>%
  distinct() %>%
  count()
```

## now glob for all of the PINT outputs

```{r identify_pint_outputs}
pint_summarys_wses <- Sys.glob(str_c(processed_mri_dir, "/*/out/ciftify_PINT/sub*/ses*/*summary.csv"))

pint_summarys_nses <- Sys.glob(str_c(processed_mri_dir, "/*/out/ciftify_PINT/sub*/*summary.csv"))

pintdf_nses <- tibble(filepath = pint_summarys_nses) %>%
  transmute(filepath = str_remove(filepath, processed_mri_dir)) %>%
  separate(filepath,
           into = c("1",'dataset','4','5','subject', 'filename'),
           sep = .Platform$file.sep) %>%
  select(dataset, subject, filename)

pintdf_wses <- tibble(filepath = pint_summarys_wses) %>%
  transmute(filepath = str_remove(filepath, processed_mri_dir)) %>%
  separate(filepath,
           into = c("1", 'dataset','4','5','subject', 'session', 'filename'),
           sep = .Platform$file.sep) %>%
  select(dataset, subject, session, filename)

pintdf <- bind_rows(pintdf_wses, pintdf_nses)

rm(pint_summarys_nses, pint_summarys_wses, pintdf_nses, pintdf_wses)
```

## read in the combined demographics from the last chapter

```{r}
# removing session id column because it is redundant
simple_pheno <- read_csv(here('data/processed/pheno/simple_pheno_20200214.csv')) 
```

## also read in an concatenate all the surface area info from freesurfer

```{r}
all_surfs <- tibble(dataset = sub_projects) %>%
  mutate(data = map(dataset, ~read_csv(str_c(processed_mri_dir,.x,
                                             '/out/freesurfer/CorticalMeasuresENIGMA_SurfAvg.csv'),
                                       col_types = cols(
                                         .default = col_double(),
                                         SubjID = col_character())))) %>%
  unnest() %>%
  select(dataset, SubjID, LSurfArea, RSurfArea) %>%
  mutate(SurfArea = LSurfArea + RSurfArea)
```


## anti-join the pheno data with the usable scan data to see if we have everything..


```{r}
usable_scans %>%
  anti_join(simple_pheno, by = c("subject", "dataset")) %>%
  drop_na(num_scans)
```

#### we see that the only people we have bold info but no phenotype for is that one VIPR participant in SPINS and the 5 people from ds00030 who don't have a T1w scan

## Setting the motion threshold:

We have set the motion threshold to:
Mean FD < 0.5mm and
No more than 50% of the scan with motion > 0.2mm

```{r}
mean_fd_thres <- 0.5
perc_fd_thres <- 50

pre_qa <- bolds_condensed %>%
  inner_join(select(usable_scans, -task_id, -subject_id), 
             by = c("subject", "dataset")) %>%
  drop_na(num_scans) %>%
  inner_join(simple_pheno, by = c("subject", "dataset")) %>%
  inner_join(all_surfs %>% rename(subject = SubjID), by = c("subject", "dataset"))
```

```{r}

pre_qa_counts <- pre_qa %>%
  select(subject, dataset, DX) %>%
  distinct() %>%
  count(DX)

qa_passes_pheno <- pre_qa %>%
  filter(fd_mean < 0.5, fd_perc < 50, size_t > 100) 

qa_passes_pheno %>%
  select(subject, dataset, DX) %>%
  distinct() %>%
  count(DX) %>%
  inner_join(pre_qa_counts, by = "DX", suffix = c("_after_qa", "_before_qa"))
```

## who is still missing a PINT output?

```{r}
anti_join(qa_passes_pheno, pintdf,
          by = c("dataset", "subject", "session")) 
```

## Selecting scans with least motion


```{r select-scans-with-least-motion}
# select the scan for each participant with the least motion
pheno <- qa_passes_pheno %>%
  select(-ends_with("_x"), -ends_with("_y")) %>%
  left_join(pintdf,
          by = c("dataset", "subject", "session")) %>%
  filter(!is.na(filename)) %>%
  group_by(subject, dataset) %>%
  arrange(fd_perc) %>%
  slice(1) %>%
  ungroup() 
```


```{r}
pheno %>%
  ggplot(aes(x = Age, y = SurfArea)) + 
  geom_point(aes(color = Site)) + geom_smooth(method = "lm") 
```

## final mangle of the phenotypic data (transforming variables)

```{r}
transform_to_normal <- function(X) {
  # calculate the best exponent using powerTransform:
  pT <- car::powerTransform(X)
  # apply the power transform and save the result to a new variable
  X_pT <- X^pT$lambda ## note ^ is exponent in r
  xout = scales::rescale(X_pT)
  return(X_pT)
}

# transform age and fd_mean to normality
pheno <- pheno %>%
  mutate(Age_pt = transform_to_normal(Age),
         fd_mean_pt = transform_to_normal(fd_mean),
         SurfArea_pt = transform_to_normal(SurfArea))
```



```{r}
pheno %>%
  select(subject, dataset, DX) %>%
  distinct() %>%
  count(DX) %>%
  inner_join(pre_qa_counts, by = "DX", suffix = c("_after_qa", "_before_qa"))
```


```{r}
pheno %>%
  group_by(Site, DX) %>%
  summarise(n = n(),
            nMale = sum(Sex == "M"),
            perc_male = nMale/n()*100,
            age_mean = mean(Age, na.rm = T),
            age_sd = sd(Age, na.rm = T),
            age_min = min(Age, na.rm = T),
            age_max = max(Age, na.rm = T)) %>%
    mutate(age_report =sprintf("%0.1f(%0.1f) %0.0f - %0.0f", 
                               age_mean, age_sd, age_min, age_max),
           sex_report = str_c(nMale, '(', sprintf("%0.1f", perc_male), '%)')) %>%
  select(Site, DX, n, age_report, sex_report)

```
```{r}
qa_passes_pheno %>%
  mutate(scan_length = size_t*2/60,
         spacing_x_round = round(spacing_x, 3),
         spacing_z_round = round(spacing_z,3)) %>%
  group_by(subject) %>%
  sample_n(1) %>%
  ungroup() %>%
  group_by(Site, size_t, size_x, size_y, size_z, spacing_x_round, spacing_z_round, scan_length) %>%
  count() %>%
  ungroup() %>%
  group_by(Site) %>%
  arrange(-n) %>%
  slice(1) %>%
  t()

```



```{r} 
write_csv(pheno, here('data/processed/pheno/20200214_pheno_qapass.csv'))
```

```{r}
pheno %>%
  filter(!is.na(DX)) %>%
  count(Site, DX) 
```


+ ASDD is done!
+ ZHH is done! (note that the TR for scans without a TR was set to 2s by Saba and Dayton)
+ RTMSWM is done!
+ PNSC is done
+ DTI3T is done!
+ SPINS has one extra bold (CMHAA2102 - from VIPR - disregard)
+ COBRE is done (enough) - but half of it never downloaded
+ ds00030 5 subjects need to rerun ciftify..

### write out subject list for further analysis

this section is run manually before the postPINT group steps are done..

```{r eval = FALSE}
source(here('code','R','file_reading_helpers.R'))

final_sublist <- pheno %>%
  mutate(func_base = get_func_base_from_pint_summary_filename(filename,subject, session), 
         outputprefix = construct_output_prefix(subject, session, func_base),
         expected_filepath = file.path(dataset, "out",'ciftify_PINT', 
                                 str_c(outputprefix, '_desc-clean_bold_summary.csv')))

final_sublist %>%
  select(expected_filepath) %>%
  arrange(expected_filepath) %>%
  write_csv(path = here('data/processed/mri/all_qa_passes_group/pint_summary_filelist.csv'), col_names = FALSE)
```

