---
title: "Sub-cortical Cortical Stats Split by Hemisphere"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    keep_md: yes
---

# Sub-cortical Cortical Stats Left and Right

This analysis tries to combine timeseries data from PINT outputs with subcortical timeseries to ask two questions

1. "External" validation of PINT. If PINT is indeed helping us better target meaningful resting state networks than we should see "cleaner" patterns of between the PINT output cortical ROIs and parcels of the subcortical structure that have been associated with these networks in literature.
   + i.e. connectivity of the cortical ROIS with "expected" subcortical parcel should increae and correlation with other parcels should decrease after PINT.
   
2. To interograte SSD related differences in Cortical-Subcortical connectivity - and to see if they persist after PINT.

Some work Ji (in prep) kinda suggests that there might be differences between left and right subcortical structures. AND spliting the left and right seemed to make more sense for whole brain correlations (because our cortical nodes have a hemisphere). So in this analysis have separate left and right ROIs

```{r}
library(tidyverse)
library(broom)
library(knitr)
library(tableone)
library(cowplot)
library(ggridges)
library(here)
```


## The paths to data

```{r setting paths}

source(here('code/R/settings_helpers.R'))
pheno <- read_pheno_file()
YeoNet_colours <- define_Yeo7_colours()
Yeo7_2011_80verts <- read_Yeo72011_template()
the_subcortical_guide <- get_subcortical_guide()
node_annotations <- get_node_annotations(Yeo7_2011_80verts, the_subcortical_guide)
source(here('code/R/custom_plot_helpers.R'))

source(here('code/R/file_reading_helpers.R'))
```


This reads all files and generate PINT to subcortical correlation values for a given subject



### This reads all the subcortical files it can find

Write a func_base and outputprefix cols into the pheno file for the file reading step

```{r}
pheno <- pheno %>%
  mutate(func_base = get_func_base_from_pint_summary_filename(filename,subject, session), 
         outputprefix = construct_output_prefix(subject, session, func_base)) 
```

a litle chunck I use to test if test if the reader is working...




```{r eval = FALSE}
run_read_all_subject_timeseries_and_subcortcort_corZ(pheno$outputprefix[1], pheno$dataset[1])
```


```{r read all the data}

all_subcort_results <- pheno %>%
  select(subject, outputprefix, dataset) %>%
  mutate(subcort_corrs = map2(outputprefix, dataset,
                              ~run_read_all_subject_timeseries_and_subcortcort_corZ(.x, .y)))
```

```{r cache-subcort-Rdata, eval = FALSE}
save(all_subcort_results, file = here("data/processed/Rdata_cache/03_subcort_results_cache.Rdata"))
```

```{r load-cached-results, eval=FALSE}
load(here("data/processed/Rdata_cache/03_subcort_results_cache.Rdata"))
```



### merge with the phenotypic data

```{r merge with pheno and clean}
results_pheno <- all_subcort_results %>%
  inner_join(pheno, by = c("subject", "dataset")) %>%
  unnest() %>%
  inner_join(the_subcortical_guide, by = c("combined_name")) %>%
  mutate(YeoNet = str_sub(PINT_ROI, 1,2),
         hemisphere = str_sub(PINT_ROI, 5,5)) %>%
  mutate(conn_type = if_else(YeoNet == subcort_NET, "same_net", "diff_net"),
         YeoNet = factor(YeoNet, levels = c("VI", "SM", "DA", "VA", "FP", "DM")),
         subcort_NET = factor(subcort_NET, levels = c("VI", "SM", "DA", "VA", "FP", "DM", "LI"))) %>%
  select(subject, dataset, PINT_ROI, subcort_ROI, subcort_NET,subcort_hemi, 
         pvertex_corr, tvertex_corr, tvolume_corr,
         DX, Sex, fd_mean, Age, Site, Scanner, Age_pt, fd_mean_pt,  
         YeoNet, hemisphere, conn_type) 

```





## make a subject table from resuts pheno


```{r report_demographics}
library(tableone)
therealtable1 <- CreateTableOne(
  strata = c("DX", "Site"),
  vars = c("Age", "Sex", "fd_mean", "fd_perc"),
  data = filter(results_pheno, PINT_ROI=="DMP1L",subcort_ROI=="thalamus", subcort_NET=="VA", subcort_hemi == "L")
)
tabMat <- print(therealtable1, quote = FALSE, noSpaces = TRUE, printToggle = FALSE)
kable(tabMat)

```

```{r report_demographics-pooled}
library(tableone)
therealtable1 <- CreateTableOne(
  vars = c("Age", "Sex", "DX", "fd_mean", "fd_perc"),
  data = filter(results_pheno, PINT_ROI=="DMP1L",subcort_ROI=="thalamus", subcort_NET=="VA", subcort_hemi == "L")
)
tabMat <- print(therealtable1, quote = FALSE, noSpaces = TRUE, printToggle = FALSE)
kable(tabMat)

```


# Is PINT "focusing" cortical subcortical connectivity

```{r plotting-PINT-change-matrix, fig.width=6, fig.height=8}
table1 <- results_pheno %>%
  mutate(corr_diff = pvertex_corr - tvertex_corr) %>%
  gather(corr_type, rval, pvertex_corr, tvertex_corr, tvolume_corr) %>%
  group_by(corr_type, YeoNet, subcort_ROI, subcort_NET) %>%
  summarise(n = n(),
            Mean = mean(rval),
            SD = sd(rval)) 
  
ggplot(table1, aes(y = YeoNet, x = subcort_NET, fill = Mean)) + 
  geom_tile() +
  scale_fill_distiller(breaks = c(-0.5,0.5), type = "div", palette = 5) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  facet_grid(subcort_ROI~corr_type) 

```
functions to help re-annotated the function axes

```{r function-to-plot-annots}
#' sets some the main variables to factors to more descriptive labels
add_corrtype_and_subcortROI_columns <- function(data) {
  result <- data %>%
    mutate(corrtype = factor(corr_type, levels = c('tvolume_corr','tvertex_corr','pvertex_corr'),
                           labels = c("Volume Template", "Surface Template", "Surface Personalized")),
         subcortROI = factor(subcort_ROI, 
                             levels = c("striatum", "thalamus", "cerebellum"),
                             labels = c("Striatum", "Thalamus", "Cerebellum"))) 
  return(result)
}

#'drop VI DA and LI network from resutls
drop_VI_DA_LI <- function(data) {
  result <- data %>%
    filter(subcort_NET != "VI",
         subcort_NET != "DA",
         subcort_NET != "LI",
         YeoNet != "VI",
         YeoNet != "DA") 
  return(result)
}
```


```{r plotting-PINT-change-matrix-reduce, fig.width=7.5, fig.height=7.5}

table1 %>%
  drop_VI_DA_LI() %>%
  add_corrtype_and_subcortROI_columns() %>%
ggplot(aes(y = YeoNet, x = subcort_NET, fill = Mean)) + 
  geom_tile() +
  geom_text(aes(label = sprintf('%3.2f',Mean))) +
  scale_fill_distiller(breaks = c(-0.5,0.5), type = "div", palette = 5) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  facet_grid(corrtype~subcortROI) +
  labs(y = "Cortical RSN Network", x = "Subcortical Subregion")

```


```{r plotting-PINT-change-matrix-hemi, fig.width=12, fig.height=12}
table1 <- results_pheno %>%
  mutate(corr_diff = pvertex_corr - tvertex_corr) %>%
  gather(corr_type, rval, pvertex_corr, tvertex_corr, tvolume_corr) %>%
  group_by(corr_type, YeoNet, hemisphere, subcort_ROI, subcort_NET, subcort_hemi) %>%
  summarise(n = n(),
            Mean = mean(rval),
            SD = sd(rval)) 

table1 %>%
  drop_VI_DA_LI() %>%
  add_corrtype_and_subcortROI_columns() %>%
ggplot(aes(y = YeoNet, x = subcort_NET, fill = Mean)) + 
  geom_tile() +
  geom_text(aes(label = sprintf('%3.2f',Mean))) +
  scale_fill_distiller(breaks = c(-0.5,0.5), type = "div", palette = 5) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  facet_grid(subcortROI*subcort_hemi~corrtype*hemisphere) +
  labs(y = "Cortical RSN Network", x = "Subcortical Subregion")  
```

We see in the above figure that the Yeo 7 Network connectivity strongly shows the expected pattern in the cerebeullum. 

Lower evidence is seen in the striatum and thalamus, although there is a faint increase across the diagonal for the SM, VA and DM especially

```{r paired-ttests-of-PINT-effect, fig.heigth = 2, fig.width=8}
net_means <- results_pheno %>%
  mutate(corr_diff = pvertex_corr - tvertex_corr) %>%
  group_by(YeoNet, subcort_ROI, subcort_NET, conn_type, subject) %>%
  summarise(netmean_pvertex = mean(pvertex_corr),
            netmean_tvertex = mean(tvertex_corr),
            netmean_tvolume = mean(tvolume_corr)) %>%
  ungroup()

net_means_pint_t <- net_means %>%
  group_by(YeoNet, subcort_ROI, subcort_NET) %>%
  do(tidy(t.test(.$netmean_pvertex, .$netmean_tvertex, paired = TRUE))) %>%
  ungroup() %>% mutate(p_FDR = p.adjust(p.value, method = "fdr"))

net_means_pint_t %>%
  ungroup() %>%
  mutate(sig = if_else(p_FDR < 0.05, '*', NA_character_) ) %>%
  drop_VI_DA_LI() %>%
  mutate(subcortROI = factor(subcort_ROI, 
                           levels = c("striatum", "thalamus", "cerebellum"),
                           labels = c("Striatum", "Thalamus", "Cerebellum"))) %>%
ggplot(aes(x = YeoNet, y = subcort_NET, fill = statistic)) + 
  geom_tile(color = "black", na.rm = TRUE) +
  geom_point(aes(shape = sig), na.rm = TRUE) +
  scale_fill_distiller(breaks = c(-10,10), type = "div", palette = 5) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  facet_wrap(~subcortROI)
```
Here we plot the paired t-stat camparing personalized to template, we see a very strong increase in correlation along the diagonal (i.e. with the hypothesized regions) and decreases on the off-dignonal (i.e. decreased connectivity with the other network's parcels)

```{r}
net_means_vpint_t <- net_means %>%
  group_by(YeoNet, subcort_ROI, subcort_NET) %>%
  do(tidy(t.test(.$netmean_pvertex, .$netmean_tvolume, paired = TRUE))) %>%
  ungroup() %>% mutate(p_FDR = p.adjust(p.value, method = "fdr"))

net_means_vpint_t %>%
  ungroup() %>%
  mutate(sig = if_else(p_FDR < 0.05, '*', NA_character_) ) %>%
  drop_VI_DA_LI() %>%
  mutate(subcortROI = factor(subcort_ROI, 
                           levels = c("striatum", "thalamus", "cerebellum"),
                           labels = c("Striatum", "Thalamus", "Cerebellum"))) %>%
ggplot(aes(x = YeoNet, y = subcort_NET, fill = statistic)) + 
  geom_tile(color = "black", na.rm = TRUE) +
  geom_point(aes(shape = sig), na.rm = TRUE) +
  scale_fill_distiller(breaks = c(-10,10), type = "div", palette = 5) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  facet_wrap(~subcortROI)
```

# trying to calculate an vs off diagonal term

In the above table to calcuculated the "focussing" effect as the change (in on person) between in connectivity with the expected parcel subtracted by the change in connectivity from other regions.

Below we plot these values against zero

```{r net-focus-tstats}
net_focus <- net_means %>%
  ungroup() %>%
  mutate(pint_diff = netmean_pvertex - netmean_tvertex,
         vpint_diff = netmean_pvertex - netmean_tvolume,
         surf_diff = netmean_tvertex - netmean_tvolume) %>%
  group_by(subject, subcort_ROI, YeoNet, conn_type) %>%
  summarise(nets_avg_pint_diff = mean(pint_diff),
            nets_avg_vpint_diff = mean(vpint_diff),
            nets_avg_surf_diff = mean(surf_diff)
            ) %>%
  ungroup() %>%
  gather(comparison, nets_avg, nets_avg_pint_diff, nets_avg_vpint_diff, nets_avg_surf_diff) %>%
  spread(conn_type, nets_avg) %>%
  mutate(focus_effect = same_net - diff_net)

net_focus %>%
  ungroup() %>%
  group_by(subcort_ROI, YeoNet, comparison) %>%
  do(tidy(t.test(.$focus_effect))) %>%
  kable()
```

Another (maybe better) way to test this is to show calculate the "focusing" value in individual subjects THAN compute how this number changes with PINT. Let try that..

```{r sub-focus-tstats}
subject_focus <- net_means %>%
  drop_VI_DA_LI() %>%
  gather(vertex_type, nets_avg, netmean_pvertex, netmean_tvertex, netmean_tvolume) %>%
  ungroup(subcort_NET) %>%
  group_by(subject, subcort_ROI, YeoNet, vertex_type, conn_type) %>%
  summarise(nets_type_avg = mean(nets_avg)) %>%
  spread(conn_type, nets_type_avg) # %>%
  # ungroup() %>%
  # mutate(focus_effect = same_net - diff_net)

subject_focus %>%
  ungroup() %>%
  group_by(subcort_ROI, YeoNet, vertex_type) %>%
  do(tidy(t.test(.$same_net, .$diff_net, paired = TRUE))) %>%
  mutate(cohenD = statistic/sqrt(parameter + 1)) %>%
  kable()
```



```{r stiatum-rainclouds}
subcortical_raincloud(subject_focus, "striatum")
```

```{r thalamus-rainclouds}
subcortical_raincloud(subject_focus, "thalamus")
```
```{r cerebellum-raincloud}
subcortical_raincloud(subject_focus, "cerebellum")
```





```{r}

subject_focus %>%
  ungroup() %>% 
  mutate(focus_effect = same_net - diff_net) %>%
  select(subject, YeoNet, vertex_type, subcort_ROI, focus_effect) %>%
  spread(vertex_type, focus_effect) %>%
  group_by(subcort_ROI, YeoNet) %>%
  do(tidy(t.test(.$netmean_pvertex, .$netmean_tvertex, paired = TRUE))) %>%
  mutate(cohenD = statistic/sqrt(parameter + 1)) %>%
  kable()
```
```{r}
subject_focus %>%
  ungroup() %>% 
  mutate(focus_effect = same_net - diff_net) %>%
  select(subject, YeoNet, vertex_type, subcort_ROI, focus_effect) %>%
  spread(vertex_type, focus_effect) %>%
  group_by(subcort_ROI, YeoNet) %>%
  do(tidy(t.test(.$netmean_tvertex, .$netmean_tvolume, paired = TRUE))) %>%
  mutate(cohenD = statistic/sqrt(parameter + 1)) %>%
  kable()
```





Recreating the DM plot from the poster to double check

```{r DM-cerebellum-plot-part1, eval = FALSE}

net_means <- results_pheno %>%
  ungroup() %>%
  group_by(YeoNet, subcort_ROI, subcort_NET, subject) %>%
  summarise(netmean_pvertex = mean(pvertex_corr),
            netmean_tvertex = mean(tvertex_corr),
            pint_diff = netmean_pvertex - netmean_tvertex) 

pint_diff_sub_DM <- net_means %>%
  ungroup() %>% 
  filter(YeoNet == "DM", subcort_ROI == "cerebellum") %>%
  select(subject, subcort_NET, pint_diff) %>%
  spread(subcort_NET, pint_diff) %>%
  mutate(overall_pint_diff = DM - (SM + VA + FP + DA)/4,
         x_val = '') %>%
  select(subject, overall_pint_diff, x_val) %>%
  ggplot(aes(y = overall_pint_diff, x = x_val)) +
    geom_boxplot(outlier.shape = NA) +
    geom_jitter(alpha = 0.3, color = YeoNet_colours$DM, fill = "grey") +
    geom_hline(yintercept = 0) + 
    labs(y = "Change in correlation after PINT", x = "Cerebellum DM - Others") +
  scale_y_continuous(limits = c(-0.3, 0.3))

DM_submeans_plot <- net_means %>%
  mutate(is_DM = if_else(subcort_NET == 'DM', TRUE, FALSE),
         SubCortNET = factor(subcort_NET, levels = c("DM", "SM", "DA", "VA", "FP"))) %>%
  filter(subcort_ROI == "cerebellum", !is.na(SubCortNET), YeoNet == "DM") %>%
  ggplot(aes(y = pint_diff, x = SubCortNET, color = is_DM)) +
  geom_boxplot(color = "black", outlier.shape = NA) + 
  geom_jitter(alpha = 0.3) +
  geom_hline(yintercept = 0) +
  scale_color_manual(values = c('black',YeoNet_colours$DM)) +
  labs(y = "Change in correlation after PINT", color = NULL, x = "Subregion of Cerebellum") +
  theme(legend.position = "none") +
  scale_y_continuous(limits = c(-0.3, 0.3))

# DM_brain_pic <- ggdraw + draw_image('DM_striatum_pic.png')

plot_grid(pint_diff_sub_DM, DM_submeans_plot, rel_widths = c(1,2.5))
```



