---
title: "Whole Connectome Stats"
output:
  html_document:
    keep_md: true
---

# Whole Connectome Results

We are now going to see if there is anything in cortical-cortical connectivity by running the matrix of all possible connections instead of just subcortical-cortical stats. 

```{r message=FALSE, warning=FALSE}
library(tidygraph)
library(tidyverse)
library(broom)
library(knitr)
library(cowplot)
library(igraph)
library(ggraph)
library(here)
```

## The paths to data


```{r setting paths}
# These functions are for reading timeseries files
source(here('code/R/settings_helpers.R'))
source(here('code/R/file_reading_helpers.R'))

pheno <- read_pheno_file()%>%
  drop_na(DX)
YeoNet_colours <- define_Yeo7_colours()
Yeo7_2011_80verts <- read_Yeo72011_template()  

```

# Code for reading in all the timeseries..


A table that describes the current expected subortical files



These functions are for reading timeseries files




This reads all files and generate PINT to subcortical correlation values for a given subject

```{r read and correlated function}

the_subcortical_guide <- get_subcortical_guide()

#run_read_subject_subcort_corrs(subcort_outputlist$subid[1])

```

## This was run once in order to detemine the too small subcortical ROIs

```{r eval = FALSE}
read_vx_count <- function(filepath) {
  read_csv(filepath, col_names = FALSE) %>%
    mutate(network = c('VI','SM','DA','VA', 'LI','FP','DM')) 
}

vx_counts <- the_subcortical_guide %>%
  select(subcort_hemi, subcort_ROI) %>%
  distinct() %>%
  mutate(vx_count = str_c(output_base,'/ZHH/out/ciftify_meants/templates/7RSN_roi-',subcort_hemi, subcort_ROI,'_vxcount.txt')) %>%
mutate(vxnum = map(vx_count, ~read_vx_count(.x))) %>%
  unnest() %>%
  select(subcort_hemi, subcort_ROI, X1, network) %>%
  rename(numvx = X1)

write_csv(vx_counts, '../templates/subcort_vxcounts.csv')
```



```{r}
node_annotations <- get_node_annotations(Yeo7_2011_80verts, the_subcortical_guide)
```



### This reads all the subcortical files it can find

Write a func_base and outputprefix cols into the pheno file for the file reading step

```{r}
pheno <- pheno %>%
  mutate(func_base = get_func_base_from_pint_summary_filename(filename,subject, session), 
         outputprefix = construct_output_prefix(subject, session, func_base)) 
```

```{r eval = FALSE}
map2(pheno$outputprefix[1], pheno$dataset[1],
                              ~run_read_all_subject_timeseries_and_wholebrain_corZ(.x, .y))
```


```{r read all the data}

all_corZ_results <- pheno %>%
  select(subject, outputprefix, dataset) %>%
  mutate(the_corrs = map2(.$outputprefix, .$dataset,
                              ~run_read_all_subject_timeseries_and_wholebrain_corZ(.x, .y)))
```

```{r cache-subcort-Rdata}
save(all_corZ_results, file = file.path(output_base, "all_qa_passes_group", "Rdata_cache", "06_wholebrain_results_cache.Rdata"))
```

```{r load-cached-results, eval=FALSE}
load(file.path(output_base, "all_qa_passes_group", "Rdata_cache", "06_wholebrain_results_cache.Rdata"))
```


### merge with the phenotypic data

```{r merge with pheno and clean}
results_pheno <- all_corZ_results %>%
  inner_join(pheno, by = c("subject", "dataset")) %>%
  unnest()  

```


```{r eval = FALSE}
results_pheno
```

```{r}
DX_lm_model_full <- results_pheno %>%
  semi_join(node_annotations, by = c("to"="node_name")) %>%
  semi_join(node_annotations, by = c("from"="node_name")) %>%
  mutate(corZ = weight) %>%
  group_by(vertex_type, to, from) %>%
  do(tidy(lm(corZ ~ DX + Age_pt + Sex + fd_mean_pt + Scanner,.))) 
```


```{r}
annotated_graph_edges <- DX_lm_model_full %>%
  ungroup() %>%
  select(to, from) %>%
  distinct() %>%
  inner_join(node_annotations, by = c("to"="node_name")) %>%
  inner_join(node_annotations, by = c("from"="node_name"), suffix = c('_to','_from')) %>%
  unite(from_to_type, etype_from, etype_to) %>%
  unite(hemis, hemi_from, hemi_to, sep = "") %>%
  unite(networks, network_from, network_to, sep = "", remove = FALSE) %>%
  mutate(from_to_type = recode(from_to_type, "Cort_SubCort" = "SubCort_Cort")) %>%
  mutate(hemis = recode(hemis, "RL" = "LR")) 

```

## filters out some unwanted edges before FDR correction

```{r}
DX_lm_model <- DX_lm_model_full %>%
  ungroup() %>%
  inner_join(annotated_graph_edges, by = c("to", "from")) %>%
  mutate(withinsubcort = if_else((from_to_type == "SubCort_SubCort") & (subcort_ROI_from == subcort_ROI_to), "drop", "keep")) %>%
  filter(withinsubcort == "keep") %>%
  select(vertex_type, to, from, term, statistic, p.value) %>%
  ungroup() %>%
  group_by(term) %>%
  mutate(p_FDR = p.adjust(p.value, method = "fdr")) %>%
  arrange(p.value)
```

## Make co

```{r fig.height=10, fig.width=10}
source(here('code/R/swirly_plot_helpers.R'))
DX_lm_model %>%
  ungroup() %>%
  ## filtering steps
  filter(term == "DXSSD") %>%
  filter(vertex_type == "pvertex") %>%
  
  ## make a pretty plot
  make_swirly_results_plot(pos_label = "SSD > HC", 
                      neg_label = "HC > SSD",
                      plot_title = "Personalized",
                      node_annotations = node_annotations)
```


```{r fig.height=10, fig.width=10}
DX_lm_model %>%
  ungroup() %>%
  filter(term == "DXSSD") %>%
  filter(vertex_type == "tvertex") %>%
  make_swirly_results_plot(pos_label = "SSD > HC", 
                      neg_label = "HC > SSD",
                      plot_title = "Template",
                      node_annotations = node_annotations)
```


```{r fig.height=10, fig.width=10}
DX_lm_model %>%
  ungroup() %>%
  filter(term == "DXSSD") %>%
  filter(vertex_type == "tvolume") %>%
  make_swirly_results_plot(pos_label = "SSD > HC", 
                      neg_label = "HC > SSD",
                      plot_title = "Volume",
                      node_annotations = node_annotations)
```

## make table FDR corrected Edges that survive correction

```{r}
DX_lm_model %>%
  inner_join(annotated_graph_edges, by = c("to", "from")) %>%
  mutate(sig_edge = if_else(p_FDR < 0.05, "sig", "ns"),
         stat_pos = if_else(statistic > 0, "pos", "neg")) %>%
  filter(term == "DXSSD") %>% 
  count(vertex_type, from_to_type, sig_edge) %>%
  spread(sig_edge, n) %>%
  mutate(perc_sig = sig/(ns + sig)*100)

```



```{r}
#' convert from three col graph df to adjacency matrix
uppertri_df_to_agjmat <- function(graph_df) {
  
names(graph_df) <- c('to', 'from', 'myattr')
matrix_out <- graph_df %>%
  graph_from_data_frame(.,directed = F) %>%
  get.adjacency(., type = "both", attr = "myattr") %>%
  as.matrix() 
return(matrix_out)
}

#' go uppertri data to full dataframe for geom_tile
uppertri_df_to_full <- function(graph_df) {
result <- graph_df %>%
  uppertri_df_to_agjmat() %>%
  as.data.frame() %>%
  mutate(to = row.names(.)) %>%
  gather(from, value, -to) 
return(result)
}
```





```{r fig.height=20, fig.width= 12}
DX_lm_model %>%
  filter(term == "DXSSD") %>%
  mutate(t_filtered = if_else(p_FDR < 0.1, statistic, 0)) %>%
  ungroup() %>%
  select(vertex_type, to, from, t_filtered) %>%
  group_by(vertex_type) %>%
  nest() %>%
  mutate(uptri = map(data, uppertri_df_to_full)) %>%
  unnest(uptri) %>%
  mutate(to_lab = factor(to, levels = (node_annotations %>% arrange(subcort_ROI, network))$node_name),
         from_lab = factor(from, levels = (node_annotations %>% arrange(subcort_ROI, network))$node_name)) %>%
  ggplot(aes(x=to_lab, y=from_lab, fill=value)) + 
  geom_tile(color = "white") +
  scale_fill_gradient2(high = "#b2182b", mid = "white", low = "#2166ac") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  facet_wrap(~vertex_type, ncol = 1) +
  labs(title = "T statistic for effect of DX (thesholded)",
       x = NULL, y = NULL, fill = "T statistic for DX")
```

`













```{r fig.height=12, fig.width= 12}
full_DX_mat <- DX_lm_model %>%
  filter(term == "DXSSD", vertex_type == "pvertex") %>%
  ungroup() %>%
  select(to, from, statistic) %>%
  uppertri_df_to_full() 

full_DX_mat %>%
  mutate(to_lab = factor(to, levels = node_annotations$node_name), 
         from_lab = factor(from, levels = node_annotations$node_name)) %>%
  ggplot(aes(x=to_lab, y=from_lab, fill=value)) + 
  geom_tile(color = "white") +
  scale_fill_gradient2(high = "#b2182b", mid = "white", low = "#2166ac") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(title = "T statistic for effect of DX",
       x = NULL, y = NULL, fill = "T statistic for DX")
```

```{r}

calc_fc_weights <- function(lm_df, t_threshold) {
  
    full_DX_mat <- lm_df %>%
      ungroup() %>%
      select(to, from, statistic) %>%
      uppertri_df_to_full() %>%
      inner_join(node_annotations, by = c("to"="node_name")) %>%
      inner_join(node_annotations, by = c("from"="node_name")) 
    
hypo_cerebullum_to_striatum <- full_DX_mat %>%
    filter(subcort_ROI.x == "cerebellum") %>%
    filter(subcort_ROI.y == "striatum") %>%
    filter(value < -t_threshold) %>%
    select(to, from, value) 

hyper_subcort_to_SM <- full_DX_mat %>%
    filter(etype.x == "SubCort") %>%
    filter(etype.y == "Cort") %>%
    filter(as.character(network.y) %in% c("SM")) %>%
    filter(value > t_threshold) %>%
    select(to, from, value)

hyper_subcort_to_VI <- full_DX_mat %>%
    filter(etype.x == "SubCort") %>%
    filter(etype.y == "Cort") %>%
    filter(as.character(network.y) %in% c("VI")) %>%
    filter(value > t_threshold) %>%
    select(to, from, value)

hyper_subcort_to_DM <- full_DX_mat %>%
    filter(etype.x == "SubCort") %>%
    filter(etype.y == "Cort") %>%
    filter(as.character(network.y) %in% c("DM")) %>%
    filter(value > t_threshold) %>%
    select(to, from, value)

hypo_subcort_to_FP <- full_DX_mat %>%
    filter(etype.x == "SubCort") %>%
    filter(etype.y == "Cort") %>%
    filter(as.character(network.y) %in% c("FP")) %>%
    filter(value < -t_threshold) %>%
    select(to, from, value)

hypo_subcort_to_VA <- full_DX_mat %>%
    filter(etype.x == "SubCort") %>%
    filter(etype.y == "Cort") %>%
    filter(as.character(network.y) %in% c("VA")) %>%
    filter(value < -t_threshold) %>%
    select(to, from, value)

hyper_cortSMVI_to_rest <- full_DX_mat %>%
    filter(etype.x == "Cort") %>%
    filter(etype.y == "Cort") %>%
    filter(as.character(network.x) %in% c("SM", "VI")) %>%
    filter(as.character(network.y) %in% c("FP","DA", "VA", "DM")) %>%
    filter(value > t_threshold) %>%
    select(to, from, value)

hyper_cortVA_to_DA <- full_DX_mat %>%
    filter(etype.x == "Cort") %>%
    filter(etype.y == "Cort") %>%
    filter(as.character(network.x) %in% c("VA")) %>%
    filter(as.character(network.y) %in% c("DA")) %>%
    filter(value > t_threshold) %>%
    select(to, from, value)

hypo_cortDM_to_rest <- full_DX_mat %>%
    filter(etype.x == "Cort") %>%
    filter(etype.y == "Cort") %>%
    filter(as.character(network.x) %in% c("DM")) %>%
    filter(!(as.character(network.y) %in% c("DM"))) %>%
    filter(value < -t_threshold) %>%
    select(to, from, value)

Fz_weigths <-bind_rows(hypo_cortDM_to_rest = hypo_cortDM_to_rest,
                       hyper_cortSMVI_to_rest = hyper_cortSMVI_to_rest,
                       hyper_cortVA_to_DA = hyper_cortVA_to_DA,
                       hyper_subcort_to_DM = hyper_subcort_to_DM,
                       hypo_subcort_to_FP = hypo_subcort_to_FP,
                       hypo_subcort_to_VA = hypo_subcort_to_VA,
                       hyper_subcort_to_SM = hyper_subcort_to_SM,
                       hyper_subcort_to_VI = hyper_subcort_to_VI,
                       hypo_cerebullum_to_striatum = hypo_cerebullum_to_striatum,
                       .id = "direction_edge_group") %>%
  separate(direction_edge_group, into = c("effect_direction", "edge_group"), extra = "merge") %>%
  rename(edge_FC_weight = value)

  return(Fz_weigths)

}
  
```



```{r}
t_threshold = 1.1

Fz_DXweigths_pvertex <- DX_lm_model %>%
  filter(term == "DXSSD", vertex_type == "pvertex") %>%
  ungroup() %>%
  calc_fc_weights(.,t_threshold)

Fz_DXweigths_tvertex <- DX_lm_model %>%
  filter(term == "DXSSD", vertex_type == "tvertex") %>%
  ungroup() %>%
  calc_fc_weights(.,t_threshold)

Fz_DXweigths_tvolume <- DX_lm_model %>%
  filter(term == "DXSSD", vertex_type == "tvolume") %>%
  ungroup() %>%
  calc_fc_weights(.,t_threshold)

Fz_DXweigths <- bind_rows(pvertex = Fz_DXweigths_pvertex,
                     tvertex = Fz_DXweigths_tvertex,
                     tvolume = Fz_DXweigths_tvolume,
                     .id = "vertex_type") 
Fz_DXweigths %>% 
  group_by(vertex_type, edge_group, effect_direction) %>%
  summarise(median_weight = median(edge_FC_weight)) %>%
  ggplot(aes(y = abs(median_weight), x = vertex_type, color = edge_group)) +
    geom_point() +
    geom_line(aes(group = edge_group))
  
```
```{r}
Fz_DXweigths %>% 
  count(edge_group, vertex_type, effect_direction) %>%
  spread(vertex_type, n)


```
```{r}
Fz_DXweigths %>% 
  group_by(vertex_type, edge_group, effect_direction) %>%
  summarise(median_weight = median(edge_FC_weight)) %>%
  spread(vertex_type, median_weight)
```
```{r}
write_csv(Fz_DXweigths_pvertex, file.path(output_base, "all_qa_passes_group", "weighted_subject_FC_weigths", "SSD4cohorts_DXtweigths_pvertex.csv"))
write_csv(Fz_DXweigths_tvertex, file.path(output_base, "all_qa_passes_group", "weighted_subject_FC_weigths", "SSD4cohorts_DXtweigths_tvertex.csv"))
write_csv(Fz_DXweigths_tvolume, file.path(output_base, "all_qa_passes_group", "weighted_subject_FC_weigths", "SSD4cohorts_DXtweigths_tvolume.csv"))
```

```{r}

#' calculates a subjects weigthed FC score from their edgewise values
#'
#' @param subject_edges_df tibble with columns subject, to, from, and weight
#' @param edge_weights tibble with columns effect_direction, edge_group, to, from, and edge_FC_weight
#'
#' @return tibble with columns subject, dataset, effect_direction, edge_group, FC_subtype and wFC_score
#'
#' @examples
calc_subjects_wFC_score <- function(subject_edges_df, edge_weights) {
  result <- subject_edges_df %>%
  ungroup() %>%
  group_by(subject, dataset) %>%
  nest() %>%
  mutate(uptri = map(data, uppertri_df_to_full)) %>%
  unnest(uptri) %>%
  inner_join(edge_weights, by = c("to", "from")) %>%
  ungroup() %>%
  mutate(wcorZ = abs(edge_FC_weight) * value) %>%
  group_by(subject, dataset, effect_direction, edge_group) %>%
  summarise(wFC_score = sum(wcorZ)/sum(abs(edge_FC_weight)),
            mFC_score = mean(value)) %>%
  ungroup()
  return(result)
}
```


```{r}
pvertex_subject_FC_scores <- results_pheno %>%
  ungroup() %>%
  filter(vertex_type == "pvertex") %>%
  select(subject, dataset, to, from, weight) %>%
  calc_subjects_wFC_score(Fz_DXweigths_pvertex)

tvertex_subject_FC_scores <- results_pheno %>%
  ungroup() %>%
  filter(vertex_type == "tvertex") %>%
  select(subject, dataset, to, from, weight) %>%
  calc_subjects_wFC_score(Fz_DXweigths_tvertex)

tvolume_subject_FC_scores <- results_pheno %>%
  ungroup() %>%
  filter(vertex_type == "tvolume") %>%
  select(subject, dataset, to, from, weight) %>%
  calc_subjects_wFC_score(Fz_DXweigths_tvolume)

FC_scores_together <- bind_rows(
  pvertex = pvertex_subject_FC_scores,
  tvertex = tvertex_subject_FC_scores,
  tvolume = tvolume_subject_FC_scores,
  .id = "vertex_type"
)

write_csv(FC_scores_together, file.path(output_base, 
                                        "all_qa_passes_group", 
                                        "weighted_subject_FC_scores",
                                        "SSD4cohorts_DXweighted_subject_scores.csv"))
```




```{r}
FC_scores_lmfit <- FC_scores_together %>%
  inner_join(pheno, by = c("subject", "dataset")) %>%
  ungroup() %>%
  group_by(edge_group, effect_direction, vertex_type) %>%
  do(tidy(lm(wFC_score ~ DX + Age_pt + Sex + fd_mean_pt + Site,.))) 

FC_scores_lmfit %>%
  select(edge_group, effect_direction, term, statistic, p.value) %>%
  filter(term == "DXSSD") %>%
  knitr::kable()

FC_scores_lmfit %>% 
  group_by(vertex_type, edge_group, effect_direction) %>%
  filter(term == "DXSSD",
         str_detect(edge_group,"subcort")) %>%
  ggplot(aes(y = abs(statistic), x = rev(vertex_type), color = edge_group)) +
    geom_point() +
    geom_line(aes(group = edge_group))
```
```{r}
FC_scores_lmfit <- FC_scores_together %>%
  inner_join(pheno, by = c("subject", "dataset")) %>%
  ungroup() %>%
  group_by(edge_group, vertex_type,  effect_direction, Site) %>%
  do(tidy(lm(wFC_score ~ DX + Age_pt + Sex + fd_mean_pt,.))) 

FC_scores_lmfit %>%
  select(edge_group, vertex_type, Site, term, statistic, p.value) %>%
  filter(term == "DXSSD") %>%
  knitr::kable()

FC_scores_lmfit %>% 
  filter(term == "DXSSD",
         str_detect(edge_group,"subcort")) %>%
  ggplot(aes(y = abs(statistic), x = rev(vertex_type), color = edge_group)) +
    geom_point() +
    geom_line(aes(group = edge_group)) +
  facet_wrap(~Site, nrow = 1)
```

```{r eval = FALSE}
SSD_cors <- FC_scores_together %>%
  inner_join(pheno, by = c("subject", "dataset")) %>%
  ungroup() %>%
  filter(DX == "SSD", vertex_type == "pvertex") %>%
  select(subject, dataset, edge_group, wFC_score) %>%
  spread(edge_group, wFC_score) %>%
  select(-subject, -dataset) %>%
  cor(.) 

heatmap(abs(SSD_cors))
```

```{r eval = FALSE}
HC_cors <- FC_scores_together %>%
    inner_join(pheno, by = c("subject", "dataset")) %>%
  ungroup() %>%
  filter(DX == "CTRL", vertex_type == "pvertex") %>%
  select(subject, dataset, edge_group, wFC_score) %>%
  spread(edge_group, wFC_score) %>%
  select(-subject, -dataset) %>%
  cor(.) 

heatmap(abs(HC_cors))
  
```

```{r}
# Marginal densities along x axis
plot_DX_scatter_elipsed <- function(df, x, y) {
  #the tidy eval ness
  xvar <- enquo(x)
  yvar <- enquo(y)
  # make the main scatte bit using above
  main_scatter <-  ggplot(data = df, 
               aes(x = !!xvar, y = !!yvar, color = DX)) +
  geom_point(alpha = 0.7, size = 0.7) +
  stat_ellipse() +
  scale_color_manual(values = c("grey20","red"))

  xdens <- axis_canvas(main_scatter, axis = "x")+
    geom_density(data = df, aes(x = !!xvar, fill = DX),
              alpha = 0.5, size = 0.2) +
    scale_fill_manual(values = c("grey20","red"))

  ydens <- axis_canvas(main_scatter, axis = "y", coord_flip = TRUE)+
    geom_density(data = df, aes(x = !!yvar, fill = DX),
                alpha = 0.5, size = 0.2) +
  scale_fill_manual(values = c("grey20","red")) +
  coord_flip()
  
  #putting the peices together
  p1 <- insert_xaxis_grob(main_scatter, xdens, grid::unit(.2, "null"), position = "top")
  p2<- insert_yaxis_grob(p1, ydens, grid::unit(.2, "null"), position = "right")
  return(p2)
}
```


```{r , fig.height=4, fig.width = 5}
library(cowplot)
fplot <- FC_scores_together %>%
  inner_join(pheno, by = c("subject", "dataset")) %>%
  ungroup() %>%
  filter(vertex_type == "pvertex") %>%
  unite(directed_edge_group, effect_direction, edge_group) %>%
  unite(dat_sub, dataset, subject) %>%  
  select(dat_sub, Site, DX, directed_edge_group, wFC_score) %>%
  spread(directed_edge_group, wFC_score) 

```




```{r, fig.width=5, fig.height = 4}
ggdraw(plot_DX_scatter_elipsed(fplot, x = hyper_subcort_to_VI, y = hypo_cerebullum_to_striatum))
```
```{r, fig.width=5, fig.height = 4}
ggdraw(plot_DX_scatter_elipsed(fplot, x = hyper_subcort_to_SM, y = hypo_cerebullum_to_striatum))
```


```{r, fig.height=4, fig.width=6}
fig1 <- fplot %>%
  ggplot(aes(y = hypo_subcort_to_FP, x = DX, color = DX)) + 
  geom_boxplot(outlier.shape = NA) + 
  geom_dotplot(binaxis = 'y', stackdir = 'center', binwidth = 0.01, alpha = 0.5) +
  scale_color_manual(values = c("grey20","red")) +
  facet_wrap( ~ Site, ncol = 4) +
  labs(x = NULL)

#ggsave(fig1, filename = 'VA_results.png',height = 8, width = 5)

fig1
```


```{r, fig.height=4, fig.width=6}
fig1 <- fplot %>%
  ggplot(aes(y = hyper_subcort_to_SM, x = DX, color = DX)) + 
  geom_boxplot(outlier.shape = NA) + 
  geom_dotplot(binaxis = 'y', stackdir = 'center', binwidth = 0.01, alpha = 0.5) +
  scale_color_manual(values = c("grey20","red")) +
  facet_wrap( ~ Site, ncol = 4) +
  labs(x = NULL)

#ggsave(fig1, filename = 'VA_results.png',height = 8, width = 5)

fig1
```


# calculate weighted subject scores by chopping up the matrix


```{r}
YeoNet7 <- define_YeoNet7_colours()
node_annotations1 <- node_annotations %>%
  mutate(node_grouping  = if_else(etype == "Cort",
                                  str_c("Cort", cort_NET),
                                  as.character(subcort_ROI))) 

node_groupings <- factor(1:9, 
                         levels = c(1:9),
                         labels = c(levels(node_annotations$subcort_ROI),
                                    str_c("Cort",YeoNet7$network[1:6])))
edge_grouping_guide <- matrix(1, 
                  nrow = length(node_groupings),
                  ncol = length(node_groupings),
                  dimnames = list(node_groupings,
                                  node_groupings)) %>%
    graph_from_adjacency_matrix(mode="upper", 
                                weighted=T, diag=T) %>%
    as_data_frame() %>%
  filter(!(from %in% c("striatum", "thalamus", "cerebellum") & to == from)) %>%
  select(to, from)


```

```{r}
t_threshold = 1.1
define_hypohyper_weights <- function(lm_df, t_threshold, node_annotations, edge_guide) {
full_DX_mat <- lm_df %>%
      ungroup() %>%
      select(to, from, statistic) %>%
      uppertri_df_to_full() %>%
      inner_join(node_annotations, by = c("to"="node_name")) %>%
      inner_join(node_annotations, by = c("from"="node_name")) 
    
pos_weights <- full_DX_mat %>%
    filter(value > t_threshold) %>%
    semi_join(edge_grouping_guide, by = c("node_grouping.x" = "to",
                                          "node_grouping.y" = "from")) %>%
    unite(edge_group, node_grouping.x, node_grouping.y) %>%
    select(edge_group, to, from, value)

neg_weights <- full_DX_mat %>%
    filter(value < -t_threshold) %>%
    semi_join(edge_grouping_guide, by = c("node_grouping.x" = "to",
                                          "node_grouping.y" = "from")) %>%
    unite(edge_group, node_grouping.x, node_grouping.y) %>%
    select(edge_group, to, from, value)

all_weights <- bind_rows(hyper = pos_weights,
                        hypo = neg_weights,
                        .id = "effect_direction")
return(all_weights)
}

define_vertex_hypohyper_weights <- function(lm_df, v_type, t_threshold) {
  groupwise_weights <- lm_df %>%
  filter(term == "DXSSD", 
         vertex_type == v_type) %>%
  ungroup() %>%
  define_hypohyper_weights(., t_threshold,
                           node_annotations = node_annotations1,
                           edge_guide = edge_guide)
  return(groupwise_weights)
}

groupwise_weights <- tibble(vertex_type = c("pvertex", "tvertex", "tvolume")) %>%
  mutate(result = map(vertex_type, 
                      ~ define_vertex_hypohyper_weights(DX_lm_model, .x, t_threshold))) %>%
  unnest()
```

```{r}
size_threshold = 30

groupwise_weights_table <- groupwise_weights %>%
  count(vertex_type, effect_direction, edge_group) %>%
  spread(effect_direction, n, fill = 0) %>%
  group_by(edge_group) %>%
  mutate(hyperhypo_diff = (hyper - hypo)/(hyper + hypo),
         use_hypo = max(hyperhypo_diff) < 0.1 & min(hypo) > size_threshold,
         use_hyper = min(hyperhypo_diff) > -0.1 & min(hyper) > size_threshold,
         num = use_hypo + use_hyper) %>%
  select(num, use_hypo, use_hyper, everything()) %>%
  arrange(num, edge_group, vertex_type) 
  # ungroup() %>%
  # select(vertex_type, edge_group, hyperhypo_diff, max_size) %>%
  # gather(tmp_col, tmp_vals, hyperhypo_diff, max_size) %>%
  # unite(vertex_meas, tmp_col, vertex_type) %>%
  # spread(vertex_meas, tmp_vals) %>%
  # arrange(-abs(hyperhypo_diff_tvolume))

```

```{r}
edge_groups_to_use <- groupwise_weights_table %>%
  ungroup() %>%
  select(use_hypo, use_hyper, edge_group) %>%
  distinct() %>%
  filter(use_hypo | use_hyper)
```

```{r}
hyper_edgegroups <- edge_groups_to_use %>% filter(use_hyper) %>% pull(edge_group)
hypo_edgegroups <- edge_groups_to_use %>% filter(use_hypo) %>% pull(edge_group)
groupwise_weights_hyper <- groupwise_weights %>%
  filter(edge_group %in% hyper_edgegroups,
         effect_direction == "hyper")

groupwise_weights_hypo <- groupwise_weights %>%
  filter(edge_group %in% hypo_edgegroups,
         effect_direction == "hypo")

groupwise_weights_both <- bind_rows(
  groupwise_weights_hypo,
  groupwise_weights_hyper
) %>%
  rename(edge_FC_weight = value)

groupwise_weights_both %>%
  count(vertex_type, effect_direction, edge_group) %>%
  ggplot(aes(y = n, x = vertex_type, color = edge_group)) +
  geom_point() +
  geom_line(aes(group = edge_group)) +
  facet_wrap(~effect_direction)
```
```{r}
file.path(output_base, 
                                        "all_qa_passes_group", 
                                        "weighted_subject_FC_weigths",
                                        'SSD4cohorts_DXweighted_moregroups_subject_weights.csv')
```


```{r}
groupwise_weights_both %>%
  mutate(node_class = if_else(str_detect(edge_group,'_Cort'), 
                 "Within_Cortical",
                 "Subcortical_to")) %>%
  group_by(vertex_type, effect_direction, edge_group, node_class) %>%
  summarise(median_t = median(edge_FC_weight)) %>%
  ggplot(aes(y = abs(median_t), x = vertex_type, color = edge_group)) +
  geom_point() +
  geom_line(aes(group = edge_group)) +
  facet_wrap(~effect_direction*node_class)
```
```{r}
write_csv(groupwise_weights_both, file.path(output_base, 
                                        "all_qa_passes_group", 
                                        "weighted_subject_FC_weigths",
                                        'SSD4cohorts_DXweighted_moregroups_subject_weights.csv'))
```



```{r}

all_subject_FC_weights_by_vertex <- function(results_data, edge_weights, vtype) {
result <- results_data %>%
  ungroup() %>%
  filter(vertex_type == vtype) %>%
  select(subject, dataset, to, from, weight) %>%
  calc_subjects_wFC_score(edge_weights %>% filter(vertex_type == vtype))
return(result)
}

all_subject_FC_weights <- tibble(vertex_type = c("pvertex", "tvertex", "tvolume")) %>%
  mutate(result = map(vertex_type, 
                      ~all_subject_FC_weights_by_vertex(results_pheno, groupwise_weights_both, .x))) %>%
  unnest()
```

```{r}

write_csv(all_subject_FC_weights, file.path(output_base, 
                                        "all_qa_passes_group", 
                                        "weighted_subject_FC_scores",
                                        'SSD4cohorts_DXweighted_moregroups_subject_scores.csv'))
```

```{r}
FC_gscores_lmfit <- all_subject_FC_weights %>%
  inner_join(pheno, by = c("subject", "dataset")) %>%
  ungroup() %>%
  group_by(effect_direction, edge_group, vertex_type) %>%
  do(tidy(lm(wFC_score ~ DX + Age_pt + Sex + fd_mean_pt + Site,.))) 

FC_gscores_lmfit %>%
  select(effect_direction, edge_group, vertex_type, term, statistic, p.value) %>%
  filter(term == "DXSSD") %>%
  knitr::kable()

FC_gscores_lmfit %>% 
  mutate(node_class = if_else(str_detect(edge_group,'_Cort'), 
                 "Within_Cortical",
                 "Subcortical_to")) %>%
  group_by(vertex_type, effect_direction, edge_group, node_class) %>%
  filter(term == "DXSSD") %>%
  ggplot(aes(y = abs(statistic), x = rev(vertex_type), color = edge_group)) +
    geom_point() +
    geom_line(aes(group = edge_group)) +
  facet_wrap(~effect_direction*node_class)
```
```{r}
FC_gscores_lmfitbySite <- all_subject_FC_weights %>%
  inner_join(pheno, by = c("subject", "dataset")) %>%
  ungroup() %>%
  group_by(effect_direction, edge_group, vertex_type, Site) %>%
  do(tidy(lm(wFC_score ~ DX + Age_pt + Sex + fd_mean_pt,.))) 

FC_gscores_lmfitbySite %>%
  select(effect_direction, edge_group, Site, vertex_type, term, statistic, p.value) %>%
  filter(term == "DXSSD") %>%
  knitr::kable()

FC_gscores_lmfitbySite %>% 
  mutate(node_class = if_else(str_detect(edge_group,'_Cort'), 
                 "Within_Cortical",
                 "Subcortical_to")) %>%
  filter(term == "DXSSD",
         node_class == "Subcortical_to") %>%
  ggplot(aes(y = abs(statistic), x = rev(vertex_type), color = effect_direction)) +
    geom_point() +
    geom_line(aes(group = edge_group)) +
  facet_wrap(~Site)
```

```{r}
FC_gscores_lmfitbySite_mFC <- all_subject_FC_weights %>%
  inner_join(pheno, by = c("subject", "dataset")) %>%
  ungroup() %>%
  group_by(effect_direction, edge_group, vertex_type, Site) %>%
  do(tidy(lm(mFC_score ~ DX + Age_pt + Sex + fd_mean_pt,.))) 

FC_gscores_lmfitbySite_mFC %>%
  select(effect_direction, edge_group, Site, vertex_type, term, statistic, p.value) %>%
  filter(term == "DXSSD") %>%
  knitr::kable()

FC_gscores_lmfitbySite_mFC %>% 
  mutate(node_class = if_else(str_detect(edge_group,'_Cort'), 
                 "Within_Cortical",
                 "Subcortical_to")) %>%
  filter(term == "DXSSD",
         node_class == "Subcortical_to") %>%
  ggplot(aes(y = abs(statistic), x = rev(vertex_type), color = effect_direction)) +
    geom_point() +
    geom_line(aes(group = edge_group)) +
  facet_wrap(~Site)
```


```{r fig.height=7, fig.width=7}
wFC_corrs <- all_subject_FC_weights %>%
  filter(vertex_type == "pvertex") %>%
  select(subject, dataset, edge_group, wFC_score) %>%
  spread(edge_group, wFC_score) %>%
  select(-subject, -dataset) %>%
  cor(.)
heatmap(abs(wFC_corrs))
```

