---
title: "Whole Connectome Stats"
output:
  html_document:
    keep_md: true
---

# Whole Connectome Results

We are now going to see if there is anything in cortical-cortical connectivity by running the matrix of all possible connections instead of just subcortical-cortical stats. 

Adding the Schaefer template data to this analysis

```{r message=FALSE, warning=FALSE}
library(tidygraph)
library(tidyverse)
library(broom)
library(knitr)
library(cowplot)
library(igraph)
library(ggraph)
library(here)
```

## The paths to data


```{r setting paths}
# These functions are for reading timeseries files
source(here('code/R/settings_helpers.R'))
#

pheno <- read_pheno_file()%>%
  drop_na(DX) %>%
  filter(in_matched_sample)

YeoNet_colours <- define_Yeo7_colours()

Schaefer_labels <- read_Schaefer_template()
# these tables describe the subcortical data and combined node info
the_subcortical_guide <- get_subcortical_guide()

Schaefer_node_annots <- get_Schaefer_node_annotations(Schaefer_labels, the_subcortical_guide)

lm_predictor_col = c("DX")
lm_covar_cols <- c("Age_match_pt", 
                    "Sex",
                    "fd_mean_match_pt",
                    "Site")

```

# Code for reading in all the timeseries..


These functions are for reading timeseries files

This reads all files and generate PINT to subcortical correlation values for a given subject



#### This was run once in order to detemine the too small subcortical ROIs

```{r eval = FALSE}
read_vx_count <- function(filepath) {
  read_csv(filepath, col_names = FALSE) %>%
    mutate(network = c('VI','SM','DA','VA', 'LI','FP','DM')) 
}

vx_counts <- the_subcortical_guide %>%
  select(subcort_hemi, subcort_ROI) %>%
  distinct() %>%
  mutate(vx_count = str_c(output_base,'/ZHH/out/ciftify_meants/templates/7RSN_roi-',subcort_hemi, subcort_ROI,'_vxcount.txt')) %>%
mutate(vxnum = map(vx_count, ~read_vx_count(.x))) %>%
  unnest() %>%
  select(subcort_hemi, subcort_ROI, X1, network) %>%
  rename(numvx = X1)

write_csv(vx_counts, '../templates/subcort_vxcounts.csv')
```




### This reads all the subcortical files it can find

Write a func_base and outputprefix cols into the pheno file for the file reading step

```{r eval=FALSE}
pheno <- pheno %>%
  mutate(func_base = get_func_base_from_pint_summary_filename(filename,subject, session), 
         outputprefix = construct_output_prefix(subject, session, func_base)) 
```

a litle chunck I use to test if test if the reader is working...



### Use this chunk to test if the reader is working

```{r eval = FALSE}
run_read_all_subject_schaefer_timeseries_and_wholebrain_corZ(pheno$outputprefix[100], pheno$dataset[100])
```


### Reading all the data



```{r read all the schaefer data, eval=FALSE}

all_schaefer_results <- pheno %>%
  select(subject, outputprefix, dataset) %>%
  mutate(the_corrs = map2(outputprefix, dataset,
                              ~run_read_all_subject_schaefer_timeseries_and_wholebrain_corZ(.x, .y)))
```


```{r, eval=FALSE}
saveRDS(all_schaefer_results, file = file.path(output_base, "all_clinicalplusqa_group", "Rdata_cache", "06_wholebrainshaefer_FC_cache.rds"))
```

###  Use this section to the un-harmonized correlation matrixes

```{r}
all_corZ_results <- readRDS(file = file.path(output_base, "all_clinicalplusqa_group", "Rdata_cache", "06_wholebrainshaefer_FC_cache.rds"))
```




merging un-harmonized results with phenotypic data - now deprecated
```{r merge with pheno and clean eval = FALSE}
results_pheno <- all_corZ_results %>%
  inner_join(pheno, by = c("subject", "dataset")) %>%
  unnest(cols = c(the_corrs))  

```

```{r eval = FALSE}
rm(all_corZ_results)
```



## Combat Harmonize the correlation data

Run combat harmonization and save harmonized matrixes back to an intermediate file

```{r eval = FALSE}
library(neuroCombat)


pheno <- pheno %>%
  mutate(subject_dataset = str_c(subject, "_", dataset))

batch <- pheno$Site
mod <- model.matrix(~pheno$DX+pheno$Age_match_pt+ pheno$Sex)

tmp <- all_corZ_results %>%
  mutate(subject_dataset = str_c(subject, "_", dataset)) %>%
  unnest(the_corrs) %>%
  filter(vertex_type == "surfschaefer") %>%
  select(subject_dataset, from, to, weight) %>%
  pivot_wider(id_cols = c("to", "from"),
             names_from = "subject_dataset",
             values_from = "weight") 

the_edges <- tmp %>% select("to", "from")
  
data_for_harmonize_surf <- tmp %>%
  select(all_of(pheno$subject_dataset))

surf_harmonized <- neuroCombat(dat=data_for_harmonize_surf , batch=batch, mod=mod)


data_for_harmonize_vol <- all_corZ_results %>%
  mutate(subject_dataset = str_c(subject, "_", dataset)) %>%
  unnest(the_corrs) %>%
  filter(vertex_type == "volschaefer") %>%
  select(subject_dataset, from, to, weight) %>%
  pivot_wider(id_cols = c("to", "from"),
             names_from = "subject_dataset",
             values_from = "weight") %>%
  select(all_of(pheno$subject_dataset))

vol_harmonized <- neuroCombat(dat=data_for_harmonize_vol, 
                                  batch=batch, mod=mod)


combat_data_corZ <- bind_rows(
  surfschaefer = bind_cols(the_edges, as_tibble(surf_harmonized$dat.combat)),
  volschaefer = bind_cols(the_edges, as_tibble(vol_harmonized$dat.combat)),
  .id = "vertex_type")

saveRDS(combat_data_corZ, file = file.path(output_base, "all_clinicalplusqa_group", "Rdata_cache", "06_wholebrain_FC_Schaefercombat_cache.rds"))
```

### Load the cached combat-harmonized matrixes

```{r load-cached-results}
combat_data_corZ <- readRDS(file = file.path(output_base, "all_clinicalplusqa_group", "Rdata_cache", "06_wholebrain_FC_Schaefercombat_cache.rds"))
```


combine the combat - data with the phenotypic data

```{r}
pheno <- pheno %>% mutate(subject_dataset = str_c(subject, "_", dataset))

results_pheno <- combat_data_corZ %>%
  pivot_longer(all_of(pheno$subject_dataset),
               names_to = "subject_dataset",
               values_to = "weight") %>%
  inner_join(pheno, by = "subject_dataset")
```


### remove the phenotypic we don't use for this notebook from the df

```{r}
simpler_results <- results_pheno %>% 
  select(vertex_type, to, from, subject, dataset, weight, DX, all_of(lm_covar_cols))
```

```{r}
results_pheno <- ungroup(simpler_results)
```



# Running Networkwise models 

helpers functions for dealing with correlation matrixes

```{r}
#' convert from three col graph df to adjacency matrix
uppertri_df_to_agjmat <- function(graph_df) {
  
  names(graph_df) <- c("to", "from", "myattr")
  matrix_out <- graph_df %>%
    graph_from_data_frame(., directed = F) %>%
    as_adjacency_matrix(., type = "both", attr = "myattr", sparse = FALSE) #%>%
    #as.matrix() 
  return(matrix_out)
}

#' go uppertri data to full dataframe for geom_tile
uppertri_df_to_full <- function(graph_df) {
  result <- graph_df %>%
    uppertri_df_to_agjmat() %>%
    as.data.frame() %>%
    mutate(to = row.names(.)) %>%
    gather(from, value, -to) 
  return(result)
}

```

Defining function to reduce the whole brain correlation matrix to networkwise correlations




```{r}

networkg_order = c("CortLI", "CortDM","CortFP", "CortVA","CortDA","CortSM","CortVI", 
                   "striatum", "thalamus","cerebellum")

node_annotations1 <- Schaefer_node_annots %>%
  mutate(node_grouping  = if_else(etype == "Cort",
                                  str_c("Cort", as.character(network)),
                                  as.character(subcort_ROI))) %>%
  filter(!(etype == "SubCort" & numvx < 10))


within_tbw_net_corrs <- function(upper_tri_edges) {
  results <- upper_tri_edges %>%
  uppertri_df_to_full() %>%
  inner_join(node_annotations1 %>% select(node_name, node_grouping), 
             by = c("to" = "node_name")) %>%
  inner_join(node_annotations1 %>% select(node_name, node_grouping), 
             by = c("from" = "node_name"), suffix = c("_to", "_from")) %>%
  filter(!(to == from)) %>%
  group_by(node_grouping_to, node_grouping_from) %>%
  summarise(mean_corZ = mean(value), .groups = "keep") %>%
  
  # taking only the upper triangle 
  mutate(node_grouping_to  = factor(node_grouping_to, levels = networkg_order),
         node_grouping_from = factor(node_grouping_from, levels = networkg_order)) %>%
  arrange(node_grouping_to, node_grouping_from) %>%
  uppertri_df_to_agjmat() %>%
  graph_from_adjacency_matrix(mode="upper", 
                                weighted=T, diag=T) %>%
  as_data_frame()
  
  return(results)
}


# ### un-comment the line below to test the above function
# test_edges <- results_pheno %>%
#   select(vertex_type, subject, dataset, to, from, weight) %>%
#   group_by(vertex_type, subject, dataset) %>%
#   nest() %>%
#   slice(1) %>%
#   unnest(data) %>%
#   ungroup() %>%
#   select(to, from, weight)
# 
# within_tbw_net_corrs(test_edges)
```


```{r}
networkwise_corrz <- function(results_pheno_df) {
  result <- results_pheno_df %>%
  select(vertex_type, subject, dataset, to, from, weight) %>%
  ungroup() %>%
  group_by(vertex_type, subject, dataset) %>%
  nest() %>%
  mutate(results = map(data, ~within_tbw_net_corrs(.x))) %>%
  select(vertex_type, subject, dataset, results) %>%
  return(result)
}

## had to split this by vertex because of RAM issues on laptop
surf_networkwise <- results_pheno %>%
  filter(vertex_type == "surfschaefer") %>%
  networkwise_corrz()
vol_networkwise <- results_pheno %>%
  filter(vertex_type == "volschaefer") %>%
  networkwise_corrz()

networkwise_corrs <- bind_rows(
  surf_networkwise,
  vol_networkwise,
)

```

```{r}
saveRDS(networkwise_corrs, file = file.path(output_base, "all_clinicalplusqa_group", "Rdata_cache", "06_wholebrain_FC_Schaefercombat_networkwise_cache.rds"))
```

```{r}
networkwise_corrs <- readRDS(file = file.path(output_base, "all_clinicalplusqa_group", "Rdata_cache", "06_wholebrain_FC_Schaefercombat_networkwise_cache.rds"))
```


## calcualate Diagnosis Effect - Networkwise

a helper function for calculating cohen's D (after regressing out the covars)

```{r}
library(modelr)
library(effsize)


calc_DX_cohenD <- function(df, outcome, predictor, covars) { 
m1 <- lm(formula(paste(outcome, '~', paste(covars, collapse = " + "))),
         data = df)
result <-df %>% 
  add_residuals(m1) %>%
  cohen.d(formula(paste("resid ~", predictor)), data = .) %>% 
  .$estimate
return(result)
}
```

merging the networkwise correlations with the phenotypic data for modeling

```{r}
results_net_pheno <- networkwise_corrs %>%
  inner_join(pheno, by = c("subject", "dataset")) %>%
  unnest(cols = c(results)) %>%
  select(vertex_type, to, from, subject, dataset, weight, DX, all_of(lm_covar_cols))
  
```


calculating cohen's D of the DX for all edges

```{r}
cohenD_DX_networkwise <-  results_net_pheno %>%
  mutate(corZ = weight) %>%
  ungroup() %>%
  select(vertex_type, to, from, subject, corZ, DX, all_of(lm_covar_cols)) %>%
  group_by(vertex_type, to, from) %>%
  nest() %>%
  #slice(1:3) %>%
  mutate(DX_cohenD = map(data, ~calc_DX_cohenD(.x, 
                                               outcome = "corZ", 
                                               predictor = "DX",
                                               covars = lm_covar_cols))) %>%
  unnest(DX_cohenD) %>%
  ungroup() %>%
  select(vertex_type, to, from, DX_cohenD)
```

running a linear model for all edges

```{r}
DX_lm_formula <- formula(paste("corZ ~ ", lm_predictor_col, "+",
                               paste(lm_covar_cols, collapse = " + ")))

print(str_glue("fitting: lm formula {DX_lm_formula}"))

DX_lm_model_fit_networkwise <-  results_net_pheno %>%
  mutate(corZ = weight) %>%
  group_by(vertex_type, to, from) %>%
  do(tidy(lm(DX_lm_formula,.))) %>%
  
  # doing the 
  ungroup() %>%
  group_by(term) %>%
  mutate(p_FDR = p.adjust(p.value, method = "fdr")) %>%
  arrange(p.value)

```
merging the cohen's D with the DX results from the models

```{r}
DX_lm_model_DXcohenD_networkwise <- DX_lm_model_fit_networkwise %>%
  filter(term == "DXSSD") %>%
  inner_join(cohenD_DX_networkwise, by = c("vertex_type", "to", "from")) %>%
  mutate(cohenD_DX_tstatdir = -1 * DX_cohenD)

DX_lm_model_DXcohenD_networkwise %>%
   filter(p_FDR < 0.05) %>%
   arrange(p.value) %>%
  count(vertex_type)
```

Plotting the networkwise results to a using ggtile

```{r}

DX_lm_model_DXcohenD_networkwise %>%
  mutate(to = factor(to, levels = rev(networkg_order)),
         from = factor(from, levels = rev(networkg_order)),
         corrtype = factor(vertex_type, levels = c("volschaefer","surfschaefer" ),
                      labels = c("Volume Template", "Surface Template")),
         sig = if_else(p_FDR < 0.05, "*","")) %>%
  ggplot(aes(x = to, y = from, fill = DX_cohenD)) +
  geom_tile() +
  geom_text(aes(label = sig)) +
  scale_fill_distiller(breaks = c(-1,1), type = "div", palette = 5) +
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  facet_wrap(~ corrtype) +
  labs(x = NULL, y = NULL)

```

## Compare networkwise cohen's D across cortical surface methods using bootstrap permutations on half the sample

```{r}
# Create an empty data frame to store the results
networkwise_boot_cohenDDX_results <- data.frame()

# Run the code snippet 100 times
for (i in 1:1000) {
  
  set.seed(i*10)
  
  #print(paste("boot",i))
  # Execute the code snippet
  this_subsample <- pheno %>%
    group_by(DX) %>%
    sample_frac(size = 0.5) %>%
    select(subject, dataset, DX) 
  
  this_result <-  results_net_pheno %>%
    semi_join(this_subsample, by = c("subject", "dataset")) %>%
    mutate(corZ = weight) %>%
    ungroup() %>%
    select(vertex_type, to, from, subject, corZ, DX, all_of(lm_covar_cols)) %>%
    group_by(vertex_type, to, from) %>%
    nest() %>%
    #slice(1:3) %>%
    mutate(DX_cohenD = map(data, ~calc_DX_cohenD(.x, 
                                                 outcome = "corZ", 
                                                 predictor = "DX",
                                                 covars = lm_covar_cols))) %>%
    unnest(DX_cohenD) %>%
    ungroup() %>%
    select(vertex_type, to, from, DX_cohenD) %>%
    pivot_wider(id_cols = c("to", "from"),
                names_from = "vertex_type",
                values_from = DX_cohenD) %>%
    mutate("pvertex_minus_tvertex" = volschaefer-surfschaefer)
             
  
  # Combine the results with the existing data frame
  networkwise_boot_cohenDDX_results <- bind_rows(networkwise_boot_cohenDDX_results, this_result)
  
}



```

```{r}
saveRDS(networkwise_boot_cohenDDX_results, file = file.path(output_base, "all_clinicalplusqa_group", "Rdata_cache", "06_wholebrain_FC_Schaefercombat_networkwiseboot_cache.rds"))
```

```{r}
library(ggridges)

make_subcortcort_edges_raincloud <- function(data, this_subCort) {
  
  plt_data <- data

make_one_net_ridgelines <- function(plt_data, this_YeoNet, this_subCort, no_ticks = TRUE) {
    plt <- plt_data %>%
    filter(from == str_c("Cort",this_YeoNet)) %>%
    filter(to == this_subCort) %>%
    pivot_longer(cols = c("surfschaefer", "volschaefer"),
               names_to = "vertex_type", 
               values_to = "gvalue") %>%
    mutate(corrtype = factor_corrtype(vertex_type, "Schaefer")) %>%
    ggplot(aes(y = corrtype, x = gvalue)) +
    geom_density_ridges(
      #jittered_points = TRUE, position = "raincloud",
      alpha = 0.5, scale = 2,
      quantile_lines = TRUE, quantiles = 2,
      color = YeoNet7 %>% filter(network==this_YeoNet) %>% pull(hexcode)
    ) +
    # geom_text(aes(y = corrtype, label = hyper), 
    #       x = 0.5, 
    #       nudge_y = 0.2, data = plt_counts %>% filter(as.character(network.y) %in% c(this_YeoNet))) +
    # geom_text(aes(y = corrtype, label = hypo), 
    #       x = -0.5, 
    #       nudge_y = 0.2, data = plt_counts %>% filter(as.character(network.y) %in% c(this_YeoNet))) +
    geom_vline(xintercept = 0) +
    # geom_vline(xintercept = D_threshold, linetype = "dashed") +
    # geom_vline(xintercept = -D_threshold, linetype = "dashed") +
    scale_colour_manual(values = c(YeoNet7 %>% filter(network==this_YeoNet) %>% pull(hexcode))) +
    scale_x_continuous(limits = c(-0.8, 0.8)) +
    labs(y = NULL,
         x = NULL) +
    theme(legend.position='none')

if (no_ticks==TRUE) {
    plt <- plt + theme(axis.title.x=element_blank(),
                       axis.text.x=element_blank())
  } else {
    plt <- plt + labs(x = "Subcortical to Cortical Edges")
  }
  return(plt)
  
}

#' Right section of the raincload plots used in sub-cortical cortical change reporting
focus_subcort_raincloud <- function(data, this_YeoNet, this_subCort, no_ticks = TRUE) {
  
  plt <- data %>%
    filter(to == this_subCort, from == str_c("Cort",this_YeoNet)) %>% 
    ungroup() %>%
    ggplot(aes(x = pvertex_minus_tvertex, y = 1)) +
    geom_density_ridges(
      # jittered_points = TRUE, position = "raincloud",
      alpha = 0.5, scale = 2,
      quantile_lines = TRUE, quantiles = 2,
      fill = YeoNet7 %>% filter(network==this_YeoNet) %>% pull(hexcode),
      colour = YeoNet7 %>% filter(network==this_YeoNet) %>% pull(hexcode)
    ) +
    geom_vline(xintercept = 0) +
    scale_x_continuous(limits = c(-0.3, 0.6)) +
    labs(y = NULL,
         x = NULL) +
    theme(legend.position='none', 
          axis.title.y=element_blank(),
          axis.text.y=element_blank()) 
  if (no_ticks==TRUE) {
    plt <- plt + theme(axis.title.x=element_blank(),
                       axis.text.x=element_blank())
  } else {
    plt <- plt + labs(x = "Surface - Volume.")
  }
  return(plt)
  
}


#' Combined left and right section of the raincload plots used in sub-cortical cortical change reporting
compare_with_rainclouds <- function(plt_data, this_YeoNet, this_subCort, no_ticks = TRUE) {
  plt <- plot_grid(make_one_net_ridgelines(plt_data, this_YeoNet, this_subCort, no_ticks),
                   focus_subcort_raincloud(plt_data, this_YeoNet, this_subCort, no_ticks), 
                   rel_widths = c(2,1))
  return(plt)
}

  DM <- compare_with_rainclouds(plt_data, "DM", this_subCort)
  FP <- compare_with_rainclouds(plt_data, "FP", this_subCort)
  VA <- compare_with_rainclouds(plt_data, "VA", this_subCort)
  DA <- compare_with_rainclouds(plt_data, "DA", this_subCort)
  SM <- compare_with_rainclouds(plt_data, "SM", this_subCort)
  VI <- compare_with_rainclouds(plt_data, "VI", this_subCort, no_ticks = FALSE)

  title <- ggdraw() + draw_label(str_c(this_subCort, " to Cortical"), fontface='bold')
  full_plt <- plot_grid(title, DM, FP, VA, DA, SM, VI,
                   ncol = 1, rel_heights = c(0.5, 1, 1, 1, 1, 1, 1.5))
  return(full_plt)
}


make_subcortcort_edges_raincloud(networkwise_boot_cohenDDX_results, this_subCort = "thalamus")
```

```{r}
make_subcortcort_edges_raincloud(networkwise_boot_cohenDDX_results, this_subCort = "cerebellum")
```


```{r}
to_ROI <- "thalamus"
from_ROI <- "CortVI"
networkwise_boot_cohenDDX_results %>%
  filter(to == to_ROI, from == from_ROI) %>%
  pivot_longer(cols = c("surfschaefer", "volschaefer"),
               names_to = "vertex_type", 
               values_to = "gvalue") %>%
  mutate(corrtype = factor_corrtype(vertex_type, "Schaefer")) %>%
  ungroup() %>%
  ggplot(aes(y = corrtype, x = gvalue)) +
  geom_density_ridges(aes(fill = nettype, colour = nettype),
                        #jittered_points = TRUE, position = "raincloud",
                        alpha = 0.5, scale = 2,
                        quantile_lines = TRUE, quantiles = 2
    ) +
    geom_text(aes(y = corrtype, label = cohenD_str), 
              x = 0.55, 
              nudge_y = 0.1, data = eff_size_df) +
    geom_vline(xintercept = 0) +
    scale_colour_manual(values = c("#808080", YeoNet7 %>% filter(network==this_YeoNet) %>% pull(hexcode))) +
    scale_fill_manual(values = c("#808080", YeoNet7 %>% filter(network==this_YeoNet) %>% pull(hexcode))) +
    scale_x_continuous(limits = c(-0.5, 0.6)) +
    labs(y = NULL,
         x = NULL) +
    theme(legend.position='none')
  
```

```{r}

YeoNet7 <- tribble(
  ~network, ~hexcode,
  "VI", "#781286",
  "SM", "#4682B4",
  "DA", "#00760E",
  "VA", "#C43AFA",
  "FP", "#E69422",
  "DM", "#CD3E3A",
  "LI", "#dcf8a4")

specify_decimal <- function(x, k) trimws(format(round(x, k), nsmall=k))

factor_corrtype <- function(x, cort_atlas) {
  if (cort_atlas == "PINT") {
    corrtype = factor(x, levels = c('pvertex', 'tvertex', 'tvolume'),
                      labels = c("Surface Personalized", "Surface Template", "Volume Template"))
  } else if (cort_atlas == "Schaefer") {
    corrtype = factor(x, levels = c("volschaefer","surfschaefer" ),
                      labels = c("Volume Template", "Surface Template"))
  }
  return(corrtype)
}
```

```{r}
data %>%
    mutate(corrtype = factor_corrtype(vertex_type, cort_atlas)) %>%
    gather(nettype, gvalue, diff_net, same_net) %>%
    filter(subcort_ROI == this_subcort_ROI, YeoNet == this_YeoNet) %>% 
    ungroup() %>%
    ggplot(aes(y = corrtype, x = gvalue)) +
    geom_density_ridges(aes(fill = nettype, colour = nettype),
                        #jittered_points = TRUE, position = "raincloud",
                        alpha = 0.5, scale = 2,
                        quantile_lines = TRUE, quantiles = 2
    ) +
    geom_text(aes(y = corrtype, label = cohenD_str), 
              x = 0.55, 
              nudge_y = 0.1, data = eff_size_df) +
    geom_vline(xintercept = 0) +
    scale_colour_manual(values = c("#808080", YeoNet7 %>% filter(network==this_YeoNet) %>% pull(hexcode))) +
    scale_fill_manual(values = c("#808080", YeoNet7 %>% filter(network==this_YeoNet) %>% pull(hexcode))) +
    scale_x_continuous(limits = c(-0.5, 0.6)) +
    labs(y = NULL,
         x = NULL) +
    theme(legend.position='none')
```




## Running a whole brain (edgewise) models

Calculating cohen's D for the DX effect for each edge

```{r calc-DX-cohensD}
results_pheno_plus_DXd <- function(results_pheno) {
  results_pheno %>%
  semi_join(node_annotations, by = c("to"="node_name")) %>%
  semi_join(node_annotations, by = c("from"="node_name")) %>%
  mutate(corZ = weight) %>%
  select(vertex_type, to, from, subject, corZ, DX, lm_covar_cols) %>%
  group_by(vertex_type, to, from) %>%
  nest() %>%
  #slice(1:3) %>%
  mutate(DX_cohenD = map(data, ~calc_DX_cohenD(.x, 
                                               outcome = "corZ", 
                                               predictor = "DX",
                                               covars = lm_covar_cols))) %>%
  unnest(DX_cohenD) %>%
  ungroup() %>%
  select(vertex_type, to, from, DX_cohenD)
}

## had to split this by vertex because of RAM issues on laptop
pvertex_DXd <- results_pheno %>%
  filter(vertex_type == "pvertex") %>%
  results_pheno_plus_DXd()
tvertex_DXd <- results_pheno %>%
  filter(vertex_type == "tvertex") %>%
  results_pheno_plus_DXd()
tvolume_DXd <- results_pheno %>%
  filter(vertex_type == "tvolume") %>%
  results_pheno_plus_DXd()

DX_cohensD_results <- bind_rows(
  pvertex_DXd,
  tvertex_DXd,
  tvolume_DXd
) 


```

Running the linear model on each edge

```{r}
DX_lm_formula <- formula(paste("corZ ~ ", lm_predictor_col, "+",
                               paste(lm_covar_cols, collapse = " + ")))

print(str_c("fitting: lm formula {DX_lm_formula}"))

DX_lm_model_fit <- function(results_pheno) {
  results_pheno %>%
  semi_join(node_annotations, by = c("to"="node_name")) %>%
  semi_join(node_annotations, by = c("from"="node_name")) %>%
  mutate(corZ = weight) %>%
  group_by(vertex_type, to, from) %>%
  do(tidy(lm(DX_lm_formula,.))) 
}

## had to split this by vertex because of RAM issues on laptop
pvertex_DX_lm <- results_pheno %>%
  filter(vertex_type == "pvertex") %>%
  DX_lm_model_fit()
tvertex_DX_lm <- results_pheno %>%
  filter(vertex_type == "tvertex") %>%
  DX_lm_model_fit()
tvolume_DX_lm <- results_pheno %>%
  filter(vertex_type == "tvolume") %>%
  DX_lm_model_fit()

DX_lm_model_full <- bind_rows(
  pvertex_DX_lm,
  tvertex_DX_lm,
  tvolume_DX_lm
) 



```


## filters out some unwanted edges before FDR correction


```{r}
annotated_graph_edges <- DX_lm_model_full %>%
  ungroup() %>%
  select(to, from) %>%
  distinct() %>%
  inner_join(node_annotations, by = c("to"="node_name")) %>%
  inner_join(node_annotations, by = c("from"="node_name"), suffix = c('_to','_from')) %>%
  unite(from_to_type, etype_from, etype_to) %>%
  unite(hemis, hemi_from, hemi_to, sep = "") %>%
  unite(networks, network_from, network_to, sep = "", remove = FALSE) %>%
  mutate(from_to_type = recode(from_to_type, "Cort_SubCort" = "SubCort_Cort")) %>%
  mutate(hemis = recode(hemis, "RL" = "LR")) 


DX_lm_model <- DX_lm_model_full %>%
  ungroup() %>%
  inner_join(annotated_graph_edges, by = c("to", "from")) %>%
  mutate(withinsubcort = if_else((from_to_type == "SubCort_SubCort") & (subcort_ROI_from == subcort_ROI_to), "drop", "keep")) %>%
  filter(withinsubcort == "keep") %>%
  select(vertex_type, to, from, term, statistic, p.value) %>%
  ungroup() %>%
  group_by(term) %>%
  mutate(p_FDR = p.adjust(p.value, method = "fdr")) %>%
  arrange(p.value)
```

combine the models with the cohen's D estimate and plot t-stat vs cohen's D

```{r}
DX_lm_model_DXcohenD <- DX_lm_model %>%
  filter(term == "DXSSD") %>%
  inner_join(DX_cohensD_results, by = c("vertex_type", "to", "from")) %>%
  mutate(cohenD_DX_tstatdir = -1 * DX_cohenD)
DX_lm_model_DXcohenD %>%
  ggplot(aes(cohenD_DX_tstatdir, statistic, color = (p_FDR < 0.05))) +
  geom_point()
```

show the significant edges

```{r}
DX_lm_model_DXcohenD %>%
  filter(p_FDR < 0.05) %>%
  arrange(desc(p.value)) %>%
  slice(1:5)
```


```{r}
saveRDS(DX_lm_model_DXcohenD, file = file.path(output_base, "all_clinicalplusqa_group", "Rdata_cache", "06_wholebrain_FC_DXlmfits.rds"))
```

can get the model fit back from here..

```{r eval = FALSE}
DX_lm_model_DXcohenD <- readRDS(file = file.path(output_base, "all_clinicalplusqa_group", "Rdata_cache", "06_wholebrain_FC_DXlmfits.rds"))
```



## Make swirly plots of edgewise results

```{r fig.height=10, fig.width=10}
source(here('code/R/swirly_plot_helpers.R'))
DX_lm_model_DXcohenD %>%
  ungroup() %>%
  ## filtering steps
  filter(term == "DXSSD") %>%
  filter(vertex_type == "pvertex") %>%
  
  ## make a pretty plot
  make_swirly_results_plot(pos_label = "SSD > HC", 
                      neg_label = "HC > SSD",
                      plot_title = "Personalized",
                      node_annotations = node_annotations)
```


```{r fig.height=10, fig.width=10}
DX_lm_model_DXcohenD %>%
  ungroup() %>%
  filter(term == "DXSSD") %>%
  filter(vertex_type == "tvertex") %>%
  make_swirly_results_plot(pos_label = "SSD > HC", 
                      neg_label = "HC > SSD",
                      plot_title = "Template",
                      node_annotations = node_annotations)
```


```{r fig.height=10, fig.width=10}
DX_lm_model_DXcohenD %>%
  ungroup() %>%
  filter(term == "DXSSD") %>%
  filter(vertex_type == "tvolume") %>%
  make_swirly_results_plot(pos_label = "SSD > HC", 
                      neg_label = "HC > SSD",
                      plot_title = "Volume",
                      node_annotations = node_annotations)
```

## make table FDR corrected Edges that survive correction

```{r}
DX_lm_model_DXcohenD %>%
  inner_join(annotated_graph_edges, by = c("to", "from")) %>%
  mutate(sig_edge = if_else(p_FDR < 0.05, "sig", "ns"),
         stat_pos = if_else(statistic > 0, "pos", "neg")) %>%
  filter(term == "DXSSD") %>% 
  count(vertex_type, from_to_type, sig_edge) %>%
  spread(sig_edge, n) %>%
  mutate(perc_sig = sig/(ns + sig)*100)

```

```{r}
DX_sig_edge_table <- DX_lm_model_DXcohenD %>%
  inner_join(annotated_graph_edges, by = c("to", "from")) %>%
  mutate(sig_edge = if_else(p_FDR < 0.05, "sig", "ns"),
         stat_pos = if_else(statistic > 0, "pos", "neg")) %>%
  filter(term == "DXSSD", from_to_type != "SubCort_SubCort") %>% 
  count(vertex_type,  sig_edge) %>%
  spread(sig_edge, n) %>%
  mutate(perc_sig = sig/(ns + sig)*100)

DX_sig_edge_table

```


```{r}

#' go uppertri data to full dataframe for geom_tile
uppertri_df_to_full <- function(graph_df) {
  # converts from three col graph df to adjacency matrix
  uppertri_df_to_agjmat <- function(graph_df) {
    
    names(graph_df) <- c('to', 'from', 'myattr')
    matrix_out <- graph_df %>%
      graph_from_data_frame(.,directed = F) %>%
      get.adjacency(., type = "both", attr = "myattr") %>%
      as.matrix() 
    return(matrix_out)
  }
  
  result <- graph_df %>%
    uppertri_df_to_agjmat() %>%
    as.data.frame() %>%
    mutate(to = row.names(.)) %>%
    gather(from, value, -to) 
  return(result)
}
```

```{r}
results_pheno
```


```{r}
YeoNet7 <- define_YeoNet7_colours()
node_annotations1 <- node_annotations %>%
  mutate(node_grouping  = if_else(etype == "Cort",
                                  str_c("Cort", cort_NET),
                                  as.character(subcort_ROI))) 

node_groupings <- factor(1:9, 
                         levels = c(1:9),
                         labels = c(levels(node_annotations$subcort_ROI),
                                    str_c("Cort",YeoNet7$network[1:6])))
edge_grouping_guide <- matrix(1, 
                  nrow = length(node_groupings),
                  ncol = length(node_groupings),
                  dimnames = list(node_groupings,
                                  node_groupings)) %>%
    graph_from_adjacency_matrix(mode="upper", 
                                weighted=T, diag=T) %>%
    as_data_frame() %>%
  filter(!(from %in% c("striatum", "thalamus", "cerebellum") & to == from)) %>%
  select(to, from)


```





```{r, fig.width=6, fig.height = 8}

DX_lm_model_DXcohenD %>%
      ungroup() %>%
      inner_join(node_annotations1, by = c("from"="node_name")) %>%
      inner_join(node_annotations1, by = c("to"="node_name")) %>%
      mutate(sig_edge = if_else(p_FDR < 0.05, "sig", "ns"),
      stat_pos = if_else(statistic > 0, "pos", "neg")) %>%
      filter(term == "DXSSD") %>% 
      count(vertex_type, node_grouping.x, node_grouping.y, stat_pos, sig_edge) %>%
      group_by(vertex_type, node_grouping.x, node_grouping.y, stat_pos) %>%
      spread(sig_edge, n, fill = 0) %>%
      mutate(sig_signed = if_else(stat_pos == "pos", sig, sig*-1),
             node_grouping_x = factor(node_grouping.x, levels = node_groupings),
             node_grouping_y = factor(node_grouping.y, levels = node_groupings)) %>%
      mutate(node_grouping_fx = if_else(node_grouping_x == "CortDA" & node_grouping_y %in% c("CortVA", "CortFP", "CortDM"), 
                                        node_grouping_y, node_grouping_x),
             node_grouping_fy = if_else(node_grouping_x == "CortDA" & node_grouping_y %in% c("CortVA", "CortFP", "CortDM"), 
                                        node_grouping_x, node_grouping_y)) %>%
  ggplot(aes(x = node_grouping_fx, y = node_grouping_fy, fill = sig_signed)) +
  geom_tile() +
  geom_text(aes(label = sig)) +
  scale_fill_distiller(breaks = c(-0.5,0.5), type = "div", palette = 5) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  facet_grid(vertex_type ~ stat_pos)
```



```{r}
#' convert from three col graph df to adjacency matrix
uppertri_df_to_agjmat <- function(graph_df) {
  
names(graph_df) <- c('to', 'from', 'myattr')
matrix_out <- graph_df %>%
  graph_from_data_frame(.,directed = F) %>%
  get.adjacency(., type = "both", attr = "myattr") %>%
  as.matrix() 
return(matrix_out)
}

#' go uppertri data to full dataframe for geom_tile
uppertri_df_to_full <- function(graph_df) {
result <- graph_df %>%
  uppertri_df_to_agjmat() %>%
  as.data.frame() %>%
  mutate(to = row.names(.)) %>%
  gather(from, value, -to) 
return(result)
}
```





```{r fig.height=20, fig.width= 12}
DX_lm_model_DXcohenD %>%
  filter(term == "DXSSD") %>%
  mutate(t_filtered = if_else(p_FDR < 0.1, statistic, 0)) %>%
  ungroup() %>%
  select(vertex_type, to, from, t_filtered) %>%
  group_by(vertex_type) %>%
  nest() %>%
  mutate(uptri = map(data, uppertri_df_to_full)) %>%
  unnest(uptri) %>%
  mutate(to_lab = factor(to, levels = (node_annotations %>% arrange(subcort_ROI, network))$node_name),
         from_lab = factor(from, levels = (node_annotations %>% arrange(subcort_ROI, network))$node_name)) %>%
  ggplot(aes(x=to_lab, y=from_lab, fill=value)) + 
  geom_tile(color = "white") +
  scale_fill_gradient2(high = "#b2182b", mid = "white", low = "#2166ac") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  facet_wrap(~vertex_type, ncol = 1) +
  labs(title = "T statistic for effect of DX (thesholded)",
       x = NULL, y = NULL, fill = "T statistic for DX")
```

`













```{r fig.height=12, fig.width= 12}
full_DX_mat <- DX_lm_model_DXcohenD %>%
  filter(term == "DXSSD", vertex_type == "pvertex") %>%
  ungroup() %>%
  select(to, from, statistic) %>%
  uppertri_df_to_full() 

full_DX_mat %>%
  mutate(to_lab = factor(to, levels = node_annotations$node_name), 
         from_lab = factor(from, levels = node_annotations$node_name)) %>%
  ggplot(aes(x=to_lab, y=from_lab, fill=value)) + 
  geom_tile(color = "white") +
  scale_fill_gradient2(high = "#b2182b", mid = "white", low = "#2166ac") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(title = "T statistic for effect of DX",
       x = NULL, y = NULL, fill = "T statistic for DX")
```
### trying to plot edges in subgroups

Plotting Subcortical to Cortical Edges

```{r fig.height=8, fig.width=5}
library(ggridges)

make_subcortcort_edges_raincloud <- function(data,D_threshold) {

get_subcort_net_edges <- function(data, this_YeoNet, D_threshold) {
      data %>%
      ungroup() %>%
      select(to, from, cohenD_DX_tstatdir) %>%
      uppertri_df_to_full() %>%
      inner_join(node_annotations, by = c("to"="node_name")) %>%
      inner_join(node_annotations, by = c("from"="node_name")) %>%
      filter(etype.x == "SubCort") %>%
      filter(etype.y == "Cort")
      
}

DXweigths_pvertex <- data %>%
  filter(term == "DXSSD", vertex_type == "pvertex") %>%
  ungroup() %>%
  get_subcort_net_edges(.,this_YeoNet) 

DXweigths_tvertex <- data %>%
  filter(term == "DXSSD", vertex_type == "tvertex") %>%
  ungroup() %>%
  get_subcort_net_edges(.,this_YeoNet)

DXweigths_tvolume <- data %>%
  filter(term == "DXSSD", vertex_type == "tvolume") %>%
  ungroup() %>%
  get_subcort_net_edges(.,this_YeoNet)

Fz_DXweigths <- bind_rows(pvertex = DXweigths_pvertex,
                     tvertex = DXweigths_tvertex,
                     tvolume = DXweigths_tvolume,
                     .id = "vertex_type") %>%
      mutate(corrtype = factor(vertex_type, levels = c('pvertex', 'tvertex', 'tvolume'),
                             labels = c("Surface Personalized", 
                                        "Surface Template", 
                                        "Volume Template")),
           hyper_hypo = case_when(value < -D_threshold ~ "hypo",
                                  value > D_threshold ~ "hyper",
                                  TRUE ~ "notsig"))

plt_counts <- Fz_DXweigths %>%
  count(corrtype, network.y, hyper_hypo) %>%
  spread(hyper_hypo, n, fill = 0)


make_one_net_ridgelines <- function(plt_data, plt_counts, this_YeoNet, D_threshold, no_ticks = TRUE) {
    plt <- plt_data %>%
    filter(as.character(network.y) %in% c(this_YeoNet)) %>%
    ggplot(aes(y = corrtype, x = value)) +
    geom_density_ridges(
      #jittered_points = TRUE, position = "raincloud",
      alpha = 0.5, scale = 2,
      quantile_lines = TRUE, quantiles = 2,
      color = YeoNet7 %>% filter(network==this_YeoNet) %>% pull(hexcode)
    ) +
    geom_text(aes(y = corrtype, label = hyper), 
          x = 0.5, 
          nudge_y = 0.2, data = plt_counts %>% filter(as.character(network.y) %in% c(this_YeoNet))) +
    geom_text(aes(y = corrtype, label = hypo), 
          x = -0.5, 
          nudge_y = 0.2, data = plt_counts %>% filter(as.character(network.y) %in% c(this_YeoNet))) +
    geom_vline(xintercept = 0) +
    geom_vline(xintercept = D_threshold, linetype = "dashed") +
    geom_vline(xintercept = -D_threshold, linetype = "dashed") +
    scale_colour_manual(values = c(YeoNet7 %>% filter(network==this_YeoNet) %>% pull(hexcode))) +
    scale_x_continuous(limits = c(-0.5, 0.6)) +
    labs(y = NULL,
         x = NULL) +
    theme(legend.position='none')

if (no_ticks==TRUE) {
    plt <- plt + theme(axis.title.x=element_blank(),
                       axis.text.x=element_blank())
  } else {
    plt <- plt + labs(x = "Subcortical to Cortical Edges")
  }
  return(plt)
  
}


  DM <- make_one_net_ridgelines(Fz_DXweigths, plt_counts, "DM", D_threshold)
  FP <- make_one_net_ridgelines(Fz_DXweigths, plt_counts, "FP", D_threshold)
  VA <- make_one_net_ridgelines(Fz_DXweigths, plt_counts, "VA", D_threshold)
  DA <- make_one_net_ridgelines(Fz_DXweigths, plt_counts, "DA", D_threshold)
  SM <- make_one_net_ridgelines(Fz_DXweigths, plt_counts, "SM", D_threshold)
  VI <- make_one_net_ridgelines(Fz_DXweigths, plt_counts, "VI", D_threshold, no_ticks = FALSE)

  title <- ggdraw() + draw_label("Subcortical to Cortical", fontface='bold')
  full_plt <- plot_grid(title, DM, FP, VA, DA, SM, VI,
                   ncol = 1, rel_heights = c(0.5, 1, 1, 1, 1, 1, 1.5))
  return(full_plt)
}


make_subcortcort_edges_raincloud(DX_lm_model_DXcohenD,D_threshold = 0.2678)
```

```{r fig.height=6.5, fig.width=5}
library(ggridges)

make_cortcort_edges_raincloud <- function(data,D_threshold) {

get_cortcort_net_edges <- function(data) {
      data %>%
      ungroup() %>%
      select(to, from, cohenD_DX_tstatdir) %>%
      uppertri_df_to_full() %>%
      inner_join(node_annotations, by = c("to"="node_name")) %>%
      inner_join(node_annotations, by = c("from"="node_name")) %>%
      filter(etype.x == "Cort") %>%
      filter(etype.y == "Cort")
      
}

DXweigths_pvertex <- data %>%
  filter(term == "DXSSD", vertex_type == "pvertex") %>%
  ungroup() %>%
  get_cortcort_net_edges() 

DXweigths_tvertex <- data %>%
  filter(term == "DXSSD", vertex_type == "tvertex") %>%
  ungroup() %>%
  get_cortcort_net_edges()

DXweigths_tvolume <- data %>%
  filter(term == "DXSSD", vertex_type == "tvolume") %>%
  ungroup() %>%
  get_cortcort_net_edges()

Fz_DXweigths <- bind_rows(pvertex = DXweigths_pvertex,
                     tvertex = DXweigths_tvertex,
                     tvolume = DXweigths_tvolume,
                     .id = "vertex_type") %>%
      mutate(corrtype = factor(vertex_type, levels = c('pvertex', 'tvertex', 'tvolume'),
                             labels = c("Surface Personalized", 
                                        "Surface Template", 
                                        "Volume Template")),
           hyper_hypo = case_when(value < -D_threshold ~ "hypo",
                                  value > D_threshold ~ "hyper",
                                  TRUE ~ "notsig"))

all_plt_counts <- Fz_DXweigths %>%
  count(corrtype, network.y, network.x, hyper_hypo) %>%
  spread(hyper_hypo, n, fill = 0)


make_two_net_ridgelines <- function(plt_data, all_plt_counts, network_x, network_y, D_threshold, no_ticks = TRUE) {
    plt_counts <- all_plt_counts %>%
      filter(as.character(network.x)== network_x,
           as.character(network.y)== network_y,)
  
    plt <- plt_data %>%
    filter(as.character(network.x)== network_x,
           as.character(network.y)== network_y,) %>%
    ggplot(aes(y = corrtype, x = value)) +
    geom_density_ridges(
      #jittered_points = TRUE, position = "raincloud",
      alpha = 0.5, scale = 2,
      quantile_lines = TRUE, quantiles = 2,
      color = YeoNet7 %>% filter(network==network_x) %>% pull(hexcode),
      fill = YeoNet7 %>% filter(network==network_y) %>% pull(hexcode)
    ) +
    geom_text(aes(y = corrtype, label = hyper), 
          x = 0.5, 
          nudge_y = 0.2, data = plt_counts) +
    geom_text(aes(y = corrtype, label = hypo), 
          x = -0.5, 
          nudge_y = 0.2, data = plt_counts) +
    geom_vline(xintercept = 0) +
    geom_vline(xintercept = D_threshold, linetype = "dashed") +
    geom_vline(xintercept = -D_threshold, linetype = "dashed") +
    scale_x_continuous(limits = c(-0.5, 0.6)) +
    labs(y = NULL,
         x = NULL) +
    theme(legend.position='none')

if (no_ticks==TRUE) {
    plt <- plt + theme(axis.title.x=element_blank(),
                       axis.text.x=element_blank())
  } else {
    plt <- plt + labs(x = "Cortical to Cortical Edges")
  }
  return(plt)
  
}

  DM_DA <- make_two_net_ridgelines(Fz_DXweigths, all_plt_counts, "DM", "DA", D_threshold)
  DM_VA <- make_two_net_ridgelines(Fz_DXweigths, all_plt_counts, "DM", "VA", D_threshold)
  DM_SM <- make_two_net_ridgelines(Fz_DXweigths, all_plt_counts, "DM", "SM", D_threshold)
  FP_SM <- make_two_net_ridgelines(Fz_DXweigths, all_plt_counts, "FP", "SM", D_threshold)
  VA_DA <- make_two_net_ridgelines(Fz_DXweigths, all_plt_counts, "DA", "VA", D_threshold)
  DA_SM <- make_two_net_ridgelines(Fz_DXweigths, all_plt_counts, "DA", "SM", D_threshold)
  VI_VI <- make_two_net_ridgelines(Fz_DXweigths, all_plt_counts, "VI", "VI", D_threshold, no_ticks = FALSE)

  title <- ggdraw() + draw_label("Selected Cortical to Cortical", fontface='bold')
  full_plt <- plot_grid(title, DM_DA, DM_VA, FP_SM, VA_DA, DA_SM, VI_VI,
                   ncol = 1, rel_heights = c(0.5, 1,  1, 1, 1, 1,1.5))
  return(full_plt)
}


make_cortcort_edges_raincloud(DX_lm_model_DXcohenD,D_threshold = 0.2678)
```

```{r fig.height=1.75, fig.width=5}
D_threshold = 0.2678
hypo_cerebullum_to <- DX_lm_model_DXcohenD %>%
      ungroup() %>%
      select(to, from, cohenD_DX_tstatdir) %>%
      uppertri_df_to_full() %>%
      inner_join(node_annotations, by = c("to"="node_name")) %>%
      inner_join(node_annotations, by = c("from"="node_name")) %>% 
    filter(subcort_ROI.x == "cerebellum") %>%
    filter(subcort_ROI.y %in% c("striatum", "thalamus")) %>%
    mutate(hyper_hypo = case_when(value < -D_threshold ~ "hypo",
                                  value > D_threshold ~ "hyper",
                                  TRUE ~ "notsig"),
           corrtype = str_c(subcort_ROI.y, " to cerebellum"))

plt_counts <- hypo_cerebullum_to %>%
  count(corrtype, hyper_hypo) %>%
  spread(hyper_hypo, n, fill = 0) %>%
  mutate(hyper = 0) # note this only works because there is no hyper

hypo_cerebullum_to %>%
    ggplot(aes(y = corrtype, x = value)) +
    geom_density_ridges(
      #jittered_points = TRUE, position = "raincloud",
      alpha = 0.5, scale = 1.5,
      quantile_lines = TRUE, quantiles = 2
    ) +
    geom_text(aes(y = corrtype, label = hyper), 
          x = 0.5, 
          nudge_y = 0.2, data = plt_counts) +
    geom_text(aes(y = corrtype, label = hypo), 
          x = -2.5, 
          nudge_y = 0.2, data = plt_counts) +
    geom_vline(xintercept = 0) +
    geom_vline(xintercept = D_threshold, linetype = "dashed") +
    geom_vline(xintercept = -D_threshold, linetype = "dashed") +
    labs(y = NULL,
         x = NULL) +
    theme(legend.position='none')
```



```{r}

calc_fc_weights <- function(lm_df, t_threshold) {
  
    full_DX_mat <- lm_df %>%
      ungroup() %>%
      select(to, from, cohenD_DX_tstatdir) %>%
      uppertri_df_to_full() %>%
      inner_join(node_annotations, by = c("to"="node_name")) %>%
      inner_join(node_annotations, by = c("from"="node_name")) 
    
hypo_cerebullum_to_striatum <- full_DX_mat %>%
    filter(subcort_ROI.x == "cerebellum") %>%
    filter(subcort_ROI.y == "striatum") %>%
    filter(value < -t_threshold) %>%
    select(to, from, value) 

hypo_cerebullum_to_thalamus <- full_DX_mat %>%
    filter(subcort_ROI.x == "cerebellum") %>%
    filter(subcort_ROI.y == "thalamus") %>%
    filter(value < -t_threshold) %>%
    select(to, from, value)

hyper_subcort_to_SM <- full_DX_mat %>%
    filter(etype.x == "SubCort") %>%
    filter(etype.y == "Cort") %>%
    filter(as.character(network.y) %in% c("SM")) %>%
    filter(value > t_threshold) %>%
    select(to, from, value)

hyper_subcort_to_VI <- full_DX_mat %>%
    filter(etype.x == "SubCort") %>%
    filter(etype.y == "Cort") %>%
    filter(as.character(network.y) %in% c("VI")) %>%
    filter(value > t_threshold) %>%
    select(to, from, value)

hyper_subcort_to_DA <- full_DX_mat %>%
    filter(etype.x == "SubCort") %>%
    filter(etype.y == "Cort") %>%
    filter(as.character(network.y) %in% c("DA")) %>%
    filter(value > t_threshold) %>%
    select(to, from, value)

hyper_subcort_to_DM <- full_DX_mat %>%
    filter(etype.x == "SubCort") %>%
    filter(etype.y == "Cort") %>%
    filter(as.character(network.y) %in% c("DM")) %>%
    filter(value > t_threshold) %>%
    select(to, from, value)

hypo_subcort_to_FP <- full_DX_mat %>%
    filter(etype.x == "SubCort") %>%
    filter(etype.y == "Cort") %>%
    filter(as.character(network.y) %in% c("FP")) %>%
    filter(value < -t_threshold) %>%
    select(to, from, value)

hypo_subcort_to_VA <- full_DX_mat %>%
    filter(etype.x == "SubCort") %>%
    filter(etype.y == "Cort") %>%
    filter(as.character(network.y) %in% c("VA")) %>%
    filter(value < -t_threshold) %>%
    select(to, from, value)

hyper_cortDA_to_SM <- full_DX_mat %>%
    filter(etype.x == "Cort") %>%
    filter(etype.y == "Cort") %>%
    filter(as.character(network.x) %in% c("DA")) %>%
    filter(as.character(network.y) %in% c("SM")) %>%
    filter(value > t_threshold) %>%
    select(to, from, value)

hyper_cortVA_to_DA <- full_DX_mat %>%
    filter(etype.x == "Cort") %>%
    filter(etype.y == "Cort") %>%
    filter(as.character(network.x) %in% c("VA")) %>%
    filter(as.character(network.y) %in% c("DA")) %>%
    filter(value > t_threshold) %>%
    select(to, from, value)

hyper_cortFP_to_SM <- full_DX_mat %>%
    filter(etype.x == "Cort") %>%
    filter(etype.y == "Cort") %>%
    filter(as.character(network.x) %in% c("FP")) %>%
    filter(as.character(network.y) %in% c("SM")) %>%
    filter(value > t_threshold) %>%
    select(to, from, value)

hypo_cortDM_to_DA <- full_DX_mat %>%
    filter(etype.x == "Cort") %>%
    filter(etype.y == "Cort") %>%
    filter(as.character(network.x) %in% c("DM")) %>%
    filter(as.character(network.y) %in% c("DA")) %>%
    filter(value < -t_threshold) %>%
    select(to, from, value)

hypo_cortDM_to_VA <- full_DX_mat %>%
    filter(etype.x == "Cort") %>%
    filter(etype.y == "Cort") %>%
    filter(as.character(network.x) %in% c("DM")) %>%
    filter(as.character(network.y) %in% c("VA")) %>%
    filter(value < -t_threshold) %>%
    select(to, from, value)

hypo_cortVI_to_VI <- full_DX_mat %>%
    filter(etype.x == "Cort") %>%
    filter(etype.y == "Cort") %>%
    filter(as.character(network.x) %in% c("VI")) %>%
    filter(as.character(network.y) %in% c("VI")) %>%
    filter(value < -t_threshold) %>%
    select(to, from, value)

Fz_weigths <-bind_rows(hyper_cortDA_to_SM = hyper_cortDA_to_SM,
                       hyper_cortFP_to_SM = hyper_cortFP_to_SM,
                       hyper_cortVA_to_DA = hyper_cortVA_to_DA,
                       hypo_cortDM_to_DA = hypo_cortDM_to_DA,
                       hypo_cortDM_to_VA = hypo_cortDM_to_VA,
                       hypo_cortVI_to_VI = hypo_cortVI_to_VI,
                       hyper_subcort_to_DM = hyper_subcort_to_DM,
                       hypo_subcort_to_FP = hypo_subcort_to_FP,
                       hypo_subcort_to_VA = hypo_subcort_to_VA,
                       hyper_subcort_to_DA = hyper_subcort_to_DA,
                       hyper_subcort_to_SM = hyper_subcort_to_SM,
                       hyper_subcort_to_VI = hyper_subcort_to_VI,
                       hypo_cerebullum_to_striatum = hypo_cerebullum_to_striatum,
                       hypo_cerebullum_to_thalamus = hypo_cerebullum_to_thalamus,
                       .id = "direction_edge_group") %>%
  separate(direction_edge_group, into = c("effect_direction", "edge_group"), extra = "merge") %>%
  rename(edge_FC_weight = value)

  return(Fz_weigths)

}
  
```

### calculated extract edge weights for per participant scores

```{r}
cohenD_threshold = 0.2678
cohenD_thresname = "pFDR"

Fz_DXweigths_pvertex <- DX_lm_model_DXcohenD %>%
  filter(term == "DXSSD", vertex_type == "pvertex") %>%
  ungroup() %>%
  calc_fc_weights(.,cohenD_threshold)

Fz_DXweigths_tvertex <- DX_lm_model_DXcohenD %>%
  filter(term == "DXSSD", vertex_type == "tvertex") %>%
  ungroup() %>%
  calc_fc_weights(.,cohenD_threshold)

Fz_DXweigths_tvolume <- DX_lm_model_DXcohenD %>%
  filter(term == "DXSSD", vertex_type == "tvolume") %>%
  ungroup() %>%
  calc_fc_weights(.,cohenD_threshold)

Fz_DXweigths <- bind_rows(pvertex = Fz_DXweigths_pvertex,
                     tvertex = Fz_DXweigths_tvertex,
                     tvolume = Fz_DXweigths_tvolume,
                     .id = "vertex_type") 

write_csv(Fz_DXweigths, file.path(output_base, 
                                  "all_clinicalplusqa_group", 
                                  "weighted_subject_FC_weigths",
                                  str_c("SSD4cohorts_DXtweigths_", 
                                        cohenD_thresname, ".csv")))
  
```
```{r}
Fz_DXweigths %>% 
  count(edge_group, vertex_type, effect_direction) %>%
  spread(vertex_type, n)


```
### calculated scores per participant


```{r}

#' calculates a subjects weigthed FC score from their edgewise values
#'
#' @param subject_edges_df tibble with columns subject, to, from, and weight
#' @param edge_weights tibble with columns effect_direction, edge_group, to, from, and edge_FC_weight
#'
#' @return tibble with columns subject, dataset, effect_direction, edge_group, FC_subtype and wFC_score
#'
#' @examples
calc_subjects_wFC_score <- function(subject_edges_df, edge_weights) {
  result <- subject_edges_df %>%
  ungroup() %>%
  group_by(subject, dataset) %>%
  nest() %>%
  mutate(uptri = map(data, uppertri_df_to_full)) %>%
  unnest(uptri) %>%
  inner_join(edge_weights, by = c("to", "from")) %>%
  ungroup() %>%
  group_by(subject, dataset, effect_direction, edge_group) %>%
  summarise(wFC_score = weighted.mean(value, w = edge_FC_weight),
            mFC_score = mean(value)) %>%
  ungroup()
  return(result)
}
```


```{r}
pvertex_subject_FC_scores <- results_pheno %>%
  ungroup() %>%
  filter(vertex_type == "pvertex") %>%
  select(subject, dataset, to, from, weight) %>%
  calc_subjects_wFC_score(Fz_DXweigths_pvertex)

tvertex_subject_FC_scores <- results_pheno %>%
  ungroup() %>%
  filter(vertex_type == "tvertex") %>%
  select(subject, dataset, to, from, weight) %>%
  calc_subjects_wFC_score(Fz_DXweigths_tvertex)

tvolume_subject_FC_scores <- results_pheno %>%
  ungroup() %>%
  filter(vertex_type == "tvolume") %>%
  select(subject, dataset, to, from, weight) %>%
  calc_subjects_wFC_score(Fz_DXweigths_tvolume)

FC_scores_together <- bind_rows(
  pvertex = pvertex_subject_FC_scores,
  tvertex = tvertex_subject_FC_scores,
  tvolume = tvolume_subject_FC_scores,
  .id = "vertex_type"
)

write_csv(FC_scores_together, file.path(output_base, 
                                        "all_clinicalplusqa_group", 
                                        "weighted_subject_FC_scores",
                                        "SSD4cohorts_DXweighted_subject_scores.csv"))
```

```{r}
DX_sig_edge_table %>% filter(vertex_type == "pvertex") %>% pull(sig)
```


## write up to this point..

We observed robust patterns of dysconnectivity that were strengthened using a surface-based approach and PINT (Number of differing pairwise-correlations: volume: {`r DX_sig_edge_table %>% filter(vertex_type == "tvolume") %>% pull(sig)`}, surface: {`r DX_sig_edge_table %>% filter(vertex_type == "tvertex") %>% pull(sig)`},  PINT: {`r DX_sig_edge_table %>% filter(vertex_type == "pvertex") %>% pull(sig)`}, FDR corrected). Moreover, patterns of dyscnnectivity became more interpretable in terms of individual resting state networks and cortical heirarchy (see Supplemental Figure 2 for breakdown by cortical network). Overall, regardless of cortical mapping approach, hypoconnectivity, that is decreased connectivity in participants with schizophrenia relative to controls as observed for edges connecting subcortical regions to the fronto-parietal network. Hyperconnectivity, or increased connectivity in participants with SSD relative to controls was observed for subcortical connections to those visual, somatomor, and dorsal attention networks, which increased when moving from volume-to-surface, and again from surface-to-PINT. Additional patterns of hypoconnectivity where observed between the cortical default-mode network and the dorsal and ventral attention netoworks, as well as within visual network edges. Cortical hyperconnectivity was observed between the dorsal and ventral attenetion networks, as well as the frontoparietal network to the somatomotor network. Moreover, hypoconnectivity was observed for nearly half of edges connecting the cerebellum to the striatum and the cerebellum to the thalamus.

To investigate these patterns further, sub-scored for these groups of edges were calculated to for each participants by taking the weighted-mean of all edges with that survived FDR corretion (Cohen's D threshold = {`r cohenD_threshold`}, means were weighted by the SSD diagnosis effect size).




```{r}
FC_scores_lmfit <- FC_scores_together %>%
  inner_join(pheno, by = c("subject", "dataset")) %>%
  ungroup() %>%
  group_by(edge_group, effect_direction, vertex_type) %>%
  do(tidy(lm(wFC_score ~ DX + Age_pt + Sex + fd_mean_pt + Scanner,.))) 

FC_scores_lmfit %>%
  select(edge_group, effect_direction, term, statistic, p.value) %>%
  filter(term == "DXSSD") %>%
  knitr::kable()

FC_scores_lmfit %>% 
  group_by(vertex_type, edge_group, effect_direction) %>%
  filter(term == "DXSSD",
         str_detect(edge_group,"subcort")) %>%
  ggplot(aes(y = abs(statistic), x = rev(vertex_type), color = edge_group)) +
    geom_point() +
    geom_line(aes(group = edge_group))
```
```{r}
FC_scores_lmfit <- FC_scores_together %>%
  inner_join(pheno, by = c("subject", "dataset")) %>%
  ungroup() %>%
  group_by(edge_group, vertex_type,  effect_direction, Site) %>%
  do(tidy(lm(wFC_score ~ DX + Age_pt + Sex + fd_mean_pt,.))) 

FC_scores_lmfit %>%
  select(edge_group, vertex_type, Site, term, statistic, p.value) %>%
  filter(term == "DXSSD") %>%
  knitr::kable()

FC_scores_lmfit %>% 
  filter(term == "DXSSD",
         str_detect(edge_group,"subcort")) %>%
  ggplot(aes(y = abs(statistic), x = rev(vertex_type), color = edge_group)) +
    geom_point() +
    geom_line(aes(group = edge_group)) +
  facet_wrap(~Site, nrow = 1)
```

```{r eval = FALSE}
SSD_cors <- FC_scores_together %>%
  inner_join(pheno, by = c("subject", "dataset")) %>%
  ungroup() %>%
  filter(DX == "SSD", vertex_type == "pvertex") %>%
  select(subject, dataset, edge_group, wFC_score) %>%
  spread(edge_group, wFC_score) %>%
  select(-subject, -dataset) %>%
  cor(.) 

heatmap(abs(SSD_cors))
```

```{r eval = FALSE}
HC_cors <- FC_scores_together %>%
    inner_join(pheno, by = c("subject", "dataset")) %>%
  ungroup() %>%
  filter(DX == "CTRL", vertex_type == "pvertex") %>%
  select(subject, dataset, edge_group, wFC_score) %>%
  spread(edge_group, wFC_score) %>%
  select(-subject, -dataset) %>%
  cor(.) 

heatmap(abs(HC_cors))
  
```

```{r}
# Marginal densities along x axis
plot_DX_scatter_elipsed <- function(df, x, y) {
  #the tidy eval ness
  xvar <- enquo(x)
  yvar <- enquo(y)
  # make the main scatte bit using above
  main_scatter <-  ggplot(data = df, 
               aes(x = !!xvar, y = !!yvar, color = DX)) +
  geom_point(alpha = 0.7, size = 0.7) +
  stat_ellipse() +
  scale_color_manual(values = c("grey20","red"))

  xdens <- axis_canvas(main_scatter, axis = "x")+
    geom_density(data = df, aes(x = !!xvar, fill = DX),
              alpha = 0.5, size = 0.2) +
    scale_fill_manual(values = c("grey20","red"))

  ydens <- axis_canvas(main_scatter, axis = "y", coord_flip = TRUE)+
    geom_density(data = df, aes(x = !!yvar, fill = DX),
                alpha = 0.5, size = 0.2) +
  scale_fill_manual(values = c("grey20","red")) +
  coord_flip()
  
  #putting the peices together
  p1 <- insert_xaxis_grob(main_scatter, xdens, grid::unit(.2, "null"), position = "top")
  p2<- insert_yaxis_grob(p1, ydens, grid::unit(.2, "null"), position = "right")
  return(p2)
}
```


```{r , fig.height=4, fig.width = 5}
library(cowplot)
fplot <- FC_scores_together %>%
  inner_join(pheno, by = c("subject", "dataset")) %>%
  ungroup() %>%
  filter(vertex_type == "pvertex") %>%
  unite(directed_edge_group, effect_direction, edge_group) %>%
  unite(dat_sub, dataset, subject) %>%  
  select(dat_sub, Site, DX, directed_edge_group, wFC_score) %>%
  spread(directed_edge_group, wFC_score) 

```

```{r, fig.width=5, fig.height = 4}
ggdraw(plot_DX_scatter_elipsed(fplot, x = hyper_subcort_to_VI, y = hypo_subcort_to_FP))
```


```{r, fig.width=5, fig.height = 4}
ggdraw(plot_DX_scatter_elipsed(fplot, x = hyper_subcort_to_VI, y = hypo_cerebullum_to_striatum))
```
```{r, fig.width=5, fig.height = 4}
ggdraw(plot_DX_scatter_elipsed(fplot, x = hyper_subcort_to_SM, y = hypo_subcort_to_FP))
```


```{r, fig.height=4, fig.width=6}
fig1 <- fplot %>%
  ggplot(aes(y = hypo_subcort_to_FP, x = DX, color = DX)) + 
  geom_boxplot(outlier.shape = NA) + 
  geom_dotplot(binaxis = 'y', stackdir = 'center', binwidth = 0.01, alpha = 0.5) +
  scale_color_manual(values = c("grey20","red")) +
  facet_wrap( ~ Site, ncol = 4) +
  labs(x = NULL)

#ggsave(fig1, filename = 'VA_results.png',height = 8, width = 5)

fig1
```


```{r, fig.height=4, fig.width=6}
fig1 <- fplot %>%
  ggplot(aes(y = hyper_subcort_to_SM, x = DX, color = DX)) + 
  geom_boxplot(outlier.shape = NA) + 
  geom_dotplot(binaxis = 'y', stackdir = 'center', binwidth = 0.01, alpha = 0.5) +
  scale_color_manual(values = c("grey20","red")) +
  facet_wrap( ~ Site, ncol = 4) +
  labs(x = NULL)

#ggsave(fig1, filename = 'VA_results.png',height = 8, width = 5)

fig1
```


# calculate weighted subject scores by chopping up the matrix





```{r}
define_hypohyper_weights <- function(lm_df, cohenD_threshold, node_annotations, edge_guide) {
full_DX_mat <- lm_df %>%
      ungroup() %>%
      select(to, from, cohenD_DX_tstatdir) %>%
      uppertri_df_to_full() %>%
      inner_join(node_annotations, by = c("to"="node_name")) %>%
      inner_join(node_annotations, by = c("from"="node_name")) 
    
pos_weights <- full_DX_mat %>%
    filter(value > cohenD_threshold) %>%
    semi_join(edge_grouping_guide, by = c("node_grouping.x" = "to",
                                          "node_grouping.y" = "from")) %>%
    unite(edge_group, node_grouping.x, node_grouping.y) %>%
    select(edge_group, to, from, value)

neg_weights <- full_DX_mat %>%
    filter(value < -cohenD_threshold) %>%
    semi_join(edge_grouping_guide, by = c("node_grouping.x" = "to",
                                          "node_grouping.y" = "from")) %>%
    unite(edge_group, node_grouping.x, node_grouping.y) %>%
    select(edge_group, to, from, value)

all_weights <- bind_rows(hyper = pos_weights,
                        hypo = neg_weights,
                        .id = "effect_direction")
return(all_weights)
}

define_vertex_hypohyper_weights <- function(lm_df, v_type, cohenD_threshold) {
  groupwise_weights <- lm_df %>%
  filter(term == "DXSSD", 
         vertex_type == v_type) %>%
  ungroup() %>%
  define_hypohyper_weights(., cohenD_threshold,
                           node_annotations = node_annotations1,
                           edge_guide = edge_guide)
  return(groupwise_weights)
}


```

```{r}
size_threshold = 8
cohenD_threshold = 0.26

groupwise_weights <- tibble(vertex_type = c("pvertex", "tvertex", "tvolume")) %>%
  mutate(result = map(vertex_type, 
                      ~ define_vertex_hypohyper_weights(DX_lm_model_DXcohenD, 
                                                        .x, 
                                                        cohenD_threshold))) %>%
  unnest(cols = c(result))

groupwise_weights_table <- groupwise_weights %>%
  count(vertex_type, effect_direction, edge_group) %>%
  spread(effect_direction, n, fill = 0) %>%
  group_by(edge_group) %>%
  mutate(hyperhypo_diff = (hyper - hypo)/(hyper + hypo),
         use_hypo = max(hyperhypo_diff) < 0.1 & min(hypo) > size_threshold,
         use_hyper = min(hyperhypo_diff) > -0.1 & min(hyper) > size_threshold,
         num = use_hypo + use_hyper) %>%
  select(num, use_hypo, use_hyper, everything()) %>%
  arrange(num, edge_group, vertex_type) 
  # ungroup() %>%
  # select(vertex_type, edge_group, hyperhypo_diff, max_size) %>%
  # gather(tmp_col, tmp_vals, hyperhypo_diff, max_size) %>%
  # unite(vertex_meas, tmp_col, vertex_type) %>%
  # spread(vertex_meas, tmp_vals) %>%
  # arrange(-abs(hyperhypo_diff_tvolume))
groupwise_weights_table
```






```{r}
edge_groups_to_use <- groupwise_weights_table %>%
  ungroup() %>%
  select(use_hypo, use_hyper, edge_group) %>%
  distinct() %>%
  filter(use_hypo | use_hyper)

edge_groups_to_use
```

```{r}
hyper_edgegroups <- edge_groups_to_use %>% filter(use_hyper) %>% pull(edge_group)
hypo_edgegroups <- edge_groups_to_use %>% filter(use_hypo) %>% pull(edge_group)
groupwise_weights_hyper <- groupwise_weights %>%
  filter(edge_group %in% hyper_edgegroups,
         effect_direction == "hyper")

groupwise_weights_hypo <- groupwise_weights %>%
  filter(edge_group %in% hypo_edgegroups,
         effect_direction == "hypo")

groupwise_weights_both <- bind_rows(
  groupwise_weights_hypo,
  groupwise_weights_hyper
) %>%
  rename(edge_FC_weight = value)

groupwise_weights_both %>%
  count(vertex_type, effect_direction, edge_group) %>%
  ggplot(aes(y = n, x = vertex_type, color = edge_group)) +
  geom_point() +
  geom_line(aes(group = edge_group)) +
  facet_wrap(~effect_direction)
```




```{r}
groupwise_weights_both %>%
  mutate(node_class = if_else(str_detect(edge_group,'_Cort'), 
                 "Within_Cortical",
                 "Subcortical_to")) %>%
  group_by(vertex_type, effect_direction, edge_group, node_class) %>%
  summarise(median_t = median(edge_FC_weight)) %>%
  ggplot(aes(y = abs(median_t), x = vertex_type, color = edge_group)) +
  geom_point() +
  geom_line(aes(group = edge_group)) +
  facet_wrap(~effect_direction*node_class)
```
```{r}
write_csv(groupwise_weights_both, file.path(output_base, 
                                        "all_clinicalplusqa_group", 
                                        "weighted_subject_FC_weigths",
                                        'SSD4cohorts_DXweighted_moregroups_subject_weights.csv'))
```



```{r}

all_subject_FC_weights_by_vertex <- function(results_data, edge_weights, vtype) {
result <- results_data %>%
  ungroup() %>%
  filter(vertex_type == vtype) %>%
  select(subject, dataset, to, from, weight) %>%
  calc_subjects_wFC_score(edge_weights %>% filter(vertex_type == vtype))
return(result)
}

all_subject_FC_weights <- tibble(vertex_type = c("pvertex", "tvertex", "tvolume")) %>%
  mutate(result = map(vertex_type, 
                      ~all_subject_FC_weights_by_vertex(results_pheno, groupwise_weights_both, .x))) %>%
  unnest(cols = c(result))
```

```{r}

write_csv(all_subject_FC_weights, file.path(output_base, 
                                        "all_clinicalplusqa_group", 
                                        "weighted_subject_FC_scores",
                                    'SSD4cohorts_DXweighted_edgegroupwise_subject_scores.csv'))
```

```{r}
FC_gscores_lmfit <- all_subject_FC_weights %>%
  inner_join(pheno, by = c("subject", "dataset")) %>%
  ungroup() %>%
  group_by(effect_direction, edge_group, vertex_type) %>%
  do(tidy(lm(wFC_score ~ DX + Age_pt + Sex + fd_mean_pt + Site,.))) 

FC_gscores_lmfit %>%
  select(effect_direction, edge_group, vertex_type, term, statistic, p.value) %>%
  filter(term == "DXSSD") %>%
  knitr::kable()

FC_gscores_lmfit %>% 
  mutate(node_class = if_else(str_detect(edge_group,'_Cort'), 
                 "Within_Cortical",
                 "Subcortical_to")) %>%
  group_by(vertex_type, effect_direction, edge_group, node_class) %>%
  filter(term == "DXSSD") %>%
  ggplot(aes(y = abs(statistic), x = rev(vertex_type), color = edge_group)) +
    geom_point() +
    geom_line(aes(group = edge_group)) +
  facet_wrap(~effect_direction*node_class)
```
```{r}
FC_gscores_lmfitbySite <- all_subject_FC_weights %>%
  inner_join(pheno, by = c("subject", "dataset")) %>%
  ungroup() %>%
  group_by(effect_direction, edge_group, vertex_type, Site) %>%
  do(tidy(lm(wFC_score ~ DX + Age_pt + Sex + fd_mean_pt,.))) 

FC_gscores_lmfitbySite %>%
  select(effect_direction, edge_group, Site, vertex_type, term, statistic, p.value) %>%
  filter(term == "DXSSD") %>%
  knitr::kable()

FC_gscores_lmfitbySite %>% 
  mutate(node_class = if_else(str_detect(edge_group,'_Cort'), 
                 "Within_Cortical",
                 "Subcortical_to")) %>%
  filter(term == "DXSSD",
         node_class == "Subcortical_to") %>%
  ggplot(aes(y = abs(statistic), x = rev(vertex_type), color = effect_direction)) +
    geom_point() +
    geom_line(aes(group = edge_group)) +
  facet_wrap(~Site)
```

```{r}
FC_gscores_lmfitbySite_mFC <- all_subject_FC_weights %>%
  inner_join(pheno, by = c("subject", "dataset")) %>%
  ungroup() %>%
  group_by(effect_direction, edge_group, vertex_type, Site) %>%
  do(tidy(lm(mFC_score ~ DX + Age_pt + Sex + fd_mean_pt,.))) 

FC_gscores_lmfitbySite_mFC %>%
  select(effect_direction, edge_group, Site, vertex_type, term, statistic, p.value) %>%
  filter(term == "DXSSD") %>%
  knitr::kable()

FC_gscores_lmfitbySite_mFC %>% 
  mutate(node_class = if_else(str_detect(edge_group,'_Cort'), 
                 "Within_Cortical",
                 "Subcortical_to")) %>%
  filter(term == "DXSSD",
         node_class == "Subcortical_to") %>%
  ggplot(aes(y = abs(statistic), x = rev(vertex_type), color = effect_direction)) +
    geom_point() +
    geom_line(aes(group = edge_group)) +
  facet_wrap(~Site)
```


```{r fig.height=7, fig.width=7}
wFC_corrs <- all_subject_FC_weights %>%
  filter(vertex_type == "tvertex") %>%
  select(subject, dataset, edge_group, wFC_score) %>%
  spread(edge_group, wFC_score) %>%
  select(-subject, -dataset) %>%
  cor(.)
heatmap(abs(wFC_corrs))
```

