---
title: "Run clinical against FC scores"
output:
  html_document:
    keep_md: true
---
```{r}
knitr::opts_chunk$set(dev = "png", dev.args = list(type = "cairo-png"))
```

```{r}
library(tidyverse)
library(here)
library(broom)
```
```{r}
knitr::opts_chunk$set(dev = "png", dev.args = list(type = "cairo-png"))
```

Note: to self (as of April - the one thing that is coming out is wtar wiht VI to thalamus)


## The paths to data


```{r setting paths}
# These functions are for reading timeseries files
source(here('code/R/settings_helpers.R'))
#source(here('code/R/file_reading_helpers.R'))

pheno <- read_pheno_file()%>%
  drop_na(DX)
YeoNet_colours <- define_Yeo7_colours()
Yeo7_2011_80verts <- read_Yeo72011_template()  

```

```{r}
pheno_extended <- read_csv(here("data/processed/pheno/qa_pheno_compiled_2020_mar02.csv")) %>%
  mutate(subject = str_c("sub-",sub_id))
```

```{r}
ZHH_extended <- read_csv(here("data/processed/pheno/20200722_ZHH_clinical.csv"))
```


```{r}
weighted_subject_scores <- read_csv(here("data/processed/mri/all_clinicalplusqa_group/weighted_subject_FC_scores/SSD4cohorts_DXweighted_subject_scores.csv"))

```

```{r}
weighted_subject_scores <- weighted_subject_scores%>%
  group_by(vertex_type, edge_group, effect_direction) %>%
  mutate(upper_wFC = mean(wFC_score) + 3*sd(wFC_score),
         lower_wFC = mean(wFC_score) - 3*sd(wFC_score),
         upper_out = upper_wFC < wFC_score,
         lower_out = lower_wFC > wFC_score,
         wFC_score_cliped = if_else(upper_out, upper_wFC, wFC_score),
         wFC_score_cliped = if_else(lower_out, lower_wFC, wFC_score_cliped)) 
#  facet_grid(edge_group ~ vertex_type, scales = "free")
```


```{r}
inner_join(pheno, pheno_extended, by = c("subject", "dataset")) %>%
  select(subject, dataset) %>%
  distinct() %>%
  count()
```
```{r}
pheno_extended %>%
  count(sub_id, dataset) %>%
  filter(n > 1) 
```
```{r}
pheno_extended %>%
  names()
```
```{r}
pheno_extended %>%
  gather(clinical_measure, clinical_score, 
         starts_with("panss"), 
         starts_with("sans"),
         starts_with("wtar"),
         "Edu") %>%
  group_by(Site, dx, clinical_measure) %>%
  summarise(n = sum(!is.na(clinical_score))) %>%
  spread(clinical_measure, n)
```
```{r}
summary(pheno_extended$sans_G_total)
```




```{r}
with_wFC1 <- weighted_subject_scores %>%
  inner_join(pheno_extended, by = c("subject", "dataset")) %>%
  drop_na(dx)
```

```{r}
with_wFC_zhh <- weighted_subject_scores %>%
  inner_join(ZHH_extended, by = c("subject", "dataset")) 
```




```{r}
wFC_corrs <- with_wFC1 %>%
   ungroup() %>%
  filter(vertex_type == "pvertex", 
         dx == "SSD") %>%
  select(subject, dataset, edge_group, wFC_score) %>%
  spread(edge_group, wFC_score) %>%
  select(-subject, -dataset) %>%
  cor(.)
heatmap(abs(wFC_corrs))
```

```{r}
wFC_corrs <- with_wFC1 %>%
   ungroup() %>%
  filter(vertex_type == "pvertex", 
         dx == "CTRL") %>%
  select(subject, dataset, edge_group, wFC_score) %>%
  spread(edge_group, wFC_score) %>%
  select(-subject, -dataset) %>%
  cor(.)
heatmap(abs(wFC_corrs))
```

```{r}
wFC_corrs <- with_wFC1 %>%
   ungroup() %>%
  filter(vertex_type == "pvertex") %>%
  select(subject, dataset, edge_group, wFC_score) %>%
  spread(edge_group, wFC_score) %>%
  select(-subject, -dataset) %>%
  cor(.)
heatmap(abs(wFC_corrs))
```

```{r}
wFC_corrs <- with_wFC1 %>%
   ungroup() %>%
  filter(vertex_type == "tvertex") %>%
  select(subject, dataset, edge_group, wFC_score) %>%
  spread(edge_group, wFC_score) %>%
  select(-subject, -dataset) %>%
  cor(.)
heatmap(abs(wFC_corrs))
```

```{r}
wFC_corrs <- with_wFC1 %>%
   ungroup() %>%
  filter(vertex_type == "tvolume") %>%
  select(subject, dataset, edge_group, wFC_score) %>%
  spread(edge_group, wFC_score) %>%
  select(-subject, -dataset) %>%
  cor(.)
heatmap(abs(wFC_corrs))
```

```{r}
library(cowplot)
# Marginal densities along x axis
plot_greyred_scatter_elipsed <- function(df, x, y, color) {
  #the tidy eval ness
  xvar <- enquo(x)
  yvar <- enquo(y)
  colorvar <- enquo(color)
  # make the main scatte bit using above
  main_scatter <-  ggplot(data = df, 
               aes(x = !!xvar, y = !!yvar, color = !!colorvar)) +
  geom_point(alpha = 0.7, size = 1) +
  geom_smooth(method = "lm") +
  #stat_ellipse() +
  theme_bw() +
  scale_color_manual(values = c("grey20","red"))

  xdens <- axis_canvas(main_scatter, axis = "x")+
    geom_density(data = df, aes(x = !!xvar, fill = !!colorvar),
              alpha = 0.5, size = 0.2) +
    scale_fill_manual(values = c("grey20","red"))

  ydens <- axis_canvas(main_scatter, axis = "y", coord_flip = TRUE)+
    geom_density(data = df, aes(x = !!yvar, fill = !!colorvar),
                alpha = 0.5, size = 0.2) +
  scale_fill_manual(values = c("grey20","red")) +
  coord_flip()
  
  #putting the peices together
  p1 <- insert_xaxis_grob(main_scatter, xdens, grid::unit(.2, "null"), position = "top")
  p2<- insert_yaxis_grob(p1, ydens, grid::unit(.2, "null"), position = "right")
  return(p2)
}
```

```{r}
with_wFC1 %>%
  ungroup() %>%
  select(subject, dataset, dx) %>%
  distinct() %>%
  count(dx)
```

```{r fig.width=5, fig.height = 4}
plt <- with_wFC1 %>%
  ungroup() %>%
  select(subject, dataset, dx, vertex_type, edge_group, wFC_score) %>%
  filter(vertex_type=="pvertex") %>%
  spread(edge_group, wFC_score) %>%
  plot_greyred_scatter_elipsed(subcort_to_VI, subcort_to_FP, dx)
  
ggdraw(plt)  
```
```{r fig.width=5, fig.height = 4}
plt <- with_wFC1 %>%
  ungroup() %>%
  select(subject, dataset, dx, vertex_type, edge_group, wFC_score) %>%
  filter(vertex_type=="tvertex") %>%
  spread(edge_group, wFC_score) %>%
  plot_greyred_scatter_elipsed(subcort_to_VI, subcort_to_FP, dx)
  
ggdraw(plt)  
```

```{r fig.width=5, fig.height = 4}
plt <- with_wFC1 %>%
  ungroup() %>%
  select(subject, dataset, dx, vertex_type, edge_group, wFC_score) %>%
  filter(vertex_type=="tvolume") %>%
  spread(edge_group, wFC_score) %>%
  plot_greyred_scatter_elipsed(subcort_to_VI, subcort_to_FP, dx)
  
ggdraw(plt)  
```


```{r fig.height=3, fig.width=8}
with_wFC_zhh %>%
  filter(WRAT3SS > 60) %>%
  filter(edge_group %in% c("subcort_to_VI")) %>%
  ggplot(aes(x = WRAT3SS, y = wFC_score, color = DX)) +
  geom_point() +
  geom_smooth(method = "lm") +
  scale_color_manual(values = c("grey20","red")) +
  facet_grid(edge_group~vertex_type, scales = "free_x") +
  theme_bw() +
  labs(x = "WRAT Standard score (ZHH Site)")
  
```
```{r fig.height=3, fig.width=8}
with_wFC_zhh %>%
  filter(WRAT3SS > 60) %>%
  filter(edge_group %in% c("subcort_to_FP")) %>%
  ggplot(aes(x = WRAT3SS, y = wFC_score, color = DX)) +
  geom_point() +
  geom_smooth(method = "lm") +
  scale_color_manual(values = c("grey20","red")) +
  facet_grid(edge_group~vertex_type, scales = "free_x") +
  theme_bw() +
  labs(x = "WRAT Standard score (ZHH Site)")
  
```

```{r fig.height=3, fig.width=8}
with_wFC1 %>%
  filter(Site %in% c("CMH", "COBRE"),
         dx == "SSD",
         wtar_std < 900) %>%
  filter(edge_group %in% c("subcort_to_VI")) %>%
  ggplot(aes(x = wtar_std, y = wFC_score, color = Site)) +
  geom_point() +
  geom_smooth(method = "lm") +
  scale_color_manual(values = c("tomato3", "orangered3")) +
  facet_grid(edge_group~vertex_type, scales = "free_x") +
  theme_bw()
  
```
```{r fig.height=3, fig.width=8}
with_wFC1 %>%
  filter(Site %in% c("CMH", "COBRE"),
         dx == "SSD",
         wtar_std < 900) %>%
  filter(edge_group %in% c("subcort_to_FP")) %>%
  ggplot(aes(x = wtar_std, y = wFC_score, color = Site)) +
  geom_point() +
  geom_smooth(method = "lm") +
  scale_color_manual(values = c("tomato3", "orangered3")) +
  facet_grid(edge_group~vertex_type, scales = "free_x") +
  theme_bw()
  
```
```{r fig.height=3, fig.width=8}
with_wFC1 %>%
  filter(Site %in% c("CMH", "COBRE"),
         dx == "SSD",
         wtar_std < 900) %>%
  filter(edge_group %in% c("subcort_to_DA")) %>%
  ggplot(aes(x = wtar_std, y = wFC_score_cliped, color = Site)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_grid(edge_group~vertex_type, scales = "free_x")
  
```


```{r fig.height=3, fig.width=8}
with_wFC1 %>%
  filter(Site %in% c("CMH", "COBRE"),
         dx == "SSD") %>%
  filter(edge_group %in% c("subcort_to_DA")) %>%
  ggplot(aes(x = panss_total_calc, y = wFC_score, color = Site)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_grid(edge_group~vertex_type, scales = "free_x")
  
```



```{r}
wf1_edgegroup_num <- unique(with_wFC1$edge_group) %>% length()
wtar_panss_models_lm_glance <- with_wFC_zhh %>%
  gather(clinical_measure, clinical_score, WRAT3SS) %>%
  filter(clinical_score > 70) %>%
  group_by(edge_group, effect_direction, vertex_type, clinical_measure) %>%
  do(glance(lm(wFC_score_cliped ~ clinical_score*DX, data = .))) 

wtar_panss_models_tidylm <- with_wFC_zhh %>%
  gather(clinical_measure, clinical_score, WRAT3SS) %>%
  filter(clinical_score > 70) %>%
  group_by(edge_group, effect_direction, vertex_type, clinical_measure) %>%
  do(tidy(lm(wFC_score_cliped ~ clinical_score*DX, data = .))) %>%
  filter(term == "clinical_score") %>%
  mutate(p_bonf = p.value*wf1_edgegroup_num)
  
wtar_panss_models_tidylm %>% 
  arrange(p.value) %>%
  select(vertex_type, clinical_measure, edge_group, statistic, p.value, p_bonf) %>% 
knitr::kable()
```

```{r}
wf1_edgegroup_num <- unique(with_wFC1$edge_group) %>% length()
wtar_panss_models_lm_glance <- with_wFC1 %>%
  filter(Site %in% c("CMH", "COBRE"),
         dx == "SSD") %>%
  gather(clinical_measure, clinical_score, wtar_std, panss_total_calc) %>%
  filter(clinical_score < 900) %>%
  group_by(edge_group, effect_direction, vertex_type, clinical_measure) %>%
  do(glance(lm(wFC_score_cliped ~ clinical_score + Site, data = .))) 

wtar_panss_models_tidylm <- with_wFC1 %>%
  filter(Site %in% c("CMH", "COBRE"),
         dx == "SSD") %>%
  gather(clinical_measure, clinical_score, wtar_std, panss_total_calc) %>%
  filter(clinical_score < 900) %>%
  group_by(edge_group, effect_direction, vertex_type, clinical_measure) %>%
  do(tidy(lm(wFC_score_cliped ~ clinical_score + Site, data = .))) %>%
  filter(term == "clinical_score") %>%
  mutate(p_bonf = p.value*wf1_edgegroup_num)
  
wtar_panss_models_tidylm %>% 
  arrange(p.value) %>%
  select(vertex_type, clinical_measure, edge_group, statistic, p.value, p_bonf) %>% knitr::kable()
```





```{r}
with_wFC1 %>%
  filter(Site %in% c("CMH", "ds000030_R1.0.5", "ZHH"),
         dx == "SSD") %>%
  gather(clinical_measure, clinical_score, starts_with("sans")) %>%
  group_by(edge_group, effect_direction, clinical_measure, vertex_type) %>%
  do(tidy(lm(wFC_score_cliped ~ clinical_score + Site, data = .))) %>%
  filter(term == "clinical_score") %>%
  mutate(p_bonf = p.value*wf1_edgegroup_num) %>%
  arrange(p.value) %>%
  select(clinical_measure, edge_group, statistic, p.value, p_bonf) %>%
  knitr::kable()
```

```{r fig.height=3, fig.width=8}
with_wFC1 %>%
  filter(Site %in% c("CMH", "ds000030_R1.0.5", "ZHH"),
         dx == "SSD") %>%
  filter(edge_group %in% c("cortDA_to_SM")) %>%
  ggplot(aes(x = sans_G_total, y = wFC_score_cliped, color = Site)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_grid(edge_group~vertex_type, scales = "free_y")
  
```



```{r fig.height=12, fig.width=12}
weighted_subject_scores %>%
  inner_join(pheno, by = c("subject", "dataset")) %>%
  filter(Site == "ZHH") %>%
  filter(effect_direction == "hypo") %>% 
  drop_na(isFEP) %>%
  ggplot(aes(x = isFEP, y = wFC_score)) +
  geom_boxplot() +
  geom_jitter(alpha = 0.3) +
  facet_grid(vertex_type~edge_group, scales = "free_y")
  
```


```{r}
with_wFC1 %>%
  filter(Site == "ZHH") %>%
  drop_na(isFEP) %>%
  group_by(edge_group, vertex_type) %>%
  do(tidy(lm(wFC_score ~ isFEP, data = .))) %>%
  mutate(p_bonf = p.value*wf1_edgegroup_num) %>%
  arrange(p.value) %>%
  filter(term != "(Intercept)") %>%
  select(term, statistic, p.value, p_bonf) %>%
  knitr::kable()
```

### refit the models with Education included

```{r}
refit_w_edu_pooled_glance <- with_wFC1 %>%
  inner_join(pheno, by = c("subject","dataset")) %>%
  filter(in_matched_sample) %>%
  group_by(edge_group, vertex_type) %>%
  do(glance(lm(wFC_score ~ DX + Age_match_pt + Sex + fd_mean_match_pt + Site.x + Edu, data = .))) %>%
  select(edge_group, vertex_type, df.residual) %>%
  distinct()

refit_w_edu_pooled_tidy <- with_wFC1 %>%
  inner_join(pheno, by = c("subject","dataset")) %>%
  filter(in_matched_sample) %>%
  group_by(edge_group, vertex_type) %>%
  do(tidy(lm(wFC_score ~ DX + Age_match_pt + Sex + fd_mean_match_pt + Site.x + Edu, data = .))) %>%
  mutate(p_bonf = p.value*wf1_edgegroup_num) 

refit_w_edu_pooled <- refit_w_edu_pooled_glance %>% 
  select(edge_group, vertex_type, `df.residual`) %>%
  distinct() %>%
  inner_join(refit_w_edu_pooled_tidy, by = c("vertex_type", "edge_group")) %>%
  mutate(Site = "pooled") %>%
  mutate(
      beta = specify_decimal(estimate,2),
      beta_se = specify_decimal(std.error,2),
      t_stat = specify_decimal(statistic,2),
      pval_str = ifelse(p_bonf < 0.001, 
                           format(p_bonf, scientific = TRUE, digits = 2),
                           specify_decimal(p_bonf,3)),
      pval_str = ifelse(p_bonf > 0.10, "ns", pval_str),
      report_str = str_glue("beta(SE)={beta}({beta_se}), t({df.residual})={t_stat}, p={pval_str}")) %>%
    filter(term == "DXSSD") %>%
    select(edge_group, vertex_type, report_str) %>%
    spread(vertex_type, report_str)

refit_w_edu_pooled %>% knitr::kable()
```

The Site-wise version

```{r}
refit_w_edu_sitewise_glance <- with_wFC1 %>%
  inner_join(pheno, by = c("subject","dataset")) %>%
  filter(in_matched_sample) %>%
  group_by(edge_group, vertex_type, Site.x) %>%
  do(glance(lm(wFC_score ~ DX + Age_match_pt + Sex + fd_mean_match_pt, data = .))) %>%
  select(edge_group, vertex_type, Site.x, df.residual) %>%
  distinct()

refit_w_edu_sitewise_tidy <- with_wFC1 %>%
  inner_join(pheno, by = c("subject","dataset")) %>%
  filter(in_matched_sample) %>%
  group_by(edge_group, vertex_type, Site.x) %>%
  do(tidy(lm(wFC_score ~ DX + Age_match_pt + Sex + fd_mean_match_pt, data = .))) %>%
  mutate(p_bonf = p.value*wf1_edgegroup_num) 

refit_w_edu_sitewise <- refit_w_edu_sitewise_glance %>% 
  select(edge_group, vertex_type, Site.x, `df.residual`) %>%
  distinct() %>%
  inner_join(refit_w_edu_sitewise_tidy, by = c("vertex_type", "edge_group", "Site.x")) %>%
  mutate(
      beta = specify_decimal(estimate,2),
      beta_se = specify_decimal(std.error,2),
      t_stat = specify_decimal(statistic,2),
      pval_str = ifelse(p_bonf < 0.001, 
                           format(p_bonf, scientific = TRUE, digits = 2),
                           specify_decimal(p_bonf,3)),
      pval_str = ifelse(p_bonf > 0.10, "ns", pval_str),
      report_str = str_glue("beta(SE)={beta}({beta_se}), t({df.residual})={t_stat}, p={pval_str}")) %>%
    filter(term == "DXSSD") %>%
    select(edge_group, vertex_type, Site.x, report_str) %>%
    spread(vertex_type, report_str)

refit_w_edu_sitewise  %>% knitr::kable()
```





```{r}
report_model_beta_t_wdf <- function(tidy_model, glance_models, this_term, p_value_col = p.value, ...) {
  p_value_col = enquo(p_value_col)
  the_df <- glance_models %>% 
    filter(...) %>%
    pull(df.residual) %>% unique()
  tidy_model %>% 
    filter(...) %>%
    filter(term == this_term) %>%
    mutate(
      beta = specify_decimal(estimate,2),
      beta_se = specify_decimal(std.error,2),
      t_stat = specify_decimal(statistic,2),
      pval_str = ifelse(!!p_value_col < 0.001, 
                           format(!!p_value_col, scientific = TRUE, digits = 2),
                           specify_decimal(!!p_value_col,3)),
      pval_str = ifelse(!!p_value_col > 0.10, "ns", pval_str),
      report_str = str_glue("beta(SE)={beta}({beta_se}), t({the_df})={t_stat}, p={pval_str}")) %>%
    pull(report_str)
}



report_model_beta_t_wdf(wtar_panss_models_tidylm,                         wtar_panss_models_lm_glance,"clinical_score", p_value_col = p_bonf,                         vertex_type == "pvertex", clinical_measure=="wtar_std", edge_group == "subcort_to_VI")
```

```{r}
report_wtar_model_t <- function(this_edgegroup, this_vertextype) {
  report_model_beta_t_wdf(
      wtar_panss_models_tidylm,   
      wtar_panss_models_lm_glance,
      "clinical_score", 
      p_value_col = p_bonf,                         
      vertex_type == this_vertextype, 
      clinical_measure=="wtar_std", 
      edge_group == this_edgegroup)
  
  }

report_wtar_model_t("subcort_to_VI", "tvolume")
```



### The results write-up

A significant main effect of SSD diagnosis was also observed when models were refitted with an additional covariate of years of Education (see Supplemental Table 4 for all model fits).  When models were fit separately for each site all model fits remained significant for the two larger cohort ZHH and CAMH sample, with more variability observed in the COBRE and UCLA cohorts. 
Interestingly, hypoconnectivity between the subcortical areas and the frontal-partietal network was negatively correlated with hyperconnectivity between subcortical areas and the visual networks (see Figure 4a). These dysconnectivity patterns were also associated with verbal intelligence (WTAR scores) within participants with SSD from the COBRE and CAMH cohorts (subcortical to VI: template volume `r report_wtar_model_t("subcort_to_VI", "tvolume")` , template surface `r report_wtar_model_t("subcort_to_VI", "tvertex")`, PINT `r report_wtar_model_t("subcort_to_VI", "pvertex")` ; subcortical to FP: template volume `r report_wtar_model_t("subcort_to_FP", "tvolume")` template surface `r report_wtar_model_t("subcort_to_FP", "tvertex")`, PINT `r report_wtar_model_t("subcort_to_FP", "pvertex")`)see Supplemental Figure 4b). However, these associations between intelligence and functinal connectivity were not observed in the ZHH sample where intelligence was measures using the WRAT. Clinical scores (SANS for CMH, UCLA, ZHH cohorts) nor PANSS total scores (in CAMH and COBRE), were not correlated with any FC weighted scores after correction for multiple comparisons. In the ZHH sample, no significant differences between first episode and chronic SSD participants in FC scores were observed after correction for multiple comparisons ().

